### 2014-11-26 paper/paper.tex
add latex template from vldb2015

% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2012
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>
% Removed the requirement to include *bbl file in here. (AhmetSacan, Sep2012)
% Fixed the equation on page 3 to prevent line overflow. (AhmetSacan, Sep2012)

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\begin{document}

% ****************** TITLE ****************************************

\title{A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX
Format\titlenote{for use with vldb.cls}}

% possible, but not really needed or used for PVLDB:
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as\textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
(The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle

\begin{abstract}
The abstract for your paper for the PVLDB Journal submission.
The template and the example document are based on the ACM SIG Proceedings  templates. This file is part of a package for preparing the submissions for review. These files are in the camera-ready format, but they do not contain the full copyright note.
Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
\end{abstract}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM / PVLDB has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.pdf} files to be
displayable with \LaTeX (See Figures  and  ).  More details on each of these is found in the
\textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{fly}
\caption{A sample black and white graphic (.pdf format).}
\label{fig:fly}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1in,height=1in]{fly}
\caption{A sample black and white graphic (.pdf format)
that has been resized with the \texttt{includegraphics} command.}
\label{fig:bigfly}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption (See Figure~\ref{fig:flies}). And don't forget to end the environment with {figure*}, not {figure}!

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic (.pdf format)
that needs to span two columns of text.}
\label{fig:flies}
\end{figure*}

Note that only {\textbf{.pdf}} files were used; if you want to include
{\textbf{.ps}} or {\textbf{.eps}} formats, you can use the
\texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{align*}
l&=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ] \\
&= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{align*}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

% ensure same length columns on last page (might need two sub-sequent latex runs)
\balance

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references).

%APPENDIX is optional.
% ****************** APPENDIX **************************************
% Example of an appendix; typically would start on a new page
%pagebreak

\begin{appendix}
You can use an appendix for optional proofs or details of your evaluation which are not absolutely necessary to the core understanding of your paper.

\section{Final Thoughts on Good Layout}
Please use readable font sizes in the figures and graphs. Avoid tempering with the correct border values, and the spacing (and format) of both text and captions of the PVLDB format (e.g. captions are bold).

At the end, please check for an overall pleasant layout, e.g. by ensuring a readable and logical positioning of any floating figures and tables. Please also check for any line overflows, which are only allowed in extraordinary circumstances (such as wide formulas or URLs where a line wrap would be counterintuitive).

Use the \texttt{balance} package together with a \texttt{\char'134 balance} command at the end of your document to ensure that the last page has balanced (i.e. same length) columns.

\end{appendix}

\end{document}

### 2014-12-05 code/invindex.js
add extension of IDBRequest

@@ -16,17 +16,9 @@ var InvIndex = function(objStore, name, field, dbconn) {
 	
     // Perform index search for a phrase
     this.get = function(text) {
-    	
-    	var ret = {
-			// Caller will override these if needed
-			onstatusupdate: function(){},
-			onsuccess: function(){},
-			onerror: function(){},
-			source: this.objectStore,
-			transaction: this.transaction,
-		};
+    	var ret = new IDBIndexRequest(this.objectStore, this.transaction);
+
     	var result_id;
-    	
     	var objStore = this.objectStore;
     	
     	var tokenCount = basictokenize(text);
@@ -43,7 +35,6 @@ var InvIndex = function(objStore, name, field, dbconn) {
     				result_id = result[i];
     			}
    				
-   				console.log(result_id);
    				var request_text = objStore.get(result_id);
    				request_text.onerror = function(evt) {
     				console.log(evt, token);

### 2014-12-06 code/trieindex.js
don't use compound key in trieindex

@@ -15,29 +15,28 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
     // Perform prefix search
     // Return list of document objects with matches
     this.get = function(text) {
-        if (this.mode == "suffix") {
+        /////
+        console.log(this);
+        var requestText = this.store.get(0);
+        requestText.onerror = function(evt) {
+            console.log(evt, text);
+            return evt;
+        };
+        requestText.onsuccess = function(evt) {
+            console.log(requestText);
+            if (evt.target.result){
+                console.log('FOUND IT');
+            }
+        };
+        return {};
+        //////
+        /*if (this.mode == "suffix") {
             text = reverse(text);
         }
-        var docIds;
-    	var objStore = this.objectStore;
-    	
-        var parentId = 0;
-    	for (var i=0; i<text.length; i++) {
-            var c = text.charAt(i);
-    		var request = this.index.get([parentId, c]);
-    		request.onerror = function(evt) {
-    			console.log(evt, text);
-    			return evt;
-    		};
-    		request.onsuccess = function(evt) {
-                if (evt.target.result) {
-                    docIds = evt.target.result.docIds;
-                    console.log(docIds);
-                } else {
-                    return [];
-                }
-            };
-        }
+        var objStore = this.objectStore;
+        var docIds = [];
+        searchHelper(this, docIds, text, 0);
+
         var results = [];
         for (var i=0; i<docIds.length; i++) {
             docId = docIds[i];
@@ -54,8 +53,34 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
                 }
             };
         }
-        return results;
+        return results;*/
     };
+
+    function searchHelper(trieindex, docIds, token, parentId) {
+        console.log("token:", token, "parentId:", parentId);
+        if (token.length == 0)
+            return;
+        var c = token.charAt(0);
+        var request = trieindex.parentCharIndex.get([0, 'w']);
+        (function(trieindex, token, parentId) {
+            request.onsuccess = function(evt) {
+                console.log(evt);
+                if (evt.target.result) {
+                    if (token.length == 1) {
+                        result = evt.target.result;
+                        console.log(result.docIds);
+                        docIds.push.apply(docIds, result.docIds);
+                    } else {
+                        searchHelper(trieindex, docIds, token.substring(1), result.id);
+                    }
+                }
+            };
+            request.onerror = function(evt) {
[…]

### 2014-12-06 code/trieindex.js
fixed prefix search, only returns doc ids

@@ -6,6 +6,7 @@ Constructs a TrieIndex for prefix/suffix search.
 var TrieIndex = function(objStore, name, field, mode, dbconn) {
 
 	this.objectStore = objStore;
+    this.transaction = objStore.transaction;
 	this.name = name;
 	this.unique = false;
 	this.indexField = field;
@@ -15,29 +16,15 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
     // Perform prefix search
     // Return list of document objects with matches
     this.get = function(text) {
-        /////
-        console.log(this);
-        var requestText = this.store.get(0);
-        requestText.onerror = function(evt) {
-            console.log(evt, text);
-            return evt;
-        };
-        requestText.onsuccess = function(evt) {
-            console.log(requestText);
-            if (evt.target.result){
-                console.log('FOUND IT');
-            }
-        };
-        return {};
-        //////
-        /*if (this.mode == "suffix") {
+        if (this.mode == "suffix") {
             text = reverse(text);
         }
         var objStore = this.objectStore;
+        var trieIndex = this.index.index(this.indexName);
         var docIds = [];
-        searchHelper(this, docIds, text, 0);
+        searchHelper(trieIndex, docIds, text, 0);
 
-        var results = [];
+        /*var results = [];
         for (var i=0; i<docIds.length; i++) {
             docId = docIds[i];
             console.log(docId);
@@ -56,22 +43,22 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         return results;*/
     };
 
-    function searchHelper(trieindex, docIds, token, parentId) {
+    function searchHelper(trieIndex, docIds, token, parentId) {
         console.log("token:", token, "parentId:", parentId);
         if (token.length == 0)
             return;
         var c = token.charAt(0);
-        var request = trieindex.parentCharIndex.get([0, 'w']);
-        (function(trieindex, token, parentId) {
+        var request = trieIndex.get([parentId, c]);
+        (function(trieIndex, docIds, token, parentId) {
             request.onsuccess = function(evt) {
                 console.log(evt);
                 if (evt.target.result) {
+                    var result = evt.target.result;
                     if (token.length == 1) {
-                        result = evt.target.result;
                         console.log(result.docIds);
                         docIds.push.apply(docIds, result.docIds);
                     } else {
-                        searchHelper(trieindex, docIds, token.substring(1), result.id);
[…]

### 2014-12-06 code/invindex.js
add tokenize to Lucy static class

@@ -17,11 +17,10 @@ var InvIndex = function(objStore, name, field, dbconn) {
     // Perform index search for a phrase
     this.get = function(text) {
     	var ret = new IDBIndexRequest(this.objectStore, this.transaction);
-
     	var result_id;
     	var objStore = this.objectStore;
     	
-    	var tokenCount = basictokenize(text);
+    	var tokenCount = Lucy.tokenize(text);
     	for (var token in tokenCount) {
     		var request = this.index.get(token);
     		request.onerror = function(evt) {
@@ -53,34 +52,17 @@ var InvIndex = function(objStore, name, field, dbconn) {
    				
     		};
     	}
-    	
     	return ret;
     };
 
     // Tokenize and normalize data before insertion.
     this.insert = function(text) {
-    	var tokenCount = basictokenize(text);
+    	var tokenCount = Lucy.tokenize(text);
 				
 		for (var token in tokenCount) {
 			indexToken(id, token, tokenCount[token]);
 		}
     };
-    
-	function basictokenize(s) {
-		s = s.toLowerCase();
-		var tokens = s.match(/\w+/g);
-		
-		var tokenCount = {};
-		for (var i=0; i<tokens.length; i++) {
-			if (tokens[i] in tokenCount) {
-				tokenCount[tokens[i]]++;
-			} else {
-				tokenCount[tokens[i]] = 1;
-			}
-		}
-		
-		return tokenCount;
-	}
 	
 	function indexToken(invindex, id, token, count) {	
 		var getter = invindex.index.get(token);
@@ -127,7 +109,7 @@ var InvIndex = function(objStore, name, field, dbconn) {
 				var value = cursor.value[invindex.indexField];
 				var id = cursor.value[keyval];
 				//tokenize string
-				var tokenCount = basictokenize(value);
+				var tokenCount = Lucy.tokenize(value);
 				
 				for (var token in tokenCount) {
 					indexToken(invindex, id, token, tokenCount[token]);

### 2014-12-06 code/lucy.js

@@ -4,17 +4,50 @@
  * 
  */
 
+
+/*
+ * Static class for general purpose natural language processing functions 
+ * 
+ */
+function Lucy() {};
+
+Lucy.tokenize = function(string) { 
+	string = string.toLowerCase();
+	var tokens = string.match(/\w+/g);
+	
+	var tokenCount = {};
+	for (var i=0; i<tokens.length; i++) {
+		if (tokens[i] in tokenCount) {
+			tokenCount[tokens[i]]++;
+		} else {
+			tokenCount[tokens[i]] = 1;
+		}
+	}
+	
+	return tokenCount;
+};
+
+
+
+
 /*
  * Extends IDBRequest
  * 
  */
 var IDBIndexRequest = function(objStore, transaction) {
-	onsuccess = function(){};
-	onerror = function(){};
-	source = objStore;
-	transaction = transaction;
+	this.onsuccess = function(){};
+	this.onerror = function(){};
+	this.source = objStore;
+	this.transaction = transaction;
 };
 
+IDBIndexRequest.prototype = IDBRequest;
+
+
+
+/*
+ * Intercept functions of IDBObjectStore
+ */
 
 (function() {
 	

### 2014-12-06 code/invindex.js
add stopwords and stemming

@@ -3,13 +3,14 @@
 Constructs an InvIndex for full-text search.
 */
 
-var InvIndex = function(objStore, name, field, dbconn) {
+var InvIndex = function(objStore, name, field, dbconn, language) {
 
 	this.objectStore = objStore;
 	this.name = name;
 	this.unique = false;
 	this.transaction = objStore.transaction;
 	
+	this.language = language;
 	this.indexField = field;
 	
 	createIndex(this, dbconn);

### 2014-12-06 code/lucy.js

@@ -5,11 +5,30 @@
  */
 
 
+var SUPPORTED_LANGUAGES = ['english',
+						   'danish',
+						   'dutch',
+						   'finnish',
+						   'french',
+						   'german',
+						   'hungarian',
+						   'italian',
+						   'norwegian',
+						   'portuguese',
+						   'russian',
+						   'spanish',
+						   'swedish',
+						   'romanian',
+						   'turkish'];
+
 /*
  * Static class for general purpose natural language processing functions 
  * 
  */
+
 function Lucy() {};
+
+Lucy.language = "english";
 
 Lucy.tokenize = function(string) { 
 	string = string.toLowerCase();
@@ -17,16 +36,35 @@ Lucy.tokenize = function(string) {
 	
 	var tokenCount = {};
 	for (var i=0; i<tokens.length; i++) {
-		if (tokens[i] in tokenCount) {
-			tokenCount[tokens[i]]++;
-		} else {
-			tokenCount[tokens[i]] = 1;
+		if (!Lucy.isStopWord(tokens[i])) {
+			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
+			if (stem in tokenCount) {
+				tokenCount[stem]++;
+			} else {
+				tokenCount[stem] = 1;
+			}
 		}
 	}
 	
 	return tokenCount;
 };
 
+Lucy.isStopWord = function(word) {
+	if(Lucy.stopwords.indexOf(word) <= 0) {
+		return false;
+	} else {
+		return true;	
+	}
+};
+
+Lucy.stemmer = function(language) {
+	var snowball = new Snowball(language);
+	return function(word) {
+		snowball.setCurrent(word);
+		snowball.stem();
+		return snowball.getCurrent();
+	};
+};
 
 
 
@@ -140,8 +178,15 @@ IDBIndexRequest.prototype = IDBRequest;
             // build the appropriate index using the builder functions below
             // add new index to this.textSearchIndexes
             var dbconn = optionalArgs["dbconn"];
+            var language = optionalArgs["language"];
+            if (!language || (SUPPORTED_LANGUAGES.indexOf(language) <= -1)) {
+            	language = "english";
+            }
+            language = language.toLowerCase();
+            Lucy.language = language;
+            
             if (optionalArgs["type"] == "inverted") {
-            	return buildInvertedIndex(this, indexName, keypath, dbconn);
+            	return buildInvertedIndex(this, indexName, keypath, dbconn, language);
[…]

### 2014-12-06 code/stopwords/english_stopwords.js

@@ -1,0 +1,547 @@
+
+Lucy.stopwords = [
+"",
+"a's",
+"able",
+"about",
+"above",
+"according",
+"accordingly",
+"across",
+"actually",
+"after",
+"afterwards",
+"again",
+"against",
+"ain't",
+"all",
+"allow",
+"allows",
+"almost",
+"alone",
+"along",
+"already",
+"also",
+"although",
+"always",
+"am",
+"among",
+"amongst",
+"an",
+"and",
+"another",
+"any",
+"anybody",
+"anyhow",
+"anyone",
+"anything",
+"anyway",
+"anyways",
+"anywhere",
+"apart",
+"appear",
+"appreciate",
+"appropriate",
+"are",
+"aren't",
+"around",
+"as",
+"aside",
+"ask",
+"asking",
+"associated",
+"at",
+"available",
+"away",
+"awfully",
+"be",
+"became",
+"because",
+"become",
+"becomes",
+"becoming",
+"been",
+"before",
+"beforehand",
+"behind",
+"being",
+"believe",
+"below",
+"beside",
+"besides",
+"best",
+"better",
+"between",
+"beyond",
+"both",
+"brief",
+"but",
+"by",
+"c'mon",
+"c's",
+"came",
+"can",
+"can't",
+"cannot",
+"cant",
+"cause",
+"causes",
+"certain",
+"certainly",
+"changes",
+"clearly",
+"co",
+"com",
+"come",
+"comes",
+"concerning",
+"consequently",
+"consider",
+"considering",
+"contain",
+"containing",
+"contains",
+"corresponding",
+"could",
+"couldn't",
+"course",
+"currently",
+"definitely",
+"described",
+"despite",
+"did",
+"didn't",
+"different",
+"do",
+"does",
+"doesn't",
+"doing",
+"don't",
+"done",
+"down",
+"downwards",
+"during",
+"each",
+"edu",
+"eg",
+"eight",
+"either",
+"else",
+"elsewhere",
+"enough",
+"entirely",
+"especially",
+"et",
+"etc",
+"even",
+"ever",
+"every",
+"everybody",
+"everyone",
+"everything",
+"everywhere",
+"ex",
+"exactly",
+"example",
+"except",
+"far",
+"few",
+"fifth",
+"first",
+"five",
+"followed",
+"following",
+"follows",
+"for",
[…]

### 2014-12-06 code/demo.js
return multiple matches if they exist

@@ -133,12 +133,21 @@ $("#submit-search").onclick = function () {
 		
 		//get returns a single entry (one with lowest key value)
 		var request = index.get(searchQuery);
+		console.log(request);
 		request.onerror = function(evt) {
 			console.log(evt, searchQuery);
 		};
 		request.onsuccess = function(evt) {
 			var searchResults = $('.search-results');
-			searchResults.textContent = request.result.text;
+			var result = "";
+			if (request.result.length == 0) {
+				result = "No results";
+			} else {
+				for (var i=0; i<request.result.length; i++) {
+					result = result + "<P>" + request.result[i].text + "</P>";
+				}
+			}
+			searchResults.innerHTML = result;
 		};
 		
 		evt.target.result.close();

### 2014-12-06 code/invindex.js

@@ -18,40 +18,45 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
     // Perform index search for a phrase
     this.get = function(text) {
     	var ret = new IDBIndexRequest(this.objectStore, this.transaction);
-    	var result_id;
+    	var result_ids;
     	var objStore = this.objectStore;
     	
     	var tokenCount = Lucy.tokenize(text);
-    	for (var token in tokenCount) {
-    		var request = this.index.get(token);
-    		request.onerror = function(evt) {
-    			console.log(evt, token);
-    			ret.result = evt.result;
-    		};
-    		request.onsuccess = function(evt) {
-    			var result = request.result.ids;
-    			console.log(result);
-    			for (var i=0; i<result.length; i++) {
-    				result_id = result[i];
-    			}
-   				
-   				var request_text = objStore.get(result_id);
-   				request_text.onerror = function(evt) {
-    				console.log(evt, token);
-    				return evt;
-    			};
-    			request_text.onsuccess = function(evt) {
-    				console.log(request_text);
-    				if (request_text.result){
-    					ret.result = request_text.result;
-    					ret.onsuccess();
-    				} else {
-    					ret.result = evt;
-    				}
-    			};
-    			
-   				
-    		};
+    	
+    	ret.result = [];
+    	if (tokenCount.length == 0) {
+	    	ret.onsuccess();
+    	} else {
+    		var counter = 0;
+	    	for (var token in tokenCount.tokens) {
+	    		var request = this.index.get(token);
+	    		counter++;
+	    		
+	    		request.onerror = function(evt) {
+	    			console.log(evt, token);
+	    			ret.result = evt.result;
+	    			ret.onerror();
+	    		};
+	    		request.onsuccess = function(evt) {
+	    			var result_ids = request.result.ids;
+	
+	    			for (var j=0; j<result_ids.length; j++) {
+	    				var request_text = objStore.get(result_ids[j]);
+		    			request_text.onerror = function(evt) {
+			    			console.log(evt, token);
+			    			ret.onerror();
+			    		};
+		    			request_text.onsuccess = function(evt) {
+		    				if (evt.srcElement.result){
+		    					ret.result.push(evt.srcElement.result);
+		    				}
+		    				if (counter == tokenCount.length && j == result_ids.length) {
+								ret.onsuccess();
+							}
+		    			};
+	    			}
+	    		};
+    		}
     	}
[…]

### 2014-12-06 code/lucy.js

@@ -34,15 +34,18 @@ Lucy.tokenize = function(string) {
 	string = string.toLowerCase();
 	var tokens = string.match(/\w+/g);
 	
-	var tokenCount = {};
+	var tokenCount = {length: 0,
+					  tokens: {}};
+					  
 	for (var i=0; i<tokens.length; i++) {
 		if (!Lucy.isStopWord(tokens[i])) {
 			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
 			if (stem in tokenCount) {
-				tokenCount[stem]++;
+				tokenCount["tokens"][stem]++;
 			} else {
-				tokenCount[stem] = 1;
+				tokenCount["tokens"][stem] = 1;
 			}
+			tokenCount.length++;
 		}
 	}
 	

### 2014-12-06 code/invindex.js
stopwords are searched if query has only stopwords, no results still trigger onsuccess

@@ -24,23 +24,20 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
     	var tokenCount = Lucy.tokenize(text);
     	
     	ret.result = [];
-    	if (tokenCount.length == 0) {
-	    	ret.onsuccess();
-    	} else {
-    		var counter = 0;
-	    	for (var token in tokenCount.tokens) {
-	    		var request = this.index.get(token);
-	    		counter++;
-	    		
-	    		request.onerror = function(evt) {
-	    			console.log(evt, token);
-	    			ret.result = evt.result;
-	    			ret.onerror();
-	    		};
-	    		request.onsuccess = function(evt) {
-	    			var result_ids = request.result.ids;
-	
-	    			for (var j=0; j<result_ids.length; j++) {
+		var counter = 0;
+    	for (var token in tokenCount.tokens) {
+    		var request = this.index.get(token);
+    		counter++;
+    		
+    		request.onerror = function(evt) {
+    			console.log(evt, token);
+    			ret.result = evt.result;
+    			ret.onerror();
+    		};
+    		request.onsuccess = function(evt) {
+				if (request.result) {
+					var result_ids = request.result.ids;
+					for (var j=0; j<result_ids.length; j++) {
 	    				var request_text = objStore.get(result_ids[j]);
 		    			request_text.onerror = function(evt) {
 			    			console.log(evt, token);
@@ -55,8 +52,12 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
 							}
 		    			};
 	    			}
-	    		};
-    		}
+				} else {
+					if (counter == tokenCount.length) {
+						ret.onsuccess();
+					}
+				}
+    		};
     	}
     	return ret;
     };

### 2014-12-06 code/lucy.js

@@ -37,6 +37,9 @@ Lucy.tokenize = function(string) {
 	var tokenCount = {length: 0,
 					  tokens: {}};
 					  
+	var stopwordCount = {length: 0, 
+						 tokens: {}};
+					  
 	for (var i=0; i<tokens.length; i++) {
 		if (!Lucy.isStopWord(tokens[i])) {
 			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
@@ -46,10 +49,21 @@ Lucy.tokenize = function(string) {
 				tokenCount["tokens"][stem] = 1;
 			}
 			tokenCount.length++;
+		} else {
+			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
+			if (stem in stopwordCount) {
+				stopwordCount["tokens"][stem]++;
+			} else {
+				stopwordCount["tokens"][stem] = 1;
+			}
+			stopwordCount.length++;
 		}
 	}
-	
-	return tokenCount;
+	if (tokenCount.length == 0) {
+		return stopwordCount;
+	} else {
+		return tokenCount;
+	}
 };
 
 Lucy.isStopWord = function(word) {

### 2014-12-06 code/invindex.js
weights and scoring now works, results are returned in reverse score order

@@ -3,6 +3,7 @@
 Constructs an InvIndex for full-text search.
 */
 
+
 var InvIndex = function(objStore, name, field, dbconn, language) {
 
 	this.objectStore = objStore;
@@ -23,20 +24,40 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
     	
     	var tokenCount = Lucy.tokenize(text);
     	
-    	ret.result = [];
-		var counter = 0;
+    	var result_dict = {};
+    	
+    	var finish_counter = {count: 0};
+    	for (var token in tokenCount.tokens) {
+    		finish_counter[token] = undefined;
+    		finish_counter.count++;
+    	}
+    	
+		var check_done = function() {
+			if (finish_counter.count == 0) return true;
+			for (var vals in finish_counter) {
+				if (finish_counter[vals] != 0) {
+					return false;
+				}
+			}
+			return true;
+		};
+
     	for (var token in tokenCount.tokens) {
     		var request = this.index.get(token);
-    		counter++;
-    		
+    		var weight = tokenCount.tokens[token];
     		request.onerror = function(evt) {
     			console.log(evt, token);
     			ret.result = evt.result;
     			ret.onerror();
     		};
     		request.onsuccess = function(evt) {
-				if (request.result) {
-					var result_ids = request.result.ids;
+    			finish_counter.count--;
+				if (evt.srcElement.result) {
+					var curr_token = evt.srcElement.result.token;
+					var result_ids = evt.srcElement.result.ids;
+					
+					finish_counter[curr_token] = result_ids.length;
+					
 					for (var j=0; j<result_ids.length; j++) {
 	    				var request_text = objStore.get(result_ids[j]);
 		    			request_text.onerror = function(evt) {
@@ -44,16 +65,25 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
 			    			ret.onerror();
 			    		};
 		    			request_text.onsuccess = function(evt) {
-		    				if (evt.srcElement.result){
-		    					ret.result.push(evt.srcElement.result);
+		    				finish_counter[curr_token]--;
+		    				var result = evt.srcElement.result;
+		    				if (result){
+		    					if (result.id in result_dict) {
+		    						result_dict[result.id].score += weight;
+		    					} else {
+			    					result_dict[result.id] = result;
+			    					result_dict[result.id].score = weight;
+			    				}
 		    				}
[…]

### 2014-12-06 code/lucy.js

@@ -21,6 +21,8 @@ var SUPPORTED_LANGUAGES = ['english',
 						   'romanian',
 						   'turkish'];
 
+
+
 /*
  * Static class for general purpose natural language processing functions 
  * 
@@ -83,6 +85,19 @@ Lucy.stemmer = function(language) {
 	};
 };
 
+// convert dictionary to ordered list, reverse score
+Lucy.convert_dict = function(dict) {
+	function comparator(a, b) {
+		return b.score - a.score;
+	}
+	
+	var olist = [];
+	for (var item in dict) {
+		olist.push(dict[item]);
+	}
+	olist.sort(comparator);
+	return olist;
+};
 
 
 /*
@@ -94,6 +109,7 @@ var IDBIndexRequest = function(objStore, transaction) {
 	this.onerror = function(){};
 	this.source = objStore;
 	this.transaction = transaction;
+	this.result = undefined;
 };
 
 IDBIndexRequest.prototype = IDBRequest;
@@ -151,8 +167,6 @@ IDBIndexRequest.prototype = IDBRequest;
     Raise DOMException with type DataError if key invalid
     */  
     IDBObjectStore.prototype.index = function(field, optionalArgs) {
-    	console.log(this.fieldToIndex);
-    	console.log(this.textSearchIndexes);
     	
     	if (field in this.fieldToIndex) {
 			var indexName = this.fieldToIndex[field];
@@ -161,10 +175,8 @@ IDBIndexRequest.prototype = IDBRequest;
 			textIndex.objectStore = this;
 			
 			var transaction = this.transaction;
-			console.log(transaction);
 			textIndex.index = transaction.objectStore(indexName);
 			textIndex.transaction = transaction;
-			console.log(textIndex);
 			return textIndex;
     	}
         return _index.apply(this, arguments);

### 2014-12-06 code/stopwords/english_stopwords.js

@@ -1,7 +1,7 @@
 
 Lucy.stopwords = [
 "",
-"a's",
+"a",
 "able",
 "about",
 "above",
@@ -78,7 +78,7 @@ Lucy.stopwords = [
 "but",
 "by",
 "c'mon",
-"c's",
+"c",
 "came",
 "can",
 "can't",
@@ -352,6 +352,7 @@ Lucy.stopwords = [
 "relatively",
 "respectively",
 "right",
+"s",
 "said",
 "same",
 "saw",
@@ -401,7 +402,7 @@ Lucy.stopwords = [
 "such",
 "sup",
 "sure",
-"t's",
+"t",
 "take",
 "taken",
 "tell",

### 2014-12-06 paper/paper.tex
abstract

@@
 
-\title{A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX
-Format\titlenote{for use with vldb.cls}}
+\title{Client Side Indexes for Fast Full-Text Searching}
 
@@
 
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
+\numberofauthors{3}
 
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
-       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+Amy X. Zhang\\
+       \email{axz@mit.edu}
+\alignauthor Lea Verou\\
+       \email{leaverou@mit.edu}
+\alignauthor Manali Naik\\
+       \email{manalinaik@mit.edu}
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
-(The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
 
@@
 \begin{abstract}
-The abstract for your paper for the PVLDB Journal submission.
-The template and the example document are based on the ACM SIG Proceedings  templates.
-This file is part of a package for preparing the submissions for review.
-These files are in the camera-ready format, but they do not contain the full copyright note.
-Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
+
+Today, many applications on the web use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
+However, standard client side databases within browsers do not currently support full-text searching. 
+In this paper, we describe a client side search engine built on top of IndexedDB that makes use of several types of indexes common to many well-known server side search engines.
+We compare the performance of different indexes on different types of full-text content and queries and find that....
+We also compare the performance of our system with that of fully server side systems and examine scenarios where a hybrid approach may be fastest. We find that...
+
 \end{abstract}
@@
 \section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM / PVLDB has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (2.54cm [1"] top and
-bottom and 1.9cm [.75"] left and right; specified column width
-(8.45cm [3.33"]) and gutter size (.083cm [.33"]).
-
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
 

### 2014-12-06 code/trieindex.js
trie index search works (really slow to build)

@@ -19,54 +19,65 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         if (this.mode == "suffix") {
             text = reverse(text);
         }
-        var objStore = this.objectStore;
         var trieIndex = this.index.index(this.indexName);
         var docIds = [];
-        searchHelper(trieIndex, docIds, text, 0);
 
-        /*var results = [];
-        for (var i=0; i<docIds.length; i++) {
-            docId = docIds[i];
-            console.log(docId);
-            var requestText = objStore.get(docId);
-            requestText.onerror = function(evt) {
-                console.log(evt, text);
-                return evt;
-            };
-            requestText.onsuccess = function(evt) {
-                console.log(requestText);
-                if (evt.target.result){
-                    results.append(evt.target.result);
-                }
-            };
-        }
-        return results;*/
+        var ret = new IDBIndexRequest(this.objectStore, this.transaction);
+        ret.result = [];
+        searchHelper(trieIndex, docIds, text, 0, ret, this.objectStore);
+        return ret;
     };
 
-    function searchHelper(trieIndex, docIds, token, parentId) {
+    function searchHelper(trieIndex, docIds, token, parentId, ret, objStore) {
         console.log("token:", token, "parentId:", parentId);
         if (token.length == 0)
-            return;
+            ret.onsuccess();
         var c = token.charAt(0);
         var request = trieIndex.get([parentId, c]);
-        (function(trieIndex, docIds, token, parentId) {
+        (function(trieIndex, docIds, token, parentId, ret, objStore) {
             request.onsuccess = function(evt) {
-                console.log(evt);
                 if (evt.target.result) {
                     var result = evt.target.result;
                     if (token.length == 1) {
                         console.log(result.docIds);
                         docIds.push.apply(docIds, result.docIds);
+                        populateResultText(docIds, ret, objStore);
                     } else {
-                        searchHelper(trieIndex, docIds, token.substring(1), result.id);
+                        searchHelper(trieIndex, docIds, token.substring(1), result.id, ret, objStore);
                     }
+                } else {
+                    ret.onsuccess();
                 }
             };
             request.onerror = function(evt) {
     			console.log(evt, token);
-    			return evt;
+    			ret.onerror();
     		};
-        })(trieIndex, docIds, token, parentId);
+        })(trieIndex, docIds, token, parentId, ret, objStore);
+    }
+
+    function populateResultText(docIds, ret, objStore) {
[…]

### 2014-12-06 paper/paper.tex
add some references

@@
 
-\title{Client Side Indexes for Fast Full-Text Searching}
+\title{Client-Side Indexes for Fast Full-Text Searching}
 
@@
 
-Today, many applications on the web use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
+Many applications on the web use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
 However, standard client side databases within browsers do not currently support full-text searching. 
-In this paper, we describe a client side search engine built on top of IndexedDB that makes use of several types of indexes common to many well-known server side search engines.
+In this paper, we describe a client-side search engine built on top of IndexedDB that makes use of several types of indexes common to many well-known server-side search engines.
 We compare the performance of different indexes on different types of full-text content and queries and find that....
@@
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+Today
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+\section{Background and Related Work}
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+There are a lot of cases where apps store a heavy amount of data in the browser. This study gives users ubiquitous access to data by allowing browser session migration \cite{lo2013imagen}
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+client-side profiles for personalized advertising, privacy concerns \cite{bilenko2011predictive}
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
+\cite{benson2010sync}
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+Search engines can be useful in the absence of connectivity on mobile phones. This system builds on a user study showing that revisitation is common.
+\cite{balasubramanian2012findall}
 
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
+Previous research has demonstrated that it is feasible to store a reverse index within IndexedDB
+\cite{lin:jscene} though it is much slower than using a server-side application such as Lucene.
 
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+\section{Lucy.js}
 
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
+\section{Index Implementations}
 
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
+\section{Evaluation}
 
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
+\section{Discussion}
 
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
+\section{Future Work}
 
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
+\section{Conclusion}
 
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.pdf} files to be
-displayable with \LaTeX (See Figures  and  ).  More details on each of these is found in the
-\textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\includegraphics{fly}
-\caption{A sample black and white graphic (.pdf format).}
-\label{fig:fly}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=1in,height=1in]{fly}
-\caption{A sample black and white graphic (.pdf format)
-that has been resized with the \texttt{includegraphics} command.}
-\label{fig:bigfly}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption (See Figure~\ref{fig:flies}). And don't forget to end the environment with {figure*}, not {figure}!
-
-\begin{figure*}
-\centering
-\includegraphics{flies}
-\caption{A sample black and white graphic (.pdf format)
-that needs to span two columns of text.}
-\label{fig:flies}
-\end{figure*}
-
-Note that only {\textbf{.pdf}} files were used; if you want to include
-{\textbf{.ps}} or {\textbf{.eps}} formats, you can use the
-\texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{align*}
-l&=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ] \\
-&= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{align*}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-% ensure same length columns on last page (might need two sub-sequent latex runs)
-\balance
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{abbrv}
-\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references).
-
-%APPENDIX is optional.
-% ****************** APPENDIX **************************************
-% Example of an appendix; typically would start on a new page
-%pagebreak
-
-\begin{appendix}
-You can use an appendix for optional proofs or details of your evaluation which are not absolutely necessary to the core understanding of your paper.
-
-\section{Final Thoughts on Good Layout}
-Please use readable font sizes in the figures and graphs.
-Avoid tempering with the correct border values, and the spacing (and format) of both text and captions of the PVLDB format (e.g.
-captions are bold).
-
-At the end, please check for an overall pleasant layout, e.g.
-by ensuring a readable and logical positioning of any floating figures and tables.
-Please also check for any line overflows, which are only allowed in extraordinary circumstances (such as wide formulas or URLs where a line wrap would be counterintuitive).
-
-Use the \texttt{balance} package together with a \texttt{\char'134 balance} command at the end of your document to ensure that the last page has balanced (i.e. same length) columns.
-
-\end{appendix}
+\bibliography{paper}
 

### 2014-12-06 code/trieindex.js
removed trie index duplicate results

@@ -129,7 +129,7 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
                 if (result) {
                     var update_obj = result;
                     var docIds = update_obj.docIds;
-                    if (!(docId in docIds))
+                    if (docIds.indexOf(docId) <= -1)
                         docIds.push(docId);
                     var insertion = trieindex.store.put(update_obj);
                     insertion.onerror = function(evt) {

### 2014-12-07 code/trieindex.js
added phrase search with trie index

@@ -20,63 +20,85 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
             text = reverse(text);
         }
         var trieIndex = this.index.index(this.indexName);
-        var docIds = [];
+        var docIdsDict = {};
 
         var ret = new IDBIndexRequest(this.objectStore, this.transaction);
         ret.result = [];
-        searchHelper(trieIndex, docIds, text, 0, ret, this.objectStore);
+        var tokenCount = Lucy.tokenize(text);
+        var finishCounter = {count: Object.keys(tokenCount.tokens).length};
+        for (token in tokenCount.tokens) {
+            var weight = tokenCount.tokens[token];
+            searchHelper(trieIndex, docIdsDict, token, weight, 0, ret, this.objectStore, finishCounter);
+        }
         return ret;
     };
 
-    function searchHelper(trieIndex, docIds, token, parentId, ret, objStore) {
-        console.log("token:", token, "parentId:", parentId);
-        if (token.length == 0)
-            ret.onsuccess();
+    function searchHelper(trieIndex, docIdsDict, token, weight, parentId, ret, objStore, finishCounter) {
+        if (token.length == 0) {
+            finishCounter.count--;
+            if (finishCounter.count == 0) {
+                populateResultText(docIdsDict, ret, objStore);
+            }
+        }
         var c = token.charAt(0);
         var request = trieIndex.get([parentId, c]);
-        (function(trieIndex, docIds, token, parentId, ret, objStore) {
+        (function(trieIndex, token, weight, parentId, ret, objStore, finishCounter) {        
             request.onsuccess = function(evt) {
                 if (evt.target.result) {
                     var result = evt.target.result;
                     if (token.length == 1) {
-                        console.log(result.docIds);
-                        docIds.push.apply(docIds, result.docIds);
-                        populateResultText(docIds, ret, objStore);
+                        finishCounter.count--;
+                        for (var i=0; i<result.docIds.length; i++) {
+                            docId = result.docIds[i];
+                            if (docId in docIdsDict) {
+                                docIdsDict[docId] += weight;
+                            } else {
+                                docIdsDict[docId] = weight;
+                            }
+                        }
+                        if (finishCounter.count == 0) {
+                            populateResultText(docIdsDict, ret, objStore);
+                        }
                     } else {
-                        searchHelper(trieIndex, docIds, token.substring(1), result.id, ret, objStore);
[…]

### 2014-12-07 code/trieindex.js
fixed trie index search with no results

@@ -16,18 +16,17 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
     // Perform prefix search
     // Return list of document objects with matches
     this.get = function(text) {
-        if (this.mode == "suffix") {
-            text = reverse(text);
-        }
         var trieIndex = this.index.index(this.indexName);
         var docIdsDict = {};
 
         var ret = new IDBIndexRequest(this.objectStore, this.transaction);
-        ret.result = [];
         var tokenCount = Lucy.tokenize(text);
         var finishCounter = {count: Object.keys(tokenCount.tokens).length};
         for (token in tokenCount.tokens) {
             var weight = tokenCount.tokens[token];
+            if (this.mode == "suffix") {
+                token = reverse(token);
+            }
             searchHelper(trieIndex, docIdsDict, token, weight, 0, ret, this.objectStore, finishCounter);
         }
         return ret;
@@ -79,6 +78,10 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
     function populateResultText(docIdsDict, ret, objStore) {
         var resultsDict = {};
         var finish_counter = { count:Object.keys(docIdsDict).length };
+        if (finish_counter.count == 0) {
+            ret.result = [];
+            ret.onsuccess();
+        }
         for (var docId in docIdsDict) {
             (function(docId) {
                 var requestText = objStore.get(docId);

### 2014-12-07 code/trieindex.js
fixed suffix search

@@ -111,40 +111,26 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
 
     // Tokenize and normalize data before insertion.
     this.insert = function(text, docId) {
-        var tokenCount = basictokenize(text);
-		for (var token in tokenCount) {
-			indexToken(trieIndex, docId, text);
-		}
+        //tokenize string
+        var tokens = Object.keys(Lucy.tokenize(text).tokens);
+        if (trieindex.mode == "suffix") {
+            for (var i=0; i<tokens.length; i++) {
+                tokens[i] = reverse(tokens[i]);
+            }
+        }
+        indexToken(trieindex, docId, tokens, 0);
     };
-
-    function basictokenize(s) {
-		s = s.toLowerCase();
-		var tokens = s.match(/\w+/g);
-		
-		var tokenCount = {};
-		for (var i=0; i<tokens.length; i++) {
-			if (tokens[i] in tokenCount) {
-				tokenCount[tokens[i]]++;
-			} else {
-				tokenCount[tokens[i]] = 1;
-			}
-		}
-		
-		return tokenCount;
-	}
 
     function indexToken(trieindex, docId, tokens, parentId, cursor) {
         if (tokens.length == 0) {
-            cursor.continue();
+            if (cursor)
+                cursor.continue();
             return;
         }
         token = tokens[0];
         if (token.length == 0) {
             tokens.shift();
             return indexToken(trieindex, docId, tokens, 0, cursor);
-        }
-        if (this.mode == "suffix") {
-            token = reverse(token);
         }
         var c = token.charAt(0);
         var getter = trieindex.index.get([parentId, c]);
@@ -212,8 +198,13 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
 				var docId = cursor.value[keyval];
 
                 //tokenize string
-				var tokenCount = basictokenize(text);
-                indexToken(trieindex, docId, Object.keys(tokenCount), 0, cursor);
+				var tokens = Object.keys(Lucy.tokenize(text).tokens);
+                if (trieindex.mode == "suffix") {
+                    for (var i=0; i<tokens.length; i++) {
+                        tokens[i] = reverse(tokens[i]);
+                    }
+                }
+                indexToken(trieindex, docId, tokens, 0, cursor);
 			} else {
 				console.log("All entries indexed.");        
 			}

### 2014-12-07 paper/paper.tex
introduction started

@@
 
-Today
+Most web applications today primarily store the bulk of their data on a web server or on the cloud, and the client-side part of the application queries the server when it needs to access data.
+In recent years, more applications have been built that rely more heavily on client-side storage, as browser standards have come to support client-side databases such as IndexedDB. 
+The ability to use local storage enables real-time interactivity on data-intensive and collaborative tasks by reducing the number of network round trips.
+These have been useful for many large and complex web applications such as massive multi-player games CITE that would have previously only existed as desktop applications.
+Issues around privacy and ownership of data have also given rise to a number of applications CITE that move most or all of data storage to the client~\cite{bilenko2011predictive}. 
+Finally, many popular smartphone browsers rely on wireless signals to transmit information, which is prone to failure in areas with poor signal, suggesting that applications that are entirely client-side or applications that retains some functionality during downtime could be useful~\cite{balasubramanian2012findall}.
+
+While much work has been done to make it easier to store and query data in the browser~\cite{benson2010sync}, currently there are few known ways to conduct full-text searching on the client side.
+Search engines are a very important component of a large number of applications and are necessary to make sense of many forms of data CITE.
+However, the current standard of IndexedDB, a key-value store, only supports simple operations such as put and get on set of keys and secondary indexes on object fields.
+There are no built-in capabilities to create indexes and then search on full-text content.
+
+In this paper, we introduce Lucy.js, a Javascript search engine that is an extension of the current IndexedDB API CITE, and we describe its design and implementation.
+It has been designed to be easy for anyone currently using IndexedDB to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communcation with IndexedDB.
+There are no dependencies on a server or on a network, so it can be harnessed offline.
+In our implementation, we created several types of indexes commonly used in well-known server-side search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and lossy search trees.
+We discuss how we managed to create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks.
+We compare their performance on different types of queries and with different sizes and types of datasets.
+We find that...
+
+Finally, we imagine the potential real-world use cases for a client-side search engine and how performance may be improved using this system.
+We implement a set of applications that would be reasonable in the real world and measure performance between fully client-side, fully server-side, and mixtures of both databases to respond to queries.
+We find that....
+This research demonstrates not only the feasibility of having search engines within the browser but also the potential for new applications and improved performance of existing applications through the additional capabilities provided by a client-side search engine.
 

### 2014-12-07 code/demo.js
Minor cosmetic changes

@@ -34,6 +34,7 @@ function resetDBVersion() {
 }
 
 $('#import-data').onclick = function () {
+	var me = this;
 	resetDBVersion();
 	
 	var loadingStatus = $('.loading-status');
@@ -46,6 +47,7 @@ $('#import-data').onclick = function () {
 	
 	importData.onsuccess = function () {
 		loadingStatus.textContent = '';
+		me.classList.add('done');
 	};	
 };
 
@@ -119,9 +121,10 @@ $('#build-suffix-index').onclick = function () {
 };
 
 
-$("#submit-search").onclick = function () {
+// TODO This needs to use the other types of indices as well.
+$(".search").onsubmit = function () {
 	
-	var searchQuery = $('#search-query').value;
+	var searchQuery = $('#search-query', this).value;
 	
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 	DBOpenRequest.onsuccess = function(evt) {
@@ -131,30 +134,34 @@ $("#submit-search").onclick = function () {
 		
 		var index = objectStore.index("text");
 		
-		//get returns a single entry (one with lowest key value)
+		// get returns a single entry (one with lowest key value)
 		var request = index.get(searchQuery);
-		console.log(request);
+		
 		request.onerror = function(evt) {
 			console.log(evt, searchQuery);
 		};
+		
 		request.onsuccess = function(evt) {
-			var searchResults = $('.search-results');
-			var result = "";
 			if (request.result.length == 0) {
-				result = "No results";
+				var result = "No results";
 			} else {
-				for (var i=0; i<request.result.length; i++) {
-					result = result + "<P>" + request.result[i].text + "</P>";
-				}
+				var result = request.result.reduce(function(prev, tweet) {
+					return prev + '<li><a href="http://twitter.com/' + tweet.username + '" class="user">' + tweet.username + '</a>: ' + tweet.text + 
+					       '<a href="http://twitter.com/' + tweet.username + '/' + 'status/' + tweet.id + '" class="date">' + tweet.date +
+					       "</a></li>";
+				}, '');
 			}
-			searchResults.innerHTML = result;
+			
+			$('.search-results ul').innerHTML = result;
 		};
 		
 		evt.target.result.close();
 	};
+	
 	DBOpenRequest.onerror = function(evt) {
 		console.log(evt);
 	};
+	
 	return false;
 };
 

### 2014-12-07 code/lucy.js

@@ -5,21 +5,12 @@
  */
 
 
-var SUPPORTED_LANGUAGES = ['english',
-						   'danish',
-						   'dutch',
-						   'finnish',
-						   'french',
-						   'german',
-						   'hungarian',
-						   'italian',
-						   'norwegian',
-						   'portuguese',
-						   'russian',
-						   'spanish',
-						   'swedish',
-						   'romanian',
-						   'turkish'];
+var SUPPORTED_LANGUAGES = [
+	'english',  'danish', 'dutch',
+	'finnish', 'french', 'german',
+	'hungarian', 'italian', 'norwegian',
+	'portuguese', 'russian', 'spanish',
+	'swedish', 'romanian', 'turkish'];
 
 
 
@@ -69,11 +60,7 @@ Lucy.tokenize = function(string) {
 };
 
 Lucy.isStopWord = function(word) {
-	if(Lucy.stopwords.indexOf(word) <= 0) {
-		return false;
-	} else {
-		return true;	
-	}
+	return Lucy.stopwords.indexOf(word) > -1;
 };
 
 Lucy.stemmer = function(language) {
@@ -87,16 +74,14 @@ Lucy.stemmer = function(language) {
 
 // convert dictionary to ordered list, reverse score
 Lucy.convert_dict = function(dict) {
-	function comparator(a, b) {
-		return b.score - a.score;
-	}
-	
 	var olist = [];
 	for (var item in dict) {
 		olist.push(dict[item]);
 	}
-	olist.sort(comparator);
-	return olist;
+	
+	return olist.sort(function (a, b) {
+		return b.score - a.score;
+	});
 };
 
 

### 2014-12-07 code/stopwords/english_stopwords.js

@@ -1,4 +1,3 @@
-
 Lucy.stopwords = [
 "",
 "a",

### 2014-12-07 code/trieindex.js

@@ -30,8 +30,11 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
 
     function searchHelper(trieIndex, docIds, token, parentId, ret, objStore) {
         console.log("token:", token, "parentId:", parentId);
-        if (token.length == 0)
+        
+        if (token.length == 0) {
             ret.onsuccess();
+        }
+        
         var c = token.charAt(0);
         var request = trieIndex.get([parentId, c]);
         (function(trieIndex, docIds, token, parentId, ret, objStore) {

### 2014-12-07 paper/paper.tex
small outlining

@@
 
-Most web applications today primarily store the bulk of their data on a web server or on the cloud, and the client-side part of the application queries the server when it needs to access data.
-In recent years, more applications have been built that rely more heavily on client-side storage, as browser standards have come to support client-side databases such as IndexedDB. 
+Most applications on the web store the bulk of their data on a backend web server or on the cloud, and the client side queries the server when it needs to access data.
+As web applications have become more interactive and responsive in the past several years, developers have built larger and more complex web servers to support them.
+However, this separation of data from the client introduces significant network effects that can often lead to noticable latency, as data may be retrieved from servers that are very far away.
+
+In recent years, more applications have been built that rely more heavily on client-side storage and offload data processing to web browsers.
+Today most commonly used browsers support the current HTML5 standards, which include a client-side persistent database called IndexedDB that is accessible via a JavaScript API.
 The ability to use local storage enables real-time interactivity on data-intensive and collaborative tasks by reducing the number of network round trips.
@@
 While much work has been done to make it easier to store and query data in the browser~\cite{benson2010sync}, currently there are few known ways to conduct full-text searching on the client side.
-Search engines are a very important component of a large number of applications and are necessary to make sense of many forms of data CITE.
-However, the current standard of IndexedDB, a key-value store, only supports simple operations such as put and get on set of keys and secondary indexes on object fields.
-There are no built-in capabilities to create indexes and then search on full-text content.
+Search engines are a very important component of a large number of applications and are necessary to make sense of many forms of full-text data such as chat or private messages, social media content, search queries, and webpage titles and content.
+As personalization has become more important for search engines, many designers of systems and architectures have highlighted the opportunities for client-side data computation~\cite{bharat2000searchpad,teevan2005personalizing}.
+Issues of privacy are also important when it comes to social applications and searching over personal data.
+New social applications such as CITE have been built that can operate without any servers, instead using peer-to-peer or Bluetooth connections.
+However, while it is possible to store full-text content on the client side, there is still no way to conduct full-text search on the client side at a reasonable speed, preventing most data computation necessary for a fully-featured search engine.
+The current standard of IndexedDB, a key-value store, only supports simple operations such as put and get on set of keys and secondary indexes on object fields.
+There are no built-in capabilities to create indexes for full-text content.
 
-In this paper, we introduce Lucy.js, a Javascript search engine that is an extension of the current IndexedDB API CITE, and we describe its design and implementation.
-It has been designed to be easy for anyone currently using IndexedDB to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communcation with IndexedDB.
-There are no dependencies on a server or on a network, so it can be harnessed offline.
-In our implementation, we created several types of indexes commonly used in well-known server-side search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and lossy search trees.
+In this paper, we introduce Lucy.js, a fully client-side JavaScript search engine that is an extension of the current IndexedDB API CITE.
+It has been designed to be easy for anyone currently using IndexedDB in their application to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communication.
+There are also no dependencies on a server or on a network, so it can be harnessed offline.
+In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and lossy search trees.
 We discuss how we managed to create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks.
@@
 
+There have been some 
+Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
+\cite{benson2010sync}
+
 There are a lot of cases where apps store a heavy amount of data in the browser. This study gives users ubiquitous access to data by allowing browser session migration \cite{lo2013imagen}
@@
 
-Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
-\cite{benson2010sync}
+previous use cases for client side search engine:
+client side application to capture search content to support web search
+\cite{bharat2000searchpad}
+
+personalization of search
+\cite{teevan2005personalizing}
+
+client side querying of search
+\cite{bozzon2010liquid}
 
@@
 
-\section{Lucy.js}
+\section{Architecture and Overview}
+
+\subsection{Extension of IndexedDB API}
+
+\subsection{Natural Language Processing}
+
+tokenizing
+
+Stopword removal
+
+Stemming
+
+different language capabilities
+
+\subsection{Scoring and Ranking}
+
+do we want to do tf-idf? postgres document normalization?
 
 \section{Index Implementations}
+
+We looked to many existing implementations of search engines and the indexes they used. Reverse indexes in Lucene. GiN and GiST indexes in PostgreSQL. Prefix and suffix tries from
+
+\subsection{Inverted Indexes}
+
+\subsection{Prefix and Suffix Tries}
+
+\subsection{Lossy Search Trees}
+
+\subsection{Performance and Comparison}
 

### 2014-12-08 code/lucy.js
Removed stemming from trie, minor refactoring in Lucy.tokenize()

@@ -23,40 +23,36 @@ function Lucy() {};
 
 Lucy.language = "english";
 
-Lucy.tokenize = function(string) { 
+Lucy.tokenize = function(string, options) {
+	options = options || {};
+	options.disableStemming = !!options.disableStemming;
+	
 	string = string.toLowerCase();
 	var tokens = string.match(/\w+/g);
 	
-	var tokenCount = {length: 0,
-					  tokens: {}};
-					  
-	var stopwordCount = {length: 0, 
-						 tokens: {}};
+	var tokenCount = {length: 0, tokens: {}};
+	var stopwordCount = {length: 0, tokens: {}};
+	
+	if (!options.disableStemming) {
+		var stemmer = Lucy.stemmer(Lucy.language);
+	}
 					  
 	for (var i=0; i<tokens.length; i++) {
-		if (!Lucy.isStopWord(tokens[i])) {
-			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
-			if (stem in tokenCount) {
-				tokenCount["tokens"][stem]++;
-			} else {
-				tokenCount["tokens"][stem] = 1;
-			}
-			tokenCount.length++;
-		} else {
-			var stem = Lucy.stemmer(Lucy.language)(tokens[i]);
-			if (stem in stopwordCount) {
-				stopwordCount["tokens"][stem]++;
-			} else {
-				stopwordCount["tokens"][stem] = 1;
-			}
-			stopwordCount.length++;
+		var stem = options.disableStemming? tokens[i] : stemmer(tokens[i]);
+		
+		var count = Lucy.isStopWord(tokens[i])? stopwordCount : tokenCount;
+		
+		if (stem in count) {
+			count.tokens[stem]++;
 		}
+		else {
+			count.tokens[stem] = 1;
+		}
+		
+		count.length++;
 	}
-	if (tokenCount.length == 0) {
-		return stopwordCount;
-	} else {
-		return tokenCount;
-	}
+	
+	return tokenCount.length == 0? stopwordCount : tokenCount;
 };
 
 Lucy.isStopWord = function(word) {
@@ -164,6 +160,7 @@ IDBIndexRequest.prototype = IDBRequest;
 			textIndex.transaction = transaction;
 			return textIndex;
     	}
+    	
         return _index.apply(this, arguments);
     };
     

### 2014-12-08 code/trieindex.js

@@ -20,7 +20,7 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         var docIdsDict = {};
 
         var ret = new IDBIndexRequest(this.objectStore, this.transaction);
-        var tokenCount = Lucy.tokenize(text);
+        var tokenCount = Lucy.tokenize(text, {disableStemming: true});
         var finishCounter = {count: Object.keys(tokenCount.tokens).length};
         for (token in tokenCount.tokens) {
             var weight = tokenCount.tokens[token];
@@ -113,12 +113,12 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
     // Tokenize and normalize data before insertion.
     this.insert = function(text, docId) {
         //tokenize string
-        var tokens = Object.keys(Lucy.tokenize(text).tokens);
+        var tokens = Object.keys(Lucy.tokenize(text, {disableStemming: true}).tokens);
+        
         if (trieindex.mode == "suffix") {
-            for (var i=0; i<tokens.length; i++) {
-                tokens[i] = reverse(tokens[i]);
-            }
+        	tokens = tokens.map(function (token) { return reverse(token); });
         }
+        
         indexToken(trieindex, docId, tokens, 0);
     };
 
@@ -199,7 +199,7 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
 				var docId = cursor.value[keyval];
 
                 //tokenize string
-				var tokens = Object.keys(Lucy.tokenize(text).tokens);
+				var tokens = Object.keys(Lucy.tokenize(text, {disableStemming: true}).tokens);
                 if (trieindex.mode == "suffix") {
                     for (var i=0; i<tokens.length; i++) {
                         tokens[i] = reverse(tokens[i]);

### 2014-12-08 paper/paper.tex
added more to related work

@@
 
-There have been some 
+Though previous HTML standards and browser capabilities were more limited, the idea of using of the client side for data storage and data computation has been around for many years.
+
+When it comes to search engines, specifically web search, prior work has found that 40\% to 60\% of search queries are re-finding queries~\cite{teevan2005personalizing}.
+This finding has lead to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,balasubramanian2012findall}.
+Prior work in this area has also highlighted how web search can often be a highly personal activity, and that web search should be personalized to the user to improve accuracy.
+Personal information can then be stored on the client side as this information is primarily useful for this particular client~\cite{teevan2005personalizing}.
+
+With the increased use of mobile phones in recent years, many web applications are now accessed via a smartphone.
+Here too, studies have shown that many queries to search engines are for re-finding.
+Using a client-side database is potentially even more impactful for a mobile phone browser because network connectivity is much less robust.
+Researchers have demonstrated this feasiblity by building a standalone search application for Android~\cite{balasubramanian2012findall}.
+However, this search engine is not usable with other browsing apps or other phones.
+Because we build an extension on top of IndexedDB, our search engine will be able to work for all browsers, desktop or mobile, that support IndexedDB, which is the majority of them.
+
 Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
@@
 
-previous use cases for client side search engine:
+Applications have also been built to take advantage of client-side storage
 client side application to capture search content to support web search
 \cite{bharat2000searchpad}
-
-personalization of search
-\cite{teevan2005personalizing}
-
-client side querying of search
-\cite{bozzon2010liquid}
-
-Search engines can be useful in the absence of connectivity on mobile phones. This system builds on a user study showing that revisitation is common.
-\cite{balasubramanian2012findall}
 

### 2014-12-08 code/demo.js
Lots of things (sorry for not breaking it down into smaller commits): - Fixed bug where multiple types of indices could not coexist on the same field - Fixed bug where indices were not working at all if the page was refreshed (this was such a pain and took so long to fix, I’m not sure it was worth it after all) - Fixed bug with token counts (they were always 1), - search now supports all three types of indices, based on the position of the % wildcard (before, after or not at all) - search now displays result count & duration - Minor refactoring here and there

@@ -1,10 +1,3 @@
-
-var databaseName = "LucyTest";
-var dataFile = "data/tweets.json";
-var currentDBVersion;
-
-loadDBVersion();
-
 function $(expr, con) {
 	return typeof expr === 'string'? (con || document).querySelector(expr) : expr;
 }
@@ -12,6 +5,22 @@ function $(expr, con) {
 function $$(expr, con) {
 	return Array.prototype.slice.call((con || document).querySelectorAll(expr));
 }
+
+
+var databaseName = "LucyTest";
+var dataFile = "data/tweets.json";
+var currentDBVersion;
+
+(function() {
+	// Init
+	loadDBVersion();
+	
+	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
+	
+	DBOpenRequest.onsuccess = function(evt) {
+		Lucy.init(evt.target.result);
+	};
+})();
 
 function loadDBVersion() {
 	var key = databaseName + "version";
@@ -64,18 +73,17 @@ $('#build-inv-index').onclick = function () {
 		var objectStore = transaction.objectStore("tweets");
 		
 		// field to create index on
-		objectStore.createIndex("tweet_text", "text", {type: "inverted", dbconn: evt.target.result});
+		objectStore.createIndex("tweets_text", "text", {type: "inverted", db: evt.target.result});
 	};
 	
 	DBOpenRequest.onsuccess = function(evt) {
 		evt.target.result.close();
 		console.log('Finished creating index.');
 	};
-
 };
 
 $('#build-prefix-index').onclick = function () {
-	var loadingStatus = $('.loading-status');
+	//var loadingStatus = $('.loading-status');
 	
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
@@ -87,7 +95,7 @@ $('#build-prefix-index').onclick = function () {
 		var objectStore = transaction.objectStore("tweets");
 		
 		// field to create index on
-		objectStore.createIndex("tweet_text_prefix", "text", {type: "prefix", dbconn: evt.target.result});
+		objectStore.createIndex("tweets_text_prefix", "text", {type: "prefix", db: evt.target.result});
 	};
 	
 	DBOpenRequest.onsuccess = function(evt) {
@@ -98,7 +106,7 @@ $('#build-prefix-index').onclick = function () {
 };
 
 $('#build-suffix-index').onclick = function () {
[…]

### 2014-12-08 code/invindex.js

@@ -5,16 +5,15 @@ Constructs an InvIndex for full-text search.
 
 
 var InvIndex = function(objStore, name, field, dbconn, language) {
-
-	this.objectStore = objStore;
-	this.name = name;
-	this.unique = false;
-	this.transaction = objStore.transaction;
+	var me = this;
 	
+	this.objectStore = objStore;
+	this.transaction = objStore && objStore.transaction;
+	
+	this.name = name;
 	this.language = language;
 	this.indexField = field;
-	
-	createIndex(this, dbconn);
+	this.unique = false;
 	
     // Perform index search for a phrase
     this.get = function(text) {
@@ -60,10 +59,12 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
 					
 					for (var j=0; j<result_ids.length; j++) {
 	    				var request_text = objStore.get(result_ids[j]);
+	    				
 		    			request_text.onerror = function(evt) {
 			    			console.log(evt, token);
 			    			ret.onerror();
 			    		};
+		    			
 		    			request_text.onsuccess = function(evt) {
 		    				finish_counter[curr_token]--;
 		    				var result = evt.srcElement.result;
@@ -102,56 +103,59 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
 		}
     };
 	
-	function indexToken(invindex, id, token, count) {	
-		var getter = invindex.index.get(token);
+	function indexToken(id, token, count) {	
+		var getter = me.index.get(token);
+		
 		getter.onsuccess = function(evt) {
 			var cursor = getter.result;
+			
 			if (cursor) {
 				var update_obj = getter.result;
 	  			var ids = update_obj.ids;
 	  			ids.push(id);
-				var insertion = invindex.index.put(update_obj);
+				var insertion = me.index.put(update_obj);
 				insertion.onerror = function(evt) {
 					console.log(evt, update_obj);
 				};
 			} else {
-				var ids = [];
-				ids.push(id);
-				var insert_obj = {"token": token, "ids": ids};
-				var insertion = invindex.index.add(insert_obj);
+				var insert_obj = {"token": token, "ids": [id]};
+				var insertion = me.index.add(insert_obj);
+
 				insertion.onerror = function(evt) {
 					console.log(evt, insert_obj);
 				};
 			}
   			
 		};
+		
 		getter.onerror = function(evt) {
 			console.log(evt, token);
 		};
 	}
     
-    function createIndex(invindex, dbconn) {
+    this.build = function() {
     	
[…]

### 2014-12-08 code/lucy.js

@@ -1,9 +1,7 @@
-
 /*
  * Lucy.js
  * 
  */
-
 
 var SUPPORTED_LANGUAGES = [
 	'english',  'danish', 'dutch',
@@ -12,14 +10,41 @@ var SUPPORTED_LANGUAGES = [
 	'portuguese', 'russian', 'spanish',
 	'swedish', 'romanian', 'turkish'];
 
-
-
 /*
  * Static class for general purpose natural language processing functions 
  * 
  */
 
-function Lucy() {};
+self.Lucy = {};
+
+Lucy.init = function(db) {
+	// Fetch all indices from database
+	this.indexCache = {};
+	
+	if (db.objectStoreNames.contains('__LucyIndices')) {
+		var cursor = db.transaction("__LucyIndices", "readonly").objectStore("__LucyIndices").openCursor();
+		
+		cursor.onsuccess = function (evt) {
+			var cursor = evt.target.result;
+			
+			if (cursor) {
+				var val = cursor.value;
+				
+				if (val.type == 'inverted') {
+					var index = new InvIndex(db.transaction(val.store).objectStore(val.store), val.name, val.path);
+				}
+				else {
+					var index = new TrieIndex(db.transaction(val.store).objectStore(val.store), val.name, val.path, val.type);
+				}
+
+				Lucy.indexCache[val.type] = Lucy.indexCache[val.type] || {};
+				Lucy.indexCache[val.type][val.name] = index;
+				
+				cursor.continue();
+			}
+		};
+	}
+}
 
 Lucy.language = "english";
 
@@ -42,17 +67,13 @@ Lucy.tokenize = function(string, options) {
 		
 		var count = Lucy.isStopWord(tokens[i])? stopwordCount : tokenCount;
 		
-		if (stem in count) {
-			count.tokens[stem]++;
-		}
-		else {
-			count.tokens[stem] = 1;
-		}
+		count.tokens[stem] = count.tokens[stem] || 0;
+		count.tokens[stem]++;
 		
 		count.length++;
 	}
 	
-	return tokenCount.length == 0? stopwordCount : tokenCount;
+	return tokenCount.length > 0? tokenCount: stopwordCount;
 };
 
 Lucy.isStopWord = function(word) {
@@ -103,41 +124,30 @@ IDBIndexRequest.prototype = IDBRequest;
 
 (function() {
 	
-    // Store mapping between index name and index objects
-    IDBObjectStore.prototype.textSearchIndexes = {};
-    
[…]

### 2014-12-08 code/trieindex.js

@@ -3,15 +3,16 @@
 Constructs a TrieIndex for prefix/suffix search.
 */
 
-var TrieIndex = function(objStore, name, field, mode, dbconn) {
+var TrieIndex = function(objStore, name, field, mode, db) {
+	var me = this;
 
 	this.objectStore = objStore;
-    this.transaction = objStore.transaction;
-	this.name = name;
+    this.transaction = objStore && objStore.transaction;
 	this.unique = false;
 	this.indexField = field;
     this.mode = mode;
-	createIndex(this, dbconn);
+    this.name = name;
+    this.indexName = this.name + "_index";
 	
     // Perform prefix search
     // Return list of document objects with matches
@@ -20,6 +21,7 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         var docIdsDict = {};
 
         var ret = new IDBIndexRequest(this.objectStore, this.transaction);
+
         var tokenCount = Lucy.tokenize(text, {disableStemming: true});
         var finishCounter = {count: Object.keys(tokenCount.tokens).length};
         for (token in tokenCount.tokens) {
@@ -50,11 +52,9 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
                         finishCounter.count--;
                         for (var i=0; i<result.docIds.length; i++) {
                             docId = result.docIds[i];
-                            if (docId in docIdsDict) {
-                                docIdsDict[docId] += weight;
-                            } else {
-                                docIdsDict[docId] = weight;
-                            }
+                            
+                            docIdsDict[docId] = docIdsDict[docId] || 0;
+                            docIdsDict[docId] += weight;
                         }
                         if (finishCounter.count == 0) {
                             populateResultText(docIdsDict, ret, objStore);
@@ -119,10 +119,10 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         	tokens = tokens.map(function (token) { return reverse(token); });
         }
         
-        indexToken(trieindex, docId, tokens, 0);
+        indexToken(docId, tokens, 0);
     };
 
-    function indexToken(trieindex, docId, tokens, parentId, cursor) {
+    function indexToken(docId, tokens, parentId, cursor) {
         if (tokens.length == 0) {
             if (cursor)
                 cursor.continue();
@@ -131,10 +131,10 @@ var TrieIndex = function(objStore, name, field, mode, dbconn) {
         token = tokens[0];
         if (token.length == 0) {
             tokens.shift();
-            return indexToken(trieindex, docId, tokens, 0, cursor);
[…]

### 2014-12-08 paper/paper.tex
finished related work

@@
 Though previous HTML standards and browser capabilities were more limited, the idea of using of the client side for data storage and data computation has been around for many years. 
+Some research has looked into building tools to support an architecture that includes client-side databases, including toolkits to synchronize data between the client and server~\cite{benson2010sync}.
+Another project facilitates ubiquitous access to client-side data across multiple browsers by enabling browser session migration from client to server to client~\cite{lo2013imagen}.
 
 When it comes to search engines, specifically web search, prior work has found that 40\% to 60\% of search queries are re-finding queries~\cite{teevan2005personalizing}.
-This finding has lead to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,balasubramanian2012findall}.
-Prior work in this area has also highlighted how web search can often be a highly personal activity, and that web search should be personalized to the user to improve accuracy.
+This finding has lead to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,bharat2000searchpad,balasubramanian2012findall}.
+Prior work in this area have also highlighted how web search can often be a highly personal activity, and that web search should be personalized to the user to improve accuracy.
 Personal information can then be stored on the client side as this information is primarily useful for this particular client~\cite{teevan2005personalizing}.
+Privacy is also a large concern for applications that collect personal data.
+Some applications have tackled personalized advertising using client-side stored profiles to mitigate this problem~\cite{bilenko2011predictive}.
 
@@
 
-Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
-\cite{benson2010sync}
-
-There are a lot of cases where apps store a heavy amount of data in the browser. This study gives users ubiquitous access to data by allowing browser session migration \cite{lo2013imagen}
-
-client-side profiles for personalized advertising, privacy concerns \cite{bilenko2011predictive}
-
-Applications have also been built to take advantage of client-side storage
-client side application to capture search content to support web search
-\cite{bharat2000searchpad}
-
-Previous research has demonstrated that it is feasible to store a reverse index within IndexedDB
-\cite{lin:jscene} though it is much slower than using a server-side application such as Lucene.
+There currently exists some prototypes of client-side search engines. Currently, all existing implementations only create inverted indexes.
+For instance, previous research has demonstrated that it is feasible to store an inverted index within IndexedDB~\cite{lin:jscene} though it is much slower than using a server-side application such as Lucene.
+We improve on these works by implementing different types of indexes for full-text search and comparing their performance. 
+Another existing implementation of a client side search engine called Lunr.js\footnote{http://www.lunrjs.com} store indexes in the client-side memory, which is infeasible for large amounts of data and also non-persistent.
+Instead, our system uses IndexedDB tables to hold indexes.
+Also, the YDN-DB module\footnote{https://github.com/yathit/ydn-db-fulltext} which wraps around the IndexedDB API, requires developers to migrate over to use the YDN system.
+Instead our system is simply an extension of IndexedDB.
+We also demonstrate several real-life situations that may call for a hybrid client and server database architecture for full-text search and measure their speed.
 

### 2014-12-08 paper/paper.tex
goals

@@
 
+In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give futher details of our implementation.
+
+\subsection{Goals}
+
+The two main goals of Lucy.js we aimed to achieve while implementing it were: (i) to build a search engine extension to IndexedDB that is easy to use and similar to the existing IndexedDB API, and (ii) to create different types of indexes that can all be used for full-text searching and find out which are more suited to which tasks and what the trade-offs are.
+We design Lucy.js so that it is easy as a developer to be able to specify which type of index to make on a field based on the type of queries that will most often be submitted.
+
+\subsection{IndexedDB}
+
 \subsection{Extension of IndexedDB API}
@@
 do we want to do tf-idf? postgres document normalization?
+
+\subsection{Implementation}
+
+We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.
 

### 2014-12-08 paper/paper.tex
introduction of indexeddb

@@
 
+Indexed Database (IndexedDB) is a Javascript API that was a Proposed Recommendation to the W3C on November 20th 2014~\cite{w3c} and is supported by most modern browsers on the desktop and phone, such as newer versions of Chrome, Firefox, Internet Exploror, Opera, and Safari.
+For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.
+On Chrome browsers, IndexedDB interfaces with a key-value store named LevelDB built at Google in C++ and inspired by BigTable.
+In LevelDB, keys and values are arbitrary byte arrays and data is stored in sorted order by key.
+It supports batch writing, put and get commands using the key, and forward and backward iteration over keys.
+
+The IndexedDB API supports transactions that rely on strict two-phase locking, so that read-only transactions can run concurrently but read-write transactions lock the specified object stores (similar to tables in a relational data store) for the entire duration of the transaction.
+Almost all transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function.
+Then a notification via a DOM event is triggered when the operation actually completes, and the type of event returned tells whether the operation succeeded or failed.
+
 \subsection{Extension of IndexedDB API}

### 2014-12-09 paper/paper.tex
create index info

@@
 
-The IndexedDB API supports transactions that rely on strict two-phase locking, so that read-only transactions can run concurrently but read-write transactions lock the specified object stores (similar to tables in a relational data store) for the entire duration of the transaction.
+The IndexedDB API supports transactions that rely on shared read and exclusive write locking.
+At transaction creation time, the code must specifies what kind of transaction it is (read-only, write-only, or read-write) and what object stores (similar to tables in a relational data store) it will access.
+Read-only transactions can run concurrently but transactions that write lock the specified object stores for the entire duration of the transaction.
 Almost all transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function.
@@
 
-\subsection{Extension of IndexedDB API}
+\subsection{Extending IndexedDB}
+
+\subsubsection{Creating a Full-Text Index}
+The interface to a database is maintained through an \texttt{IDBDatabase} object.
+To alter the schema of an IndexedDB database, for instance to create a new object store, the code must update the database version from its current version.
+This is not necessary when creating a normal secondary index on an existing object store.
+However, it will need to be updated when creating one of our new full-text indexes, as they are stored in IndexedDB as regular object stores.
+Thus the developer needs to persist locally the current version of the database and increment it before creating a new full-text index.
+Otherwise, the creation of a full-text index is very similar to that of a normal index.
+Given the object store \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, field\_name\right)$} function for creating full-text indexes.
+We additionally have the parameter of \texttt{type} which allows the developer to specify the type of full-text index they would like to build.
+The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}.
+If the developer does not specify a type, then a typical IndexedDB index would be created.
+Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.
+
+\begin{verbatim}
+var newDBVersion = incrementDBVersion();
+var DBRequest = indexedDB.open(databaseName,
+                               newDBVersion);
+DBRequest.onupgradeneeded = function(evt) {
+     var tn = evt.target.transaction;	
+     var objStore = tn.objectStore("tweets");
+     objStore.createIndex("tweets_text", "text", 
+                          {"type": "inverted"});
+};
+DBRequest.onsuccess = function(evt) {
+     evt.target.result.close();
+};
+\end{verbatim}
+
+\subsubsection{Searching over a Full-Text Index}
 

### 2014-12-09 paper/paper.tex
added some sections on prefix and suffix tries to paper

--- 2014-12-08 paper/paper.tex
@@
 
+Trie indexes are used to perform prefix and suffix searches on text data.
+While prefix/suffix search is often used for pattern-matching that matches the entire original text, the trie index in Lucy.js uses tokenization to perform finer-grained searches on multi-word text inputs (like tweet data).
+Phrase search with tries is also supported.
+This allows users to search by multiple prefixes or suffixes at a time, and get results with the most matches.
+
+Prefix and suffix tries are implemented using the same design.
+The only difference between them is that words are reversed before insertion into suffix tries, and similarly, search terms are reversed before they are looked up in the suffix trie.
+Otherwise, they rely on the same implementation as described below.
+
+A trie index in Lucy.js (prefix or suffix trie) is represented by two underlying entities in IndexedDB: an objects store to save nodes in the trie, and an index on that object store to make trie traversal faster.
+A reference to the input object store to be indexed -- which contains the full-text to be searched -- is also saved.
+
+\paragraph{Trie Node Object Store}
+Each entry in the object store represents a different node in the trie. The structure of entries in the object store is as follows:
+\begin{center}
+node\_id: \{ parent\_id: a, char: b, doc\_ids: [x,y,z] \}
+\end{center}
+The key to the object store is the node\_id, and the corresponding value object has three attributes: parent\_id, char, and doc\_ids.
+The parent\_id attribute is the node id of the parent node in the trie, and the char attribute is the character value for the trie node.
+The final attribute is doc\_ids, which is a list of keys into the input text object store.
+The keys in this list are like foreign keys that allow the trie index to retrieve the actual text from the input object store when answering queries.
+Each path -- and therefore each node -- in the trie represents a unique prefix/suffix.
+The doc\_ids for a node contains the ids of all documents with that given prefix/suffix.
+Inserting a word from a given document therefore involves appending that document's id into the doc\_ids of each node along the path corresponding to the word.
+
+\paragraph{Trie Node Index}
+While the structure of the trie node object store optimizes lookups by node id, this is not particularly useful for trie traversal.
+When traversing down a trie, we would instead like to look up nodes by both their character value and their parent id.
+It would have been possible to change the design of the trie object store so that each node stored a list of children node ids instead of a single parent id.
+However, this approach requires each node to store more information, since a list of children ids is saved per node instead of a single parent id.
+Additionally, we would then need to iterate over this list of children ids in order to find a particular child node with a given character value.
+With the current object store structure, we can optimize lookups by parent\_id and char by building an index on both these attributes.
+Overall, the trie index is backed by an object store for node storage and an index on that object store with a compound key of both parent\_id and char.
+
+\paragraph{Lookups}
+Lookups in the trie index are performed by traversing the trie downward, character by character in the search pattern.
+Partial matches are not accepted; the entire prefix (or suffix) must be present in the trie or no results are returned.
+If the entire pattern is found, the doc\_ids are extracted from the trie node corresponding to the last letter of the search pattern.
+These ids are used to key into the input text object store and retrieve the original text data.
+
+\paragraph{Tokenization}
+Unlike with the inverted index, words are not stemmed before insertion or lookups.
+This is especially important for suffix tries because many suffix searches will not succeed due to stemming of the original text being searched.
+Tokenization is still used to break up input into words; it is used during both insertion (so that prefix/suffix searches can be done by word), and during lookups (making phrase search possible).
+Phrase search in tries involves performing prefix/suffix search on each word in the input search phrase, and ranking results by the number of matching patterns in the original text.
+
+\paragraph{Synchronization}
+Due to the manner in which letters in a word need to be inserted sequentially in a trie, much of IndexedDB's built-in asynchronous behavior cannot be used to improve performance.
+In fact, the parallelization that IndexedDB introduces can cause serious problems due to collisions between different threads.
+When testing on tweet data, even inserting two tweets concurrently posed problems because the tweets contained words that started with the same letter.
+As a result, concurrently-running threads would try to insert duplicate elements, resulting in IndexedDB transaction errors.
+To avoid this, text is added sequentially to the trie index during creation, and insertion of words occurs sequentially by letter.
+While this avoids transaction errors, it greatly increases index creation time.
+
 \subsection{Lossy Search Trees}

### 2014-12-09 paper/paper.tex
Small paper edits

@@
 
-Most applications on the web store the bulk of their data on a backend web server or on the cloud, and the client side queries the server when it needs to access data.
+Most web applications store the bulk of their data on a backend web server or on the cloud, and the client side queries the server when it needs to access data.
 As web applications have become more interactive and responsive in the past several years, developers have built larger and more complex web servers to support them.
-However, this separation of data from the client introduces significant network effects that can often lead to noticable latency, as data may be retrieved from servers that are very far away.
+However, this separation of data from the client introduces significant network effects that can often lead to noticeable latency, as data may be retrieved from servers that are very far away.
 
-In recent years, more applications have been built that rely more heavily on client-side storage and offload data processing to web browsers.
-Today most commonly used browsers support the current HTML5 standards, which include a client-side persistent database called IndexedDB that is accessible via a JavaScript API.
-The ability to use local storage enables real-time interactivity on data-intensive and collaborative tasks by reducing the number of network round trips.
+In recent years, more applications are being built that heavily rely on client-side storage and offload data processing to web browsers.
+Today most commonly used browsers support the current HTML5 standards, which include a persistent client-side DBMS with the name IndexedDB that is accessible via a set of JavaScript APIs.
+The ability to use local storage enables real-time interactivity on data-intensive and collaborative tasks by reducing the number of network roundtrips.
 These have been useful for many large and complex web applications such as massive multi-player games CITE that would have previously only existed as desktop applications.
@@
 There are also no dependencies on a server or on a network, so it can be harnessed offline.
-In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and lossy search trees.
+In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene CITE and within PostgreSQL CITE, including inverted indexes, prefix and suffix tries, and lossy search trees.
 We discuss how we managed to create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks.
@@
 
-There currently exists some prototypes of client-side search engines. Currently, all existing implementations only create inverted indexes.
+Some prototypes of client-side search engines have previously been built CITE. Currently, all existing implementations only create basic inverted indexes.
 For instance, previous research has demonstrated that it is feasible to store an inverted index within IndexedDB~\cite{lin:jscene} though it is much slower than using a server-side application such as Lucene.
 We improve on these works by implementing different types of indexes for full-text search and comparing their performance. 
-Another existing implementation of a client side search engine called Lunr.js\footnote{http://www.lunrjs.com} store indexes in the client-side memory, which is infeasible for large amounts of data and also non-persistent.
-Instead, our system uses IndexedDB tables to hold indexes.
+Another existing implementation of a client side search engine called Lunr.js\footnote{http://www.lunrjs.com} stores indexes in the client-side memory, which is infeasible for large amounts of data and also non-persistent.
+Instead, our system uses IndexedDB object stores to hold indexes.
 Also, the YDN-DB module\footnote{https://github.com/yathit/ydn-db-fulltext} which wraps around the IndexedDB API, requires developers to migrate over to use the YDN system.
@@
 
-In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give futher details of our implementation.
+In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give further details of our implementation.
 
@@
 
-Indexed Database (IndexedDB) is a Javascript API that was a Proposed Recommendation to the W3C on November 20th 2014~\cite{w3c} and is supported by most modern browsers on the desktop and phone, such as newer versions of Chrome, Firefox, Internet Exploror, Opera, and Safari.
+Indexed Database (IndexedDB) is a collection of Javascript APIs and is an official W3C specification (Proposed Recommendation stage) ~\cite{w3c}.
+It is supported by almost every modern browser, both on desktop and mobile devices.
+Chrome, Firefox, Internet Explorer, Opera, and Safari are only some of the browsers that have added support for IndexedDB in their modern versions.
 For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.
@@
 Read-only transactions can run concurrently but transactions that write lock the specified object stores for the entire duration of the transaction.
-Almost all transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function.
+All transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function.
 Then a notification via a DOM event is triggered when the operation actually completes, and the type of event returned tells whether the operation succeeded or failed.

### 2014-12-09 paper/paper.tex
section on extending IndexedDB done

--- 2014-12-09 paper/paper.tex
@@
 Otherwise, the creation of a full-text index is very similar to that of a normal index.
-Given the object store \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, field\_name\right)$} function for creating full-text indexes.
-We additionally have the parameter of \texttt{type} which allows the developer to specify the type of full-text index they would like to build.
+Given the object store \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, key\_path\right)$} function for creating full-text indexes.
+We add an additional optional parameter of \texttt{type} which allows the developer to specify a type of full-text index they would like to build.
 The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}.
 If the developer does not specify a type, then a typical IndexedDB index would be created.
-Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.
+Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on an object field \texttt{text} in an object store of Twitter tweets.
 
@@
 \subsubsection{Searching over a Full-Text Index}
+
+There are two ways to retrieve items given an \texttt{IDBIndex} object using the IndexedDB API. 
+The first is to use a \texttt{get} function, which returns an \texttt{IDBRequest} object with the \texttt{result} field populated with the value in the object store that corresponds to the given index key.
+The second is to call \texttt{openCursor}, which returns an \texttt{IDBCursor} object that can be iterated over.
+One can pass in a range of keys instead of just one key to either function, using the \texttt{IDBKeyRange} interface.
+
+In our case, a given search query may return many results that have different levels of relevance to the query.
+For this reason, each object returned has an addition field called \texttt{score}, which has a relevancy value with higher being more relevant.
+In the next section, we go into more detail into how the score is calculated for different types of search queries.
+By default we return all relevant (\texttt{score} $>$ 0) objects in reverse order of \texttt{score}.
+
+However, a query can return a large number of items with low relevancy if the query contains a term that is common.
+In IndexedDB, there is an interface called \texttt{IDBKeyRange} that is used for when a user wishes to query a range of keys.
+We extend this interface to include ranges of \texttt{score} values, so that users can set a cutoff or range of the relevancy score.
+This feature is also one that is available in PostgreSQL as **********.
+
+In the follow code snippet, we provide an example of a \texttt{get} function on the inverted index created in the last section.
+The object returned is an \texttt{IDBIndexRequest} object, which mimics the behavior of \texttt{IDBRequest}.
+
+\begin{verbatim}
+var index = objStore.index("tweets_text");
+var request = index.get("follow friday");
+request.onsuccess = function(evt) {
+     console.log(request.result);
+};
+\end{verbatim}
+
+The following is an example of generating a cursor over a query on a full-text index.
+The cursor can be made to play forwards or backwards over the intended order using the parameter value of ``next" or ``prev".
+
+\begin{verbatim}
+var index = objStore.index("tweets_text");
+var request = index.openCursor("#nowplaying", "next");
+request.onsuccess = function(evt) {
+     var cursor = event.target.result;
+     if(cursor) {
+          console.log("Text: " + cursor.value.text +
+                      "Score:" cursor.value.score);
+          cursor.continue();
+     }
+};
+\end{verbatim}
+
+Other functions of \texttt{IDBIndex} that are supported include \texttt{getKey}, which returns the primary keys on the original object store that are the result of a query, and \texttt{count}, which returns the number of relevant objects.
 
@@
 
-Trie indexes are used to perform prefix and suffix searches on text data.
-While prefix/suffix search is often used for pattern-matching that matches the entire original text, the trie index in Lucy.js uses tokenization to perform finer-grained searches on multi-word text inputs (like tweet data).
-Phrase search with tries is also supported.
-This allows users to search by multiple prefixes or suffixes at a time, and get results with the most matches.
-
-Prefix and suffix tries are implemented using the same design.
-The only difference between them is that words are reversed before insertion into suffix tries, and similarly, search terms are reversed before they are looked up in the suffix trie.
-Otherwise, they rely on the same implementation as described below.
-
-A trie index in Lucy.js (prefix or suffix trie) is represented by two underlying entities in IndexedDB: an objects store to save nodes in the trie, and an index on that object store to make trie traversal faster.
-A reference to the input object store to be indexed -- which contains the full-text to be searched -- is also saved.
-
-\paragraph{Trie Node Object Store}
-Each entry in the object store represents a different node in the trie. The structure of entries in the object store is as follows:
-\begin{center}
-node\_id: \{ parent\_id: a, char: b, doc\_ids: [x,y,z] \}
-\end{center}
-The key to the object store is the node\_id, and the corresponding value object has three attributes: parent\_id, char, and doc\_ids.
-The parent\_id attribute is the node id of the parent node in the trie, and the char attribute is the character value for the trie node.
-The final attribute is doc\_ids, which is a list of keys into the input text object store.
-The keys in this list are like foreign keys that allow the trie index to retrieve the actual text from the input object store when answering queries.
-Each path -- and therefore each node -- in the trie represents a unique prefix/suffix.
-The doc\_ids for a node contains the ids of all documents with that given prefix/suffix.
-Inserting a word from a given document therefore involves appending that document's id into the doc\_ids of each node along the path corresponding to the word.
-
-\paragraph{Trie Node Index}
-While the structure of the trie node object store optimizes lookups by node id, this is not particularly useful for trie traversal.
-When traversing down a trie, we would instead like to look up nodes by both their character value and their parent id.
-It would have been possible to change the design of the trie object store so that each node stored a list of children node ids instead of a single parent id.
-However, this approach requires each node to store more information, since a list of children ids is saved per node instead of a single parent id.
-Additionally, we would then need to iterate over this list of children ids in order to find a particular child node with a given character value.
-With the current object store structure, we can optimize lookups by parent\_id and char by building an index on both these attributes.
-Overall, the trie index is backed by an object store for node storage and an index on that object store with a compound key of both parent\_id and char.
-
-\paragraph{Lookups}
-Lookups in the trie index are performed by traversing the trie downward, character by character in the search pattern.
-Partial matches are not accepted; the entire prefix (or suffix) must be present in the trie or no results are returned.
-If the entire pattern is found, the doc\_ids are extracted from the trie node corresponding to the last letter of the search pattern.
-These ids are used to key into the input text object store and retrieve the original text data.
-
-\paragraph{Tokenization}
-Unlike with the inverted index, words are not stemmed before insertion or lookups.
-This is especially important for suffix tries because many suffix searches will not succeed due to stemming of the original text being searched.
-Tokenization is still used to break up input into words; it is used during both insertion (so that prefix/suffix searches can be done by word), and during lookups (making phrase search possible).
-Phrase search in tries involves performing prefix/suffix search on each word in the input search phrase, and ranking results by the number of matching patterns in the original text.
-
-\paragraph{Synchronization}
-Due to the manner in which letters in a word need to be inserted sequentially in a trie, much of IndexedDB's built-in asynchronous behavior cannot be used to improve performance.
-In fact, the parallelization that IndexedDB introduces can cause serious problems due to collisions between different threads.
-When testing on tweet data, even inserting two tweets concurrently posed problems because the tweets contained words that started with the same letter.
-As a result, concurrently-running threads would try to insert duplicate elements, resulting in IndexedDB transaction errors.
-To avoid this, text is added sequentially to the trie index during creation, and insertion of words occurs sequentially by letter.
-While this avoids transaction errors, it greatly increases index creation time.
-
 \subsection{Lossy Search Trees}

### 2014-12-09 paper/paper.tex
natural language processing

@@
 The following is an example of generating a cursor over a query on a full-text index.
-The cursor can be made to play forwards or backwards over the intended order using the parameter value of ``next" or ``prev".
+The cursor can be made to play forwards or backwards over the intended order using the parameter value of \texttt{next} or \texttt{prev}.
 
@@
 
-tokenizing
+Queries to our full-text search engine can be words or phrases.
+In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of a word to search for parts of words.
+At this time, we do not support full regular expressions nor exact phrase matches.
 
-Stopword removal
+The processing that we conduct on queries and on the full text is standard for most search engines such as Lucene, MySQL, and PostgreSQL.
+The first thing we do is tokenize the text into contiguous strings of alphabetic characters, which are generally words.
+We convert the entire text to lower case and then remove stopwords from the bag of words.
+The stopword list we employ is taken from MySQL's full-text stopword list\footnote{http://dev.mysql.com/doc/refman/5.1/en/fulltext-stopwords.html}.
+The reason we remove stopwords is because these words are present in much of natural language and including them could grow the result set to be very large but not return very relevant results.
 
-Stemming
+Next, we employ stemming on each individual word using an open source JavaScript implementation of a Snowball stemmer\footnote{https://github.com/fortnightlabs/snowball-js}. 
+Stemming can be a useful part of search engines because a user may be interested in text containing a word even if the word is pluralized or has some other form of suffix.
 
-different language capabilities
+Sometimes however these processing techniques are not desired, given a particular type of text, type of query, or type of index used.
+For instance, stemming does not make sense when we are building a suffix trie.
+Our system allows the developer to pass optional parameters to disable stopword removal or stemming when desired.
+It is also possible for developers to edit the stopwords list for a list that is domain-specific or otherwise more preferred.
+
+Finally, our system offers flexible support for other languages.
+The stemmer that we employ has support for 14 common languages in addition to English.
+When creating an index, a developer can specify as an optional parameter the language the full-text strings are in.
+Then, when it comes time, the stemmer will choose the given language to use for stemming.
+Also, the stopword list is included as a separate JavaScript file.
+To swap out one language's stopwords with another's, one only needs to replace the JavaScript file imported in the HTML page.
+This prevents web pages from having to load stopword lists of all supported languages when using Lucy.js.
 

### 2014-12-09 paper/paper.tex
initial stuff for ranking

@@
 Queries to our full-text search engine can be words or phrases.
-In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of a word to search for parts of words.
+In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of any word to search for parts of words.
 At this time, we do not support full regular expressions nor exact phrase matches.
@@
 
-\subsection{Scoring and Ranking}
+\subsection{Scoring and Ranking Results}
 
-do we want to do tf-idf? postgres document normalization?
+There are many ways to score and rank results of a search query.
+Some techniques, such as \textit{tf-idf}, require precalculated document metadata.
+Others require knowning positional information about a word within a document.
+We define several built-in ranking functions derived from PostgreSQL's built-in \texttt{ts\_rank} and \texttt{ts\_rank\_cd} functions that take in a \texttt{normalization} option, with integer inputs providing different types of document normalizations\footnote{http://www.postgresql.org/docs/8.3/static/textsearch-controls.html}.
+The PostgreSQL's functions take into account how often the query terms appear in the document as well as how close together the terms are in the document.
+However, it is possible for a developer to implement their own ranking function and replace ours with theirs within Lucy.js.
 

### 2014-12-09 code/demo.js
More precise duration, some small refactoring of the trie code here and there (currently working on that to improve performance & implement shrinkage, so more commits on the way)

@@ -6,6 +6,9 @@ function $$(expr, con) {
 	return Array.prototype.slice.call((con || document).querySelectorAll(expr));
 }
 
+function now() {
+	return self.performance? performance.now() : Date.now();
+}
 
 var databaseName = "LucyTest";
 var dataFile = "data/tweets.json";
@@ -61,8 +64,6 @@ $('#import-data').onclick = function () {
 };
 
 $('#build-inv-index').onclick = function () {
-	var loadingStatus = $('.loading-status');
-	
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
@@ -83,8 +84,6 @@ $('#build-inv-index').onclick = function () {
 };
 
 $('#build-prefix-index').onclick = function () {
-	//var loadingStatus = $('.loading-status');
-	
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
@@ -102,12 +101,13 @@ $('#build-prefix-index').onclick = function () {
 		evt.target.result.close();
 		console.log('Finished creating index.');
 	};
-
+	
+	DBOpenRequest.onblocked = function (evt) {
+		console.error('Database is blocked yo!');
+	}
 };
 
 $('#build-suffix-index').onclick = function () {
-	//var loadingStatus = $('.loading-status');
-	
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
@@ -130,7 +130,7 @@ $('#build-suffix-index').onclick = function () {
 };
 
 function search(db, query, objectStore) {
-	var startTime = Date.now();
+	var startTime = now();
 	var type = "inverted";
 	var indexName = objectStore + '_text';
 	
@@ -159,7 +159,7 @@ function search(db, query, objectStore) {
 	
 	request.onsuccess = function(evt) {
 		$('.search-results .count').textContent = request.result.length + ' ';
-		$('.search-results .duration').textContent = (Date.now() - startTime) + 'ms';
+		$('.search-results .duration').textContent = (now() - startTime).toFixed(2) + 'ms';
 		
 		if (request.result.length == 0) {
 			var result = "No results";

### 2014-12-09 code/idbport.js

@@ -15,7 +15,13 @@ indexedDB.import = function (database, src, callback) {
 		if (xhr.readyState == 4 && xhr.status < 400) {
 			ret.onstatusupdate("Loaded JSON file");
 			
-			var data = JSON.parse(xhr.responseText);
+			try {
+				var data = JSON.parse(xhr.responseText);
+			}
+			catch (e) {
+				console.error(e);
+				console.log('Data: ', xhr.responseText);
+			}
 			
 			ret.onstatusupdate("Parsed JSON file");
 			

### 2014-12-09 code/invindex.js

@@ -4,7 +4,7 @@ Constructs an InvIndex for full-text search.
 */
 
 
-var InvIndex = function(objStore, name, field, dbconn, language) {
+var InvIndex = function(objStore, name, field, language) {
 	var me = this;
 	
 	this.objectStore = objStore;
@@ -133,10 +133,10 @@ var InvIndex = function(objStore, name, field, dbconn, language) {
 		};
 	}
     
-    this.build = function() {
+    this.build = function(db) {
     	
     	//create inverted index for field
-    	this.index = dbconn.createObjectStore(name, { keyPath: "token" });
+    	this.index = db.createObjectStore(name, { keyPath: "token", ifExists: "replace" });
     	console.log("Created Index object store");
 
     	var keyval = this.objectStore.keyPath;

### 2014-12-09 code/lucy.js

@@ -42,6 +42,9 @@ Lucy.init = function(db) {
 				
 				cursor.continue();
 			}
+			else {
+				db.close();
+			}
 		};
 	}
 }
@@ -116,6 +119,17 @@ var IDBIndexRequest = function(objStore, transaction) {
 
 IDBIndexRequest.prototype = IDBRequest;
 
+Lucy.helpers = {
+	createObjectStoreIfNotExists: function (transaction, name, optionalParameters) {
+		var db = transaction.db;
+		
+		if (db.objectStoreNames.contains(name)) {
+			return transaction.objectStore(name);
+		}
+		
+		return db.createObjectStore(name, optionalParameters);
+	}
+};
 
 
 /*
@@ -123,140 +137,157 @@ IDBIndexRequest.prototype = IDBRequest;
  */
 
 (function() {
+
+/**
+ * Helper method: Create an object store or replace the existing one if it exists
+ */
+var _createObjectStore = IDBDatabase.prototype.createObjectStore;
+IDBDatabase.prototype.createObjectStore = function(name, optionalParameters) {
+	if (this.objectStoreNames.contains(name)) {
+		// Already exists
+		if (optionalParameters.ifExists == "replace") { // replace
+			// OS already exists, drop it
+			this.deleteObjectStore(name);
+		}
+		else if (optionalParameters.ifExists == "silent") {
+			return null;
+		}
+	}
 	
-    
-    /*
-    Intercept put  
-    Raise DOMException with type DataError if key invalid
-    */
-    var _put = IDBObjectStore.prototype.put;
-    IDBObjectStore.prototype.put = function(item, optionalKey) {
-        return _put.apply(this, arguments);
-    };
+	return _createObjectStore.apply(this, arguments);
+}
 
-    /*
-    Intercept add  
-    Raise DOMException with type DataError if key invalid
-    */
-    var _add = IDBObjectStore.prototype.add;
-    IDBObjectStore.prototype.add = function(item, optionalKey) {
-        return _add.apply(this, arguments);
-    };
+/*
+Intercept put  
+Raise DOMException with type DataError if key invalid
+*/
+var _put = IDBObjectStore.prototype.put;
+IDBObjectStore.prototype.put = function(item, optionalKey) {
+	// TODO
+    return _put.apply(this, arguments);
+};
 
-    /*
-    Intercept delete
-    Raise DOMException with type DataError if key invalid
-    */
-    var _delete = IDBObjectStore.prototype.delete;
[…]

### 2014-12-09 code/trieindex.js

@@ -3,11 +3,11 @@
 Constructs a TrieIndex for prefix/suffix search.
 */
 
-var TrieIndex = function(objStore, name, field, mode, db) {
+var TrieIndex = function(objStore, name, field, mode) {
 	var me = this;
 
-	this.objectStore = objStore;
-    this.transaction = objStore && objStore.transaction;
+	this.objectStore = objStore; // overriden before index is used
+    this.transaction = objStore && objStore.transaction; // overriden before index is used
 	this.unique = false;
 	this.indexField = field;
     this.mode = mode;
@@ -24,72 +24,87 @@ var TrieIndex = function(objStore, name, field, mode, db) {
 
         var tokenCount = Lucy.tokenize(text, {disableStemming: true});
         var finishCounter = {count: Object.keys(tokenCount.tokens).length};
+        
         for (token in tokenCount.tokens) {
             var weight = tokenCount.tokens[token];
+            
             if (this.mode == "suffix") {
                 token = reverse(token);
             }
+            
             searchHelper(trieIndex, docIdsDict, token, weight, 0, ret, this.objectStore, finishCounter);
         }
+        
         return ret;
     };
 
-    function searchHelper(trieIndex, docIdsDict, token, weight, parentId, ret, objStore, finishCounter) {
+    function searchHelper(metaIndex, docIdsDict, token, weight, parentId, ret, objStore, finishCounter) {
         if (token.length == 0) {
             finishCounter.count--;
+            
             if (finishCounter.count == 0) {
                 populateResultText(docIdsDict, ret, objStore);
             }
         }
 
         var c = token.charAt(0);
-        var request = trieIndex.get([parentId, c]);
-        (function(trieIndex, token, weight, parentId, ret, objStore, finishCounter) {        
+        var request = metaIndex.get([parentId, c]);
+        
+        (function(metaIndex, token, weight, parentId, ret, objStore, finishCounter) {        
             request.onsuccess = function(evt) {
                 if (evt.target.result) {
                     var result = evt.target.result;
+                    
                     if (token.length == 1) {
                         finishCounter.count--;
+                        
                         for (var i=0; i<result.docIds.length; i++) {
                             docId = result.docIds[i];
                             
                             docIdsDict[docId] = docIdsDict[docId] || 0;
                             docIdsDict[docId] += weight;
                         }
+                        
                         if (finishCounter.count == 0) {
                             populateResultText(docIdsDict, ret, objStore);
                         }
                     } else {
[…]

### 2014-12-09 code/trieindex.js
path shortening for trie index

@@ -3,7 +3,7 @@
 Constructs a TrieIndex for prefix/suffix search.
 */
 
-var TrieIndex = function(objStore, name, field, mode) {
+var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 	var me = this;
 
 	this.objectStore = objStore; // overriden before index is used
@@ -13,6 +13,14 @@ var TrieIndex = function(objStore, name, field, mode) {
     this.mode = mode;
     this.name = name;
     this.indexName = this.name + "_index";
+    this.maxDepth = -1;
+    if (maxDepth) {
+        this.maxDepth = maxDepth;
+    }
+
+    function hasMaxDepth() {
+        return me.maxDepth != -1;
+    }
 	
     // Perform prefix search
     // Return list of document objects with matches
@@ -49,12 +57,10 @@ var TrieIndex = function(objStore, name, field, mode) {
 
         var c = token.charAt(0);
         var request = metaIndex.get([parentId, c]);
-        
         (function(metaIndex, token, weight, parentId, ret, objStore, finishCounter) {        
             request.onsuccess = function(evt) {
                 if (evt.target.result) {
                     var result = evt.target.result;
-                    
                     if (token.length == 1) {
                         finishCounter.count--;
                         
@@ -65,6 +71,22 @@ var TrieIndex = function(objStore, name, field, mode) {
                             docIdsDict[docId] += weight;
                         }
                         
+                        if (finishCounter.count == 0) {
+                            populateResultText(docIdsDict, ret, objStore);
+                        }
+                    } else if (Object.keys(result.wordMap).length != 0) { // reached maxDepth
+                        finishCounter.count--;
+                        var rem = token.substring(1);
+                        for (var key in result.wordMap) {
+                            if (key.indexOf(rem) == 0) {
+                                var matches = result.wordMap[key];
+                                for (var i=0; i < matches.length; i++) {
+                                    var m = matches[i];
+                                    docIdsDict[m] = docIdsDict[docId] || 0;
+                                    docIdsDict[m] += weight;
+                                }
+                            }
+                        }
                         if (finishCounter.count == 0) {
                             populateResultText(docIdsDict, ret, objStore);
                         }
@@ -134,10 +156,10 @@ var TrieIndex = function(objStore, name, field, mode) {
         	tokens = tokens.map(function (token) { return reverse(token); });
         }
         
-        indexToken(docId, tokens, 0);
[…]

### 2014-12-10 code/lucy.js
add normalization for doc length and unique words

@@ -64,7 +64,7 @@ Lucy.tokenize = function(string, options) {
 	if (!options.disableStemming) {
 		var stemmer = Lucy.stemmer(Lucy.language);
 	}
-					  
+
 	for (var i=0; i<tokens.length; i++) {
 		var stem = options.disableStemming? tokens[i] : stemmer(tokens[i]);
 		
@@ -78,6 +78,50 @@ Lucy.tokenize = function(string, options) {
 	
 	return tokenCount.length > 0? tokenCount: stopwordCount;
 };
+
+// optionalArgs.types
+//  1 - include document length (after tokenization)
+//  2 - include number of uniqueWords
+Lucy.normalize = function(objectStore, indexField, optionalArgs) {
+    var keyval = objectStore.keyPath;
+    var opencursor = objectStore.openCursor();
+    opencursor.onsuccess = function (evt) {	
+        var cursor = evt.target.result;
+        
+        if (cursor) {
+            var updateObj = cursor.value;
+            var text = updateObj[indexField];
+            var types = optionalArgs.types;
+            if (optionalArgs && types) {
+                var metadata = Lucy.getTextMetadata(text);
+                if (1 in types)
+                    updateObj.length = metadata.length;
+                if (2 in types)
+                    updateObj.uniqueWords = metadata.uniqueWords;
+                var insertion = objectStore.put(updateObj);
+				insertion.onerror = function(evt) {
+					console.log(evt, updateObj);
+				};
+            }            
+            cursor.continue();
+        } else {
+            console.log("All text normalized.");        
+        } 
+    };
+    
+    opencursor.onerror = function (evt) {
+        console.log(evt);
+    };
+};
+
+Lucy.getTextMetadata = function(text) {
+    var metadata = {uniqueWords: 0, length: 0};
+    var tokenCount = Lucy.tokenize(text);
+    metadata.uniqueWords = Object.keys(tokenCount.tokens).length;
+    metadata.length = tokenCount.length;
+    console.log(metadata);
+    return metadata;
+}
 
 Lucy.isStopWord = function(word) {
 	return Lucy.stopwords.indexOf(word) > -1;

### 2014-12-10 code/trieindex.js

@@ -225,6 +225,8 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
     }
     
     this.build = function(db) {
+        Lucy.normalize(this.objectStore, me.indexField, {types: [1,2]});        
+        
     	// create object store for trie
     	this.store = db.createObjectStore(name, { keyPath: "id", autoIncrement: true, ifExists: "replace" });
     	console.log("Created Index object store");

### 2014-12-10 code/lucy.js
removed unused debug statement

@@ -119,7 +119,6 @@ Lucy.getTextMetadata = function(text) {
     var tokenCount = Lucy.tokenize(text);
     metadata.uniqueWords = Object.keys(tokenCount.tokens).length;
     metadata.length = tokenCount.length;
-    console.log(metadata);
     return metadata;
 }
 

### 2014-12-10 code/stopwords/english_stopwords.js
add positional information to index in form ids: ["docid:pos1,pos2",...]

@@ -203,6 +203,7 @@ Lucy.stopwords = [
 "how",
 "howbeit",
 "however",
+"i",
 "i'd",
 "i'll",
 "i'm",
@@ -256,6 +257,7 @@ Lucy.stopwords = [
 "looking",
 "looks",
 "ltd",
+"m",
 "mainly",
 "many",
 "may",

### 2014-12-10 paper/paper.tex
add to implementation

@@
 
+The default rank that we implement is
+
 \subsection{Implementation}
@@
 We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.
+The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, and \texttt{trieindex.js} that the developer must include in their HTML file.
+The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.
+
+The file \texttt{lucy.js} contains a static class called \texttt{Lucy} which holds various text processing functions that the different indexes use.
+There is also an extension of \texttt{IDBRequest} called \texttt{IDBIndexRequest} that provides the same behavior, only for our full-text indexes.
+Finally, there are a set of functions that intercept functions of \texttt{IDBObjectStore}.
+When a user calls \texttt{create\_index} or \texttt{index}, if they are creating or referring to a full-text index we direct the function to one of our index implementations.
+When a user calls \texttt{add},  \texttt{delete}, or \texttt{put} on an object store that has a full-text index, we additionally add the item to our indexes.
 

### 2014-12-10 code/demo.js
add normalization for regular weighting, also fixed bug that made invindex slow I think

@@ -167,7 +167,7 @@ function search(db, query, objectStore) {
 			var result = request.result.reduce(function(prev, tweet) {
 				return prev + '<li><a href="http://twitter.com/' + tweet.username + '" class="user">' + tweet.username + '</a>: ' + tweet.text + 
 				       '<a href="http://twitter.com/' + tweet.username + '/' + 'status/' + tweet.id + '" class="date">' + tweet.date +
-				       "</a></li>";
+				       "</a> Score: " + tweet.score + "</li>";
 			}, '');
 		}
 		

### 2014-12-10 code/invindex.js

@@ -14,12 +14,13 @@ var InvIndex = function(objStore, name, field, language) {
 	this.language = language;
 	this.indexField = field;
 	this.unique = false;
+	this.normalization = 1;
+	this.enablePosition = true;
 	
     // Perform index search for a phrase
     this.get = function(text) {
     	var ret = new IDBIndexRequest(this.objectStore, this.transaction);
     	var result_ids;
-    	var objStore = this.objectStore;
     	
     	var tokenCount = Lucy.tokenize(text);
     	
@@ -30,20 +31,23 @@ var InvIndex = function(objStore, name, field, language) {
     		finish_counter[token] = undefined;
     		finish_counter.count++;
     	}
-    	
+    	    	
 		var check_done = function() {
-			if (finish_counter.count == 0) return true;
 			for (var vals in finish_counter) {
 				if (finish_counter[vals] != 0) {
 					return false;
 				}
 			}
-			return true;
+			if (finish_counter.count == 0) {
+				return true;
+			} else {
+				return false;
+			}
 		};
 
     	for (var token in tokenCount.tokens) {
     		var request = this.index.get(token);
-    		var weight = tokenCount.tokens[token];
+    		
     		request.onerror = function(evt) {
     			console.log(evt, token);
     			ret.result = evt.result;
@@ -56,11 +60,27 @@ var InvIndex = function(objStore, name, field, language) {
 					var result_ids = evt.srcElement.result.ids;
 					
 					finish_counter[curr_token] = result_ids.length;
-					
+
 					for (var j=0; j<result_ids.length; j++) {
 						var split = result_ids[j].split(':');
-	    				var request_text = objStore.get(split[0]);
+						var doc_id = split[0];
+						
+						var request_text = me.objectStore.get(split[0]);
+	    				var doc_positions = split.length == 2? split[1] : undefined;
 	    				
+						if (doc_id in result_dict) {
+							result_dict[doc_id].score = result_dict[doc_id].score? result_dict[doc_id].score + 1 : 1;
+							console.log(curr_token + " " + result_dict[doc_id].score);
+							result_dict[doc_id].positions = result_dict[doc_id].positions || {};
+							if (me.enablePositions) {
+	    						result_dict[doc_id].positions[curr_token] = doc_positions;
+	    					}
+	    					finish_counter[curr_token]--;
+							continue;
+						} else {
+							result_dict[doc_id] = {};
+						}
+
[…]

### 2014-12-10 code/lucy.js

@@ -158,6 +158,33 @@ Lucy.convert_dict = function(dict) {
 	});
 };
 
+Lucy.calculateCoverDensity = function(results, norm_level) {
+	for (var doc_id in results) {
+		Lucy.normalizeWeights(results[doc_id], norm_level);
+	}
+};
+Lucy.calculateWeight = function(results, norm_level) {
+	for (var doc_id in results) {
+		Lucy.normalizeWeights(results[doc_id], norm_level);
+	}
+};
+
+// normalization levels:
+// 0: do no normalization
+// 1: divide by document length
+// 2: divide by unique number of words in document
+Lucy.normalizeWeights = function(doc_obj, norm_level) {
+	var rank = doc_obj.score;
+	if (norm_level === 0) {
+		return;
+	} else if (norm_level === 1) {
+		doc_obj.score = rank*1.0/doc_obj.length;
+	} else if (norm_level === 2) {
+		doc_obj.score = rank*1.0/doc_obj.uniqueWords;
+	}
+};
+
+
 
 /*
  * Extends IDBRequest

### 2014-12-10 code/invindex.js
cover density ranking complete!

@@ -70,9 +70,8 @@ var InvIndex = function(objStore, name, field, language) {
 	    				
 						if (doc_id in result_dict) {
 							result_dict[doc_id].score = result_dict[doc_id].score? result_dict[doc_id].score + 1 : 1;
-							console.log(curr_token + " " + result_dict[doc_id].score);
 							result_dict[doc_id].positions = result_dict[doc_id].positions || {};
-							if (me.enablePositions) {
+							if (me.enablePosition) {
 	    						result_dict[doc_id].positions[curr_token] = doc_positions;
 	    					}
 	    					finish_counter[curr_token]--;
@@ -94,7 +93,7 @@ var InvIndex = function(objStore, name, field, language) {
 		    					result.score = result_dict[result.id].score? result_dict[result.id].score + 1 : 1;
 		    					result.positions = result_dict[result.id].positions || {};
 		    					
-		    					if (me.enablePositions) {
+		    					if (me.enablePosition) {
 	    							result.positions[curr_token] = doc_positions;
 	    						}
 		    					result_dict[result.id] = result; 					

### 2014-12-10 code/invindex.js
remove unnecessary line

@@ -99,7 +99,6 @@ var InvIndex = function(objStore, name, field, language) {
 		    					result_dict[result.id] = result; 					
 		    				}
 		    				if (check_done()) {
-		    					var weighted_results;
 		    					if (me.enablePosition) {
 		    						Lucy.calculateCoverDensity(result_dict, me.normalization);
 		    					} else {

### 2014-12-10 typeahead_demo/typeahead/manage.py
add initial django webserver

@@ -1,0 +1,10 @@
+#!/usr/bin/env python
+import os
+import sys
+
+if __name__ == "__main__":
+    os.environ.setdefault("DJANGO_SETTINGS_MODULE", "typeahead.settings")
+
+    from django.core.management import execute_from_command_line
+
+    execute_from_command_line(sys.argv)

### 2014-12-10 typeahead_demo/typeahead/static/code/idbport.js

@@ -1,0 +1,86 @@
+indexedDB.import = function (database, src, callback) {
+	var ret = {
+		// Caller will override these if needed
+		onstatusupdate: function(){},
+		onsuccess: function(){},
+		onerror: function(){}
+	};
+
+	// Get file first
+	var xhr = new XMLHttpRequest(src);
+	
+	xhr.open("GET", src);
+	
+	xhr.onreadystatechange = function () {
+		if (xhr.readyState == 4 && xhr.status < 400) {
+			ret.onstatusupdate("Loaded JSON file");
+			
+			try {
+				var data = JSON.parse(xhr.responseText);
+			}
+			catch (e) {
+				console.error(e);
+				console.log('Data: ', xhr.responseText);
+			}
+			
+			ret.onstatusupdate("Parsed JSON file");
+			
+			// Data should be an object with object store names as keys and arrays as values.
+			// A special __meta key at the root level defines keypaths, autoincrement behavior etc for every object store
+			self.db = undefined;
+			
+			indexedDB.deleteDatabase(database).onsuccess = function(evt) {
+				var DBOpenRequest = indexedDB.open(database);
+				
+				DBOpenRequest.onsuccess = function (evt) {
+					Object.keys(data).forEach(function(id) {
+						if (id != "__meta") {
+							var count = data[id].length;
+							
+							ret.onstatusupdate("Loading data in " + id + " (" + count + " objects total)…");
+							
+							var transaction = db.transaction(id, "readwrite").objectStore(id);
+							
+							data[id].forEach(function(o, i) {
+								if ((i+1) % ~~(count/10) === 0 && count > 100) {
+									// For large datasets, offer feedback every 10% of imported data
+									ret.onstatusupdate("Loading data in " + id + " (" + (i+1) + " of " + count + ")…");
+								}
+								
+								try { 
+									transaction.add(o);
+								}
+								catch (e) {
+									console.error(e, o);
+								}
+							});
+							
+							ret.onstatusupdate("Loaded data in " + id + ".");
+						}
+					});
+					
+					ret.onsuccess();
+					
+					evt.target.result.close();
+				};
+				
+				DBOpenRequest.onupgradeneeded = function (evt) {
+					db = this.result;
+					ret.onstatusupdate("Creating object stores…");
+					
+					Object.keys(data).forEach(function(id) {
+						if (id != "__meta") {
+							db.createObjectStore(id, data['__meta'][id]);
[…]

### 2014-12-10 typeahead_demo/typeahead/static/code/index.js

@@ -1,0 +1,31 @@
+
+/*
+Constructs a TrieIndex for pattern-matching.
+data - array of strings to be indexed
+*/
+var TrieIndex = function(data) {
+    // Perform pattern-matching (prefix/suffix search), return whole string
+    this.get = function(pattern) {
+        return null;
+    };
+
+    // Normalize data before insertion (no tokenization for pattern-matching)
+    this.insert = function(text) {};
+
+    return this;
+};
+
+/*
+Constructs a BTreeIndex for full-text search.
+data - array of strings to be indexed
+*/
+var BTreeIndex = function(data) {
+    // Perform index search for a tokenized word
+    this.get = function(word) {
+        return null;
+    };
+
+    // Normalize and tokenize data before insertion.
+    this.insert = function(text) {};
+    return this;
+};

### 2014-12-10 typeahead_demo/typeahead/static/code/invindex.js

@@ -1,0 +1,218 @@
+
+/*
+Constructs an InvIndex for full-text search.
+*/
+
+
+var InvIndex = function(objStore, name, field, language) {
+	var me = this;
+	
+	this.objectStore = objStore;
+	this.transaction = objStore && objStore.transaction;
+	
+	this.name = name;
+	this.language = language;
+	this.indexField = field;
+	this.unique = false;
+	this.normalization = 0;
+	this.enablePosition = false;
+	
+    // Perform index search for a phrase
+    this.get = function(text) {
+    	var ret = new IDBIndexRequest(this.objectStore, this.transaction);
+    	var result_ids;
+    	
+    	var tokenCount = Lucy.tokenize(text);
+    	
+    	var result_dict = {};
+    	
+    	var finish_counter = {count: 0};
+    	for (var token in tokenCount.tokens) {
+    		finish_counter[token] = undefined;
+    		finish_counter.count++;
+    	}
+    	    	
+		var check_done = function() {
+			for (var vals in finish_counter) {
+				if (finish_counter[vals] != 0) {
+					return false;
+				}
+			}
+			if (finish_counter.count == 0) {
+				return true;
+			} else {
+				return false;
+			}
+		};
+
+    	for (var token in tokenCount.tokens) {
+    		var request = this.index.get(token);
+    		
+    		request.onerror = function(evt) {
+    			console.log(evt, token);
+    			ret.result = evt.result;
+    			ret.onerror();
+    		};
+    		request.onsuccess = function(evt) {
+    			finish_counter.count--;
+				if (evt.srcElement.result) {
+					var curr_token = evt.srcElement.result.token;
+					var result_ids = evt.srcElement.result.ids;
+					
+					finish_counter[curr_token] = result_ids.length;
+
+					for (var j=0; j<result_ids.length; j++) {
+						var split = result_ids[j].split(':');
+						var doc_id = split[0];
+						
+						var request_text = me.objectStore.get(split[0]);
+	    				var doc_positions = split.length == 2? split[1] : undefined;
+	    				
+						if (doc_id in result_dict) {
+							result_dict[doc_id].score = result_dict[doc_id].score? result_dict[doc_id].score + 1 : 1;
+							result_dict[doc_id].positions = result_dict[doc_id].positions || {};
+							if (me.enablePosition) {
+	    						result_dict[doc_id].positions[curr_token] = doc_positions;
+	    				}
[…]

### 2014-12-10 typeahead_demo/typeahead/static/code/lucy.js

@@ -1,0 +1,393 @@
+/*
+ * Lucy.js
+ * 
+ */
+
+var SUPPORTED_LANGUAGES = [
+	'english',  'danish', 'dutch',
+	'finnish', 'french', 'german',
+	'hungarian', 'italian', 'norwegian',
+	'portuguese', 'russian', 'spanish',
+	'swedish', 'romanian', 'turkish'];
+
+/*
+ * Static class for general purpose natural language processing functions 
+ * 
+ */
+
+self.Lucy = {};
+
+Lucy.init = function(db) {
+	// Fetch all indices from database
+	this.indexCache = {};
+	
+	if (db.objectStoreNames.contains('__LucyIndices')) {
+		var cursor = db.transaction("__LucyIndices", "readonly").objectStore("__LucyIndices").openCursor();
+		
+		cursor.onsuccess = function (evt) {
+			var cursor = evt.target.result;
+			
+			if (cursor) {
+				var val = cursor.value;
+				
+				if (val.type == 'inverted') {
+					var index = new InvIndex(db.transaction(val.store).objectStore(val.store), val.name, val.path);
+				}
+				else {
+					var index = new TrieIndex(db.transaction(val.store).objectStore(val.store), val.name, val.path, val.type);
+				}
+
+				Lucy.indexCache[val.type] = Lucy.indexCache[val.type] || {};
+				Lucy.indexCache[val.type][val.name] = index;
+				
+				cursor.continue();
+			}
+			else {
+				db.close();
+			}
+		};
+	}
+}
+
+Lucy.language = "english";
+
+// potential options:
+// disableStemming
+// enablePosition
+
+Lucy.tokenize = function(string, options) {
+	options = options || {};
+	options.disableStemming = !!options.disableStemming;
+	options.enablePosition = !!options.enablePosition;
+	
+	string = string.toLowerCase();
+	var tokens = string.match(/\w+/g);
+	
+	var tokenCount = {length: 0, tokens: {}};
+	var stopwordCount = {length: 0, tokens: {}};
+	
+	if (!options.disableStemming) {
+		var stemmer = Lucy.stemmer(Lucy.language);
+	}
+
+	for (var i=0; i<tokens.length; i++) {
+		var stem = options.disableStemming? tokens[i] : stemmer(tokens[i]);
+		
+		var count = Lucy.isStopWord(tokens[i])? stopwordCount : tokenCount;
+		
+		
[…]

### 2014-12-10 typeahead_demo/typeahead/static/code/stopwords/english_stopwords.js

@@ -1,0 +1,548 @@
+Lucy.stopwords = [
+"",
+"a",
+"able",
+"about",
+"above",
+"according",
+"accordingly",
+"across",
+"actually",
+"after",
+"afterwards",
+"again",
+"against",
+"ain't",
+"all",
+"allow",
+"allows",
+"almost",
+"alone",
+"along",
+"already",
+"also",
+"although",
+"always",
+"am",
+"among",
+"amongst",
+"an",
+"and",
+"another",
+"any",
+"anybody",
+"anyhow",
+"anyone",
+"anything",
+"anyway",
+"anyways",
+"anywhere",
+"apart",
+"appear",
+"appreciate",
+"appropriate",
+"are",
+"aren't",
+"around",
+"as",
+"aside",
+"ask",
+"asking",
+"associated",
+"at",
+"available",
+"away",
+"awfully",
+"be",
+"became",
+"because",
+"become",
+"becomes",
+"becoming",
+"been",
+"before",
+"beforehand",
+"behind",
+"being",
+"believe",
+"below",
+"beside",
+"besides",
+"best",
+"between",
+"beyond",
+"both",
+"brief",
+"but",
+"by",
+"c'mon",
+"c",
+"came",
+"can",
+"can't",
+"cannot",
+"cant",
+"cause",
+"causes",
+"certain",
+"certainly",
+"changes",
+"clearly",
+"co",
+"com",
+"come",
+"comes",
+"concerning",
+"consequently",
+"consider",
+"considering",
+"contain",
+"containing",
+"contains",
+"corresponding",
+"could",
+"couldn't",
+"course",
+"currently",
+"definitely",
+"described",
+"despite",
+"did",
+"didn't",
+"different",
+"do",
+"does",
+"doesn't",
+"doing",
+"don't",
+"done",
+"down",
+"downwards",
+"during",
+"each",
+"edu",
+"eg",
+"eight",
+"either",
+"else",
+"elsewhere",
+"enough",
+"entirely",
+"especially",
+"et",
+"etc",
+"even",
+"ever",
+"every",
+"everybody",
+"everyone",
+"everything",
+"everywhere",
+"ex",
+"exactly",
+"example",
+"except",
+"far",
+"few",
+"fifth",
+"first",
+"five",
+"followed",
+"following",
+"follows",
+"for",
+"former",
[…]

### 2014-12-10 typeahead_demo/typeahead/static/code/trieindex.js

@@ -1,0 +1,279 @@
+
+/*
+Constructs a TrieIndex for prefix/suffix search.
+*/
+
+var TrieIndex = function(objStore, name, field, mode, maxDepth) {
+	var me = this;
+
+	this.objectStore = objStore; // overriden before index is used
+    this.transaction = objStore && objStore.transaction; // overriden before index is used
+	this.unique = false;
+	this.indexField = field;
+    this.mode = mode;
+    this.name = name;
+    this.indexName = this.name + "_index";
+    this.maxDepth = -1;
+    if (maxDepth) {
+        this.maxDepth = maxDepth;
+    }
+
+    function hasMaxDepth() {
+        return me.maxDepth != -1;
+    }
+	
+    // Perform prefix search
+    // Return list of document objects with matches
+    this.get = function(text) {
+        var trieIndex = this.index.index(this.indexName);
+        var docIdsDict = {};
+
+        var ret = new IDBIndexRequest(this.objectStore, this.transaction);
+
+        var tokenCount = Lucy.tokenize(text, {disableStemming: true});
+        var finishCounter = {count: Object.keys(tokenCount.tokens).length};
+        
+        for (token in tokenCount.tokens) {
+            var weight = tokenCount.tokens[token];
+            
+            if (this.mode == "suffix") {
+                token = reverse(token);
+            }
+            
+            searchHelper(trieIndex, docIdsDict, token, weight, 0, ret, this.objectStore, finishCounter);
+        }
+        
+        return ret;
+    };
+
+    function searchHelper(metaIndex, docIdsDict, token, weight, parentId, ret, objStore, finishCounter) {
+        if (token.length == 0) {
+            finishCounter.count--;
+            
+            if (finishCounter.count == 0) {
+                populateResultText(docIdsDict, ret, objStore);
+            }
+        }
+
+        var c = token.charAt(0);
+        var request = metaIndex.get([parentId, c]);
+        (function(metaIndex, token, weight, parentId, ret, objStore, finishCounter) {        
+            request.onsuccess = function(evt) {
+                if (evt.target.result) {
+                    var result = evt.target.result;
+                    if (token.length == 1) {
+                        finishCounter.count--;
+                        
+                        for (var i=0; i<result.docIds.length; i++) {
+                            docId = result.docIds[i];
+                            
+                            docIdsDict[docId] = docIdsDict[docId] || 0;
+                            docIdsDict[docId] += weight;
+                        }
+                        
[…]

### 2014-12-10 typeahead_demo/typeahead/tweets/migrations/0001_initial.py

@@ -1,0 +1,26 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='Tweet',
+            fields=[
+                ('id', models.AutoField(verbose_name='ID', serialize=False, auto_created=True, primary_key=True)),
+                ('text', models.CharField(max_length=200)),
+                ('date', models.DateTimeField()),
+                ('tweetid', models.BigIntegerField()),
+                ('username', models.CharField(max_length=30)),
+            ],
+            options={
+            },
+            bases=(models.Model,),
+        ),
+    ]

### 2014-12-10 typeahead_demo/typeahead/tweets/models.py

@@ -1,0 +1,10 @@
+from django.db import models
+
+# Create your models here.
+
+class Tweet(models.Model):
+    text = models.CharField(max_length=200)
+    date = models.DateTimeField();
+    tweetid = models.BigIntegerField();
+    username = models.CharField(max_length=30)
+    

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py

@@ -1,0 +1,31 @@
+from django.shortcuts import render
+from django.shortcuts import render_to_response
+
+from django.http import HttpResponse
+
+import json
+
+# Create your views here.
+
+def home(request):
+    return render_to_response('typeahead_demo.html')
+
+def query(request, query):
+    print query
+    return HttpResponse(json.dumps({'query': query}), content_type="application/json")
+
+def delete_tweets(request):
+    t = Tweet.objects.all().delete()
+    return HttpResponse(json.dumps({'result': 'success'}), content_type="application/json")
+    
+
+def insert_tweets(request):
+    tweets = request.POST['tweets']
+    
+    for tweet in tweets:
+        print tweet
+        t = Tweet.objects.create(tweetid=tweet.id, text=tweet.text, date=tweet.date, username=tweet.username)
+        
+
+    return HttpResponse(json.dumps({'result': 'success'}), content_type="application/json")
+    

### 2014-12-10 typeahead_demo/typeahead/typeahead/settings.py

@@ -1,0 +1,87 @@
+"""
+Django settings for typeahead project.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/1.7/topics/settings/
+
+For the full list of settings and their values, see
+https://docs.djangoproject.com/en/1.7/ref/settings/
+"""
+
+# Build paths inside the project like this: os.path.join(BASE_DIR, ...)
+import os
+BASE_DIR = os.path.dirname(os.path.dirname(__file__))
+
+
+# Quick-start development settings - unsuitable for production
+# See https://docs.djangoproject.com/en/1.7/howto/deployment/checklist/
+
+# SECURITY WARNING: keep the secret key used in production secret!
+SECRET_KEY = '06ky6(_fi3m5r8bz@=m+40h0uf3&k%jwdy2xwyhcjw0a62td&%'
+
+# SECURITY WARNING: don't run with debug turned on in production!
+DEBUG = True
+
+TEMPLATE_DEBUG = True
+
+ALLOWED_HOSTS = []
+
+TEMPLATE_DIRS = ("tweets/templates",)
+
+# Application definition
+
+INSTALLED_APPS = (
+    'django.contrib.admin',
+    'django.contrib.auth',
+    'django.contrib.contenttypes',
+    'django.contrib.sessions',
+    'django.contrib.messages',
+    'django.contrib.staticfiles',
+    'tweets'
+)
+
+MIDDLEWARE_CLASSES = (
+    'django.contrib.sessions.middleware.SessionMiddleware',
+    'django.middleware.common.CommonMiddleware',
+    'django.middleware.csrf.CsrfViewMiddleware',
+    'django.contrib.auth.middleware.AuthenticationMiddleware',
+    'django.contrib.auth.middleware.SessionAuthenticationMiddleware',
+    'django.contrib.messages.middleware.MessageMiddleware',
+    'django.middleware.clickjacking.XFrameOptionsMiddleware',
+)
+
+ROOT_URLCONF = 'typeahead.urls'
+
+WSGI_APPLICATION = 'typeahead.wsgi.application'
+
+
+# Database
+# https://docs.djangoproject.com/en/1.7/ref/settings/#databases
+
+DATABASES = {
+    'default': {
+        'ENGINE': 'django.db.backends.sqlite3',
+        'NAME': os.path.join(BASE_DIR, 'db.sqlite3'),
+    }
[…]

### 2014-12-10 typeahead_demo/typeahead/typeahead/urls.py

@@ -1,0 +1,16 @@
+from django.conf.urls import patterns, include, url
+from django.contrib import admin
+
+urlpatterns = patterns('',
+    # Examples:
+    
+    
+    url(r'^$', 'tweets.views.home'),
+    
+    url(r'^search/(?P<query>[\w-]+)', 'tweets.views.query'),
+    
+    url(r'^insert_tweets', 'tweets.views.insert_tweets'),
+    url(r'^delete_tweets', 'tweets.views.delete_tweets'),
+    
+    url(r'^admin/', include(admin.site.urls)),
+)

### 2014-12-10 typeahead_demo/typeahead/typeahead/wsgi.py

@@ -1,0 +1,14 @@
+"""
+WSGI config for typeahead project.
+
+It exposes the WSGI callable as a module-level variable named ``application``.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/1.7/howto/deployment/wsgi/
+"""
+
+import os
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "typeahead.settings")
+
+from django.core.wsgi import get_wsgi_application
+application = get_wsgi_application()

### 2014-12-10 typeahead_demo/typeahead/static/code/typeahead_demo.js
basic server only typeahead works sort of. mysql can only search for %str%

@@ -1,17 +1,10 @@
-function $(expr, con) {
-	return typeof expr === 'string'? (con || document).querySelector(expr) : expr;
-}
-
-function $$(expr, con) {
-	return Array.prototype.slice.call((con || document).querySelectorAll(expr));
-}
 
 function now() {
 	return self.performance? performance.now() : Date.now();
 }
 
 var databaseName = "LucyTest";
-var dataFile = "data/xad";
+var dataFile = "data/tweets2.json";
 var currentDBVersion;
 
 (function() {
@@ -45,7 +38,48 @@ function resetDBVersion() {
 	localStorage.setItem(key, 1);
 }
 
-$('#import-data').onclick = function () {
+$('#delete-data').click( function () {
+	indexedDB.deleteDatabase(databaseName);
+	
+	$.ajax({
+	    url: "delete_tweets",
+	    success: function(){
+	      console.log("Everything deleted");
+	    }
+	});
+});
+
+//Send all data to server
+$('#send-data1').click( function () {
+			
+	$.ajax({
+	    url: "insert_tweets1",
+	    
+	    success: function(){
+	      console.log("Everything inserted");
+	    }
+	});
+	
+});
+ 
+$('#the-basics .typeahead').typeahead({
+  hint: true,
+  highlight: true,
+  minLength: 1
+},
+{
+  name: 'states',
+  displayKey: 'value',
+  source: function (query, process) {
+  	return $.get('/search/' + query, {}, function (data) {
+  		console.log(data);
+            return process(data.options);
+        });
+  }
+});
+
+
+$('#import-data').click(function () {
 	var me = this;
 	resetDBVersion();
 	
@@ -61,9 +95,9 @@ $('#import-data').onclick = function () {
 		loadingStatus.textContent = '';
 		me.classList.add('done');
 	};	
-};
+});
 
-$('#build-inv-index').onclick = function () {
+$('#build-inv-index').click(function () {
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
@@ -81,9 +115,9 @@ $('#build-inv-index').onclick = function () {
 		evt.target.result.close();
 		console.log('Finished creating index.');
 	};
-};
+});
 
-$('#build-prefix-index').onclick = function () {
+$('#build-prefix-index').click(function () {
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
[…]

### 2014-12-10 typeahead_demo/typeahead/tweets/migrations/0002_remove_tweet_date.py

@@ -1,0 +1,18 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('tweets', '0001_initial'),
+    ]
+
+    operations = [
+        migrations.RemoveField(
+            model_name='tweet',
+            name='date',
+        ),
+    ]

### 2014-12-10 typeahead_demo/typeahead/tweets/models.py

@@ -4,7 +4,6 @@ from django.db import models
 
 class Tweet(models.Model):
     text = models.CharField(max_length=200)
-    date = models.DateTimeField();
     tweetid = models.BigIntegerField();
     username = models.CharField(max_length=30)
     

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py

@@ -1,7 +1,10 @@
 from django.shortcuts import render
 from django.shortcuts import render_to_response
-
+from tweets.models import Tweet
 from django.http import HttpResponse
+
+import os
+from typeahead.settings import PROJECT_ROOT
 
 import json
 
@@ -11,21 +14,38 @@ def home(request):
     return render_to_response('typeahead_demo.html')
 
 def query(request, query):
-    print query
-    return HttpResponse(json.dumps({'query': query}), content_type="application/json")
+    try:
+        tweets = Tweet.objects.extra(where=["`tweets_tweet`.`text` LIKE \"%%" + query + "%%\""])
+        print tweets.query
+        print tweets
+        result = {"options": []}
+        for tweet in tweets:
+            print tweet
+            result["options"].append({"value": tweet.text})
+    except Exception, e:
+        print e
+    
+    return HttpResponse(json.dumps(result), content_type="application/json")
 
 def delete_tweets(request):
-    t = Tweet.objects.all().delete()
+    print "deleting tweets"
+    try:
+        t = Tweet.objects.all().delete()
+    except Exception, e:
+        print e
     return HttpResponse(json.dumps({'result': 'success'}), content_type="application/json")
     
 
-def insert_tweets(request):
-    tweets = request.POST['tweets']
-    
-    for tweet in tweets:
-        print tweet
-        t = Tweet.objects.create(tweetid=tweet.id, text=tweet.text, date=tweet.date, username=tweet.username)
-        
+def insert_tweets1(request):
+    try:
+        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
+        tweets = json.loads(file.read())
+        tweets = tweets["tweets"]
+        for tweet in tweets:
+            print tweet
+            t = Tweet.objects.create(tweetid=tweet['id'], text=tweet['text'], username=tweet['username'])
+    except Exception, e:
+        print e    
 
     return HttpResponse(json.dumps({'result': 'success'}), content_type="application/json")
     

### 2014-12-10 typeahead_demo/typeahead/typeahead/settings.py

@@ -50,6 +50,8 @@ MIDDLEWARE_CLASSES = (
     'django.middleware.clickjacking.XFrameOptionsMiddleware',
 )
 
+PROJECT_ROOT = os.path.abspath(os.path.dirname(__file__))
+
 ROOT_URLCONF = 'typeahead.urls'
 
 WSGI_APPLICATION = 'typeahead.wsgi.application'
@@ -60,8 +62,12 @@ WSGI_APPLICATION = 'typeahead.wsgi.application'
 
 DATABASES = {
     'default': {
-        'ENGINE': 'django.db.backends.sqlite3',
-        'NAME': os.path.join(BASE_DIR, 'db.sqlite3'),
+        'ENGINE': 'django.db.backends.mysql',
+        'NAME': "typeahead",
+        'USER': 'admin',
+        'PASSWORD': 'koobkoob',
+        'HOST': 'localhost',   # Or an IP Address that your DB is hosted on
+        'PORT': '3306',
     }
 }
 

### 2014-12-10 typeahead_demo/typeahead/typeahead/urls.py

@@ -7,9 +7,9 @@ urlpatterns = patterns('',
     
     url(r'^$', 'tweets.views.home'),
     
-    url(r'^search/(?P<query>[\w-]+)', 'tweets.views.query'),
+    url(r'^search/(?P<query>.+)', 'tweets.views.query'),
     
-    url(r'^insert_tweets', 'tweets.views.insert_tweets'),
+    url(r'^insert_tweets1', 'tweets.views.insert_tweets1'),
     url(r'^delete_tweets', 'tweets.views.delete_tweets'),
     
     url(r'^admin/', include(admin.site.urls)),

### 2014-12-10 typeahead_demo/typeahead/static/code/idbport.js
demo works with client side only

@@ -1,3 +1,65 @@
+indexedDB.import_data = function(database, data) {
+	var ret = {
+		onsuccess: function(){},
+	};
+	
+	self.db = undefined;
+	
+	console.log('here');
+			
+	indexedDB.deleteDatabase(database).onsuccess = function(evt) {
+		var DBOpenRequest = indexedDB.open(database);
+		
+		DBOpenRequest.onsuccess = function (evt) {
+			Object.keys(data).forEach(function(id) {
+				if (id != "__meta") {
+					var count = data[id].length;
+					
+					console.log("Loading data in " + id + " (" + count + " objects total)…");
+					
+					var transaction = db.transaction(id, "readwrite").objectStore(id);
+					
+					data[id].forEach(function(o, i) {
+						if ((i+1) % ~~(count/10) === 0 && count > 100) {
+							// For large datasets, offer feedback every 10% of imported data
+							console.log("Loading data in " + id + " (" + (i+1) + " of " + count + ")…");
+						}
+						
+						try { 
+							transaction.add(o);
+						}
+						catch (e) {
+							console.error(e, o);
+						}
+					});
+					
+					console.log("Loaded data in " + id + ".");
+				}
+			});
+			
+			ret.onsuccess();
+					
+			evt.target.result.close();
+		};
+		
+		DBOpenRequest.onupgradeneeded = function (evt) {
+			db = this.result;
+			console.log("Creating object stores…");
+			
+			Object.keys(data).forEach(function(id) {
+				if (id != "__meta") {
+					db.createObjectStore(id, data['__meta'][id]);
+				}
+			});
+			
+			console.log("Created object stores.");
+		};
+	};
+	return ret;
+};
+
+
+
 indexedDB.import = function (database, src, callback) {
 	var ret = {
 		// Caller will override these if needed

### 2014-12-10 typeahead_demo/typeahead/static/code/typeahead_demo.js

@@ -7,6 +7,8 @@ var databaseName = "LucyTest";
 var dataFile = "data/tweets2.json";
 var currentDBVersion;
 
+var search_setting;
+
 (function() {
 	// Init
 	loadDBVersion();
@@ -50,16 +52,30 @@ $('#delete-data').click( function () {
 });
 
 //Send all data to server
-$('#send-data1').click( function () {
-			
+$('#send-data1').click( function () {	
+	search_setting = 1;	
 	$.ajax({
 	    url: "insert_tweets1",
-	    
 	    success: function(){
 	      console.log("Everything inserted");
 	    }
 	});
-	
+});
+
+//get all data from client
+$('#send-data2').click( function () {
+	search_setting = 2;		
+	$.ajax({
+	    url: "get_tweets",
+	    success: function(data){
+	    	var ret = indexedDB.import_data(databaseName, data);
+	    	
+	    	ret.onsuccess = function () {
+	     		console.log("Everything inserted");
+	     		build_prefix();
+	     };
+	    }
+	});
 });
  
 $('#the-basics .typeahead').typeahead({
@@ -71,10 +87,28 @@ $('#the-basics .typeahead').typeahead({
   name: 'states',
   displayKey: 'value',
   source: function (query, process) {
-  	return $.get('/search/' + query, {}, function (data) {
-  		console.log(data);
-            return process(data.options);
-        });
+  	var start = (new Date()).getTime();
+  	
+  	if (search_setting === 1) {
+	  	$.get('/search/' + query, {}, function (data) {
+	        var res = process(data.options);
+	        var stop = ((new Date()).getTime() - start) + 'ms';
+	        console.log(stop);
+	        $("#timer").text(stop);
+	        return res;
+	    });
+	}
+	if (search_setting === 2) {
+		var result = search_client(query);
+		result.onsuccess = function() {
+			console.log(result);
+			var res = process(result.result.options);
+			var stop = ((new Date()).getTime() - start) + 'ms';
+			$("#timer").text(stop);
+		    return res;
+		};
+
+	}
   }
 });
 
@@ -97,27 +131,8 @@ $('#import-data').click(function () {
 	};	
 });
 
-$('#build-inv-index').click(function () {
-	incrementDBVersion();
-	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
-	DBOpenRequest.onupgradeneeded = function(evt) {
-		var transaction = evt.target.transaction;
-		
[…]

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py

@@ -16,8 +16,6 @@ def home(request):
 def query(request, query):
     try:
         tweets = Tweet.objects.extra(where=["`tweets_tweet`.`text` LIKE \"%%" + query + "%%\""])
-        print tweets.query
-        print tweets
         result = {"options": []}
         for tweet in tweets:
             print tweet
@@ -26,6 +24,16 @@ def query(request, query):
         print e
     
     return HttpResponse(json.dumps(result), content_type="application/json")
+
+
+def get_tweets(request):
+    try:
+        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
+    except Exception, e:
+        print e    
+
+    return HttpResponse(file.read(), content_type="application/json")
+
 
 def delete_tweets(request):
     print "deleting tweets"
@@ -42,7 +50,6 @@ def insert_tweets1(request):
         tweets = json.loads(file.read())
         tweets = tweets["tweets"]
         for tweet in tweets:
-            print tweet
             t = Tweet.objects.create(tweetid=tweet['id'], text=tweet['text'], username=tweet['username'])
     except Exception, e:
         print e    

### 2014-12-10 typeahead_demo/typeahead/typeahead/urls.py

@@ -12,5 +12,7 @@ urlpatterns = patterns('',
     url(r'^insert_tweets1', 'tweets.views.insert_tweets1'),
     url(r'^delete_tweets', 'tweets.views.delete_tweets'),
     
+    url(r'^get_tweets', 'tweets.views.get_tweets'),
+    
     url(r'^admin/', include(admin.site.urls)),
 )

### 2014-12-10 typeahead_demo/typeahead/static/code/trieindex-new.js
add lea's changes to server

@@ -22,7 +22,8 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 		var ret = new IDBIndexRequest(this.objectStore, this.transaction);
 
 		var tokenCount = Lucy.tokenize(text, {disableStemming: true});
-		var finishCounter = {count: Object.keys(tokenCount.tokens).length};
+		
+		var pendingPaths = {count: 0}
 		
 		for (token in tokenCount.tokens) {
 			var weight = tokenCount.tokens[token];
@@ -31,7 +32,9 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 				token = reverse(token);
 			}
 			
-			getToken(token, docIdsDict, {count: 0}, ret);
+			pendingPaths.count++;
+			
+			getToken(token, docIdsDict, pendingPaths, ret);
 		}
 		
 		return ret;
@@ -39,13 +42,14 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 	
 	// Search for one single prefix
 	function getToken(token, docIdsDict, pendingPaths, ret) {
-		pendingPaths = pendingPaths || {count: 0};
+		pendingPaths = pendingPaths || {count: 1};
 		var getter = me.store.get(token);
 		
 		getter.onsuccess = function (evt) {
 			var node = evt.target.result;
 			
 			if (!node) {
+				pendingPaths.count--;
 				populateResultText(docIdsDict, ret, me.objectStore);
 				return;
 			}
@@ -74,7 +78,6 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 				
 				if (pendingPaths.count === 0) {
 					// We’ve explored the entire subtree, time for results yo!
-					console.log(docIdsDict);
 					populateResultText(docIdsDict, ret, me.objectStore);
 				}
 			}
@@ -146,8 +149,9 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 				}
 			}
 			else {
-				// It’s a leaf!
-				// DocIds: Documents that contain this word as a whole token
+				// DocIds: Documents that contain this word *as a whole token*
+				// Notice that the same document cannot add both docIds and
+				// children to the same node, by definition of what these are.
 				node.docIds = node.docIds || [];
 				
 				if (node.docIds.indexOf(docId) === -1) {

### 2014-12-10 typeahead_demo/typeahead/static/code/fulltext_demo.js
second demo for fulltext search

@@ -72,47 +72,14 @@ $('#send-data2').click( function () {
 	    	
 	    	ret.onsuccess = function () {
 	     		console.log("Everything inserted");
-	     		build_prefix();
+	     		build_invindex();
 	     };
 	    }
 	});
 });
- 
-$('#the-basics .typeahead').typeahead({
-  hint: true,
-  highlight: true,
-  minLength: 1
-},
-{
-  name: 'states',
-  displayKey: 'value',
-  source: function (query, process) {
-  	var start = (new Date()).getTime();
-  	
-  	if (search_setting === 1) {
-	  	$.get('/search/' + query, {}, function (data) {
-	        var res = process(data.options);
-	        var stop = ((new Date()).getTime() - start) + 'ms';
-	        console.log(stop);
-	        $("#timer").text(stop);
-	        return res;
-	    });
-	}
-	if (search_setting === 2) {
-		var result = search_client(query);
-		result.onsuccess = function() {
-			console.log(result);
-			var res = process(result.result.options);
-			var stop = ((new Date()).getTime() - start) + 'ms';
-			$("#timer").text(stop);
-		    return res;
-		};
 
-	}
-  }
-});
 
-build_prefix = function() {
+build_invindex = function () {
 	incrementDBVersion();
 	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
 
@@ -123,18 +90,72 @@ build_prefix = function() {
 		var objectStore = transaction.objectStore("tweets");
 		
 		// field to create index on
-		objectStore.createIndex("tweets_text_prefix", "text", {type: "prefix", db: evt.target.result});
+		objectStore.createIndex("tweets_text", "text", {type: "inverted", db: evt.target.result});
 	};
 	
 	DBOpenRequest.onsuccess = function(evt) {
 		evt.target.result.close();
 		console.log('Finished creating index.');
 	};
-	
-	DBOpenRequest.onblocked = function (evt) {
-		console.error('Database is blocked yo!');
-	};
 };
+
+$(".search").submit(function(evt) {
+	evt.preventDefault();
+  	var start = (new Date()).getTime();
+  	console.log(search_setting);
+  	
+  	var query = $('#search-query').val();
+  	
+  	if (search_setting === 1) {
+	  	$.get('/search_fulltext/' + query, {}, function (data) {
+	        var res = data.options;
+	        var stop = ((new Date()).getTime() - start) + 'ms';
+	        console.log(stop);
+	        
+	        console.log(res);
[…]

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py

@@ -10,12 +10,28 @@ import json
 
 # Create your views here.
 
-def home(request):
+def demo1(request):
     return render_to_response('typeahead_demo.html')
+
+def demo2(request):
+    return render_to_response('fulltextsearch_demo.html')
 
 def query(request, query):
     try:
         tweets = Tweet.objects.extra(where=["`tweets_tweet`.`text` LIKE \"%%" + query + "%%\""])
+        result = {"options": []}
+        for tweet in tweets:
+            print tweet
+            result["options"].append({"value": tweet.text})
+    except Exception, e:
+        print e
+    
+    return HttpResponse(json.dumps(result), content_type="application/json")
+
+
+def query_fulltext(request, query):
+    try:
+        tweets = Tweet.objects.filter(text__search=query)
         result = {"options": []}
         for tweet in tweets:
             print tweet

### 2014-12-10 typeahead_demo/typeahead/typeahead/urls.py

@@ -5,9 +5,11 @@ urlpatterns = patterns('',
     # Examples:
     
     
-    url(r'^$', 'tweets.views.home'),
+    url(r'^demo1', 'tweets.views.demo1'),
+    url(r'^demo2', 'tweets.views.demo2'),
     
     url(r'^search/(?P<query>.+)', 'tweets.views.query'),
+    url(r'^search_fulltext/(?P<query>.+)', 'tweets.views.query_fulltext'),
     
     url(r'^insert_tweets1', 'tweets.views.insert_tweets1'),
     url(r'^delete_tweets', 'tweets.views.delete_tweets'),

### 2014-12-10 typeahead_demo/typeahead/static/code/demo.js
add new parts to server

@@ -1,0 +1,200 @@
+function $(expr, con) {
+	return typeof expr === 'string'? (con || document).querySelector(expr) : expr;
+}
+
+function $$(expr, con) {
+	return Array.prototype.slice.call((con || document).querySelectorAll(expr));
+}
+
+function now() {
+	return self.performance? performance.now() : Date.now();
+}
+
+var databaseName = "LucyTest";
+var dataFile = "data/xad";
+var currentDBVersion;
+
+(function() {
+	// Init
+	loadDBVersion();
+	
+	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
+	
+	DBOpenRequest.onsuccess = function(evt) {
+		Lucy.init(evt.target.result);
+	};
+})();
+
+function loadDBVersion() {
+	var key = databaseName + "version";
+	if (localStorage.getItem(key)) {
+		currentDBVersion = localStorage.getItem(key);
+	} else {
+		currentDBVersion = 1;
+	}
+}
+
+function incrementDBVersion() {
+	var key = databaseName + "version";
+	localStorage.setItem(key, ++currentDBVersion);
+}
+
+function resetDBVersion() {
+	var key = databaseName + "version";
+	currentDBVersion = 1;
+	localStorage.setItem(key, 1);
+}
+
+$('#import-data').onclick = function () {
+	var me = this;
+	resetDBVersion();
+	
+	var loadingStatus = $('.loading-status');
+	var importData = indexedDB.import(databaseName, dataFile);
+	
+	importData.onstatusupdate = function (status) {
+		console.log(status);
+		loadingStatus.textContent = status;
+	};
+	
+	importData.onsuccess = function () {
+		loadingStatus.textContent = '';
+		me.classList.add('done');
+	};	
+};
+
+$('#build-inv-index').onclick = function () {
+	incrementDBVersion();
+	var DBOpenRequest = indexedDB.open(databaseName, currentDBVersion);
+
+	DBOpenRequest.onupgradeneeded = function(evt) {
+		var transaction = evt.target.transaction;
+		
+		// table to create index on
+		var objectStore = transaction.objectStore("tweets");
+		
+		// field to create index on
+		objectStore.createIndex("tweets_text", "text", {type: "inverted", db: evt.target.result});
+	};
+	
+	DBOpenRequest.onsuccess = function(evt) {
+		evt.target.result.close();
+		console.log('Finished creating index.');
+	};
+};
+
+$('#build-prefix-index').onclick = function () {
[…]

### 2014-12-10 typeahead_demo/typeahead/static/code/fulltext_demo.js

@@ -4,7 +4,7 @@ function now() {
 }
 
 var databaseName = "LucyTest";
-var dataFile = "data/tweets2.json";
+var dataFile = "data/xad";
 var currentDBVersion;
 
 var search_setting;

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py

@@ -10,6 +10,9 @@ import json
 
 # Create your views here.
 
+def index(request):
+    return render_to_response('index.html')
+
 def demo1(request):
     return render_to_response('typeahead_demo.html')
 
@@ -44,7 +47,7 @@ def query_fulltext(request, query):
 
 def get_tweets(request):
     try:
-        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
+        file = open(os.path.join(PROJECT_ROOT, 'xad'))
     except Exception, e:
         print e    
 
@@ -62,11 +65,11 @@ def delete_tweets(request):
 
 def insert_tweets1(request):
     try:
-        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
+        file = open(os.path.join(PROJECT_ROOT, 'xad'))
         tweets = json.loads(file.read())
         tweets = tweets["tweets"]
         for tweet in tweets:
-            t = Tweet.objects.create(tweetid=tweet['id'], text=tweet['text'], username=tweet['username'])
+            t = Tweet.objects.create(tweetid=tweet['id'], text=tweet['text'].encode('ascii', "ignore"), username=tweet['username'])
     except Exception, e:
         print e    
 

### 2014-12-10 typeahead_demo/typeahead/typeahead/urls.py

@@ -4,7 +4,7 @@ from django.contrib import admin
 urlpatterns = patterns('',
     # Examples:
     
-    
+    url(r'^$', 'tweets.views.index'),
     url(r'^demo1', 'tweets.views.demo1'),
     url(r'^demo2', 'tweets.views.demo2'),
     

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py
minor things

@@ -24,7 +24,6 @@ def query(request, query):
         tweets = Tweet.objects.extra(where=["`tweets_tweet`.`text` LIKE \"%%" + query + "%%\""])
         result = {"options": []}
         for tweet in tweets:
-            print tweet
             result["options"].append({"value": tweet.text})
     except Exception, e:
         print e
@@ -37,7 +36,6 @@ def query_fulltext(request, query):
         tweets = Tweet.objects.filter(text__search=query)
         result = {"options": []}
         for tweet in tweets:
-            print tweet
             result["options"].append({"value": tweet.text})
     except Exception, e:
         print e

### 2014-12-10 typeahead_demo/typeahead/typeahead/settings.py

@@ -64,7 +64,7 @@ DATABASES = {
     'default': {
         'ENGINE': 'django.db.backends.mysql',
         'NAME': "typeahead",
-        'USER': 'admin',
+        'USER': 'root',
         'PASSWORD': 'koobkoob',
         'HOST': 'localhost',   # Or an IP Address that your DB is hosted on
         'PORT': '3306',
@@ -90,4 +90,4 @@ USE_TZ = True
 
 STATIC_URL = '/static/'
 STATICFILES_DIRS = (os.path.join(BASE_DIR, "static"),)
-
+STATIC_ROOT = '/static_files/'

### 2014-12-10 typeahead_demo/typeahead/tweets/views.py
switch over to smaller dataset for live demo

@@ -45,7 +45,7 @@ def query_fulltext(request, query):
 
 def get_tweets(request):
     try:
-        file = open(os.path.join(PROJECT_ROOT, 'xad'))
+        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
     except Exception, e:
         print e    
 
@@ -63,7 +63,7 @@ def delete_tweets(request):
 
 def insert_tweets1(request):
     try:
-        file = open(os.path.join(PROJECT_ROOT, 'xad'))
+        file = open(os.path.join(PROJECT_ROOT, 'tweets2.json'))
         tweets = json.loads(file.read())
         tweets = tweets["tweets"]
         for tweet in tweets:

### 2014-12-10 typeahead_demo/typeahead/static/code/fulltext_demo.js
add time test to demo

@@ -3,6 +3,10 @@ function now() {
 	return self.performance? performance.now() : Date.now();
 }
 
+test_words = ["sleep", "access", "halo", "party", "feel", "better", "fellow", "hair", "car", "knit", "tomorrow", "twitter", "hometown",
+				"skill", "finger", "legal", "body", "day", "email", "friend"];
+
+
 var databaseName = "LucyTest";
 var dataFile = "data/xad";
 var currentDBVersion;
@@ -99,6 +103,52 @@ build_invindex = function () {
 	};
 };
 
+
+//do a time test
+$('#time-test').click( function () {
+
+	total_time = 0.0;
+	total_count = 0;
+	for (var num in test_words) {
+		var query = test_words[num];
+
+	  	console.log(query);
+	  	
+	  	
+	  	if (search_setting === 1) {
+	  		var start = (new Date()).getTime();
+		  	$.ajax({
+		  		url: '/search_fulltext/' + query,
+		  		success: function (data) {
+			        var res = data.options;
+			        var stop = ((new Date()).getTime() - start);
+			        
+			        total_time += stop;
+			        total_count += 1;
+			        console.log(stop);
+			      },
+				async: false
+		    });
+		}
+		if (search_setting === 2) {
+			var start = (new Date()).getTime();
+			
+			var index_res = search_client(query);
+			index_res.start = start;
+			index_res.onsuccess = function() {
+				var res = index_res.result.options;
+				var stop = ((new Date()).getTime() - index_res.start);
+				total_time += stop;
+		        total_count += 1;
+		        console.log(stop);
+			};
+	
+		}
+	}
+	$("#timer").text((total_time/total_count) + "ms");
+});
+
+
 $(".search").submit(function(evt) {
 	evt.preventDefault();
   	var start = (new Date()).getTime();
@@ -133,7 +183,6 @@ $(".search").submit(function(evt) {
 		var index_res = search_client(query);
 
 		index_res.onsuccess = function() {
-			console.log(index_res);
 			
 			var res = index_res.result.options;
 			var stop = ((new Date()).getTime() - start) + 'ms';

### 2014-12-10 typeahead_demo/typeahead/static/code/typeahead_demo.js

@@ -3,6 +3,10 @@ function now() {
 	return self.performance? performance.now() : Date.now();
 }
 
+
+test_words = ["sleep", "access", "halo", "party", "feel", "better", "fellow", "hair", "car", "knit", "tomorrow", "twitter", "hometown",
+				"skill", "finger", "legal", "body", "day", "email", "friend"];
+
 var databaseName = "LucyTest";
 var dataFile = "data/tweets2.json";
 var currentDBVersion;
@@ -77,6 +81,53 @@ $('#send-data2').click( function () {
 	    }
 	});
 });
+
+//do a time test
+$('#time-test').click( function () {
+
+	total_time = 0.0;
+	total_count = 0;
+	for (var num in test_words) {
+		for (var i = 1; i <= test_words[num].length; i++) {
+			var query = test_words[num].substring(0,i);
+
+		  	console.log(query);
+		  	if (search_setting === 1) {
+		  		var start = (new Date()).getTime();
+			  	$.ajax({
+			  		url: '/search/' + query,
+			  		success: function (data) {
+				        var res = data.options;
+				        var stop = ((new Date()).getTime() - start);
+				        
+				        total_time += stop;
+				        total_count += 1;
+				        console.log(stop);
+				      },
+					async: false
+			    });
+			}
+			if (search_setting === 2) {
+				var start = (new Date()).getTime();
+				
+				var result = search_client(query);
+				result.start = start;
+				result.onsuccess = function() {
+					var res = result.result.options;
+					var stop = ((new Date()).getTime() - result.start);
+					total_time += stop;
+			        total_count += 1;
+					console.log(stop);
+					
+					
+				};
+		
+			}
+		}
+	}
+	$("#timer").text((total_time/total_count) + "ms");
+});
+
  
 $('#the-basics .typeahead').typeahead({
   hint: true,

### 2014-12-10 typeahead_demo/typeahead/static/code/fulltext_demo.js
user has to manually test, but now we have numbers

@@ -103,19 +103,23 @@ build_invindex = function () {
 	};
 };
 
+var counter = 0;
+var c_total_time = 0.0;
+var c_total_cnt = 0;
 
 //do a time test
 $('#time-test').click( function () {
 
-	total_time = 0.0;
-	total_count = 0;
-	for (var num in test_words) {
-		var query = test_words[num];
-
-	  	console.log(query);
-	  	
-	  	
-	  	if (search_setting === 1) {
+	if (search_setting === 1) {
+		total_time = 0.0;
+		total_count = 0;
+		
+		for (var num in test_words) {
+			var query = test_words[num];
+	
+		  	console.log(query);
+		  	
+		  	
 	  		var start = (new Date()).getTime();
 		  	$.ajax({
 		  		url: '/search_fulltext/' + query,
@@ -130,22 +134,29 @@ $('#time-test').click( function () {
 				async: false
 		    });
 		}
-		if (search_setting === 2) {
-			var start = (new Date()).getTime();
-			
-			var index_res = search_client(query);
-			index_res.start = start;
-			index_res.onsuccess = function() {
-				var res = index_res.result.options;
-				var stop = ((new Date()).getTime() - index_res.start);
-				total_time += stop;
-		        total_count += 1;
-		        console.log(stop);
-			};
-	
-		}
+		$("#timer").text((total_time/total_count) + "ms");
 	}
-	$("#timer").text((total_time/total_count) + "ms");
+	
+
+	if (search_setting === 2) {
+		var start = (new Date()).getTime();
+		
+		var query = test_words[counter];
+		counter++;
+		console.log(query);
+		var index_res = search_client(query);
+		index_res.start = start;
+		index_res.onsuccess = function() {
+			var res = index_res.result.options;
+			var stop = ((new Date()).getTime() - index_res.start);
+			c_total_time += stop;
+	        c_total_cnt += 1;
+	        $("#timer").text((c_total_time/c_total_cnt) + "ms");
+	        console.log(stop);
+		};
+
+	}
+	
 });
 
 

### 2014-12-10 typeahead_demo/typeahead/static/code/typeahead_demo.js

@@ -82,50 +82,70 @@ $('#send-data2').click( function () {
 	});
 });
 
+var counter = 0;
+var counter2 = 1;
+var c_total_time = 0.0;
+var c_total_cnt = 0;
+
 //do a time test
 $('#time-test').click( function () {
 
-	total_time = 0.0;
-	total_count = 0;
-	for (var num in test_words) {
-		for (var i = 1; i <= test_words[num].length; i++) {
-			var query = test_words[num].substring(0,i);
 
-		  	console.log(query);
-		  	if (search_setting === 1) {
-		  		var start = (new Date()).getTime();
-			  	$.ajax({
-			  		url: '/search/' + query,
-			  		success: function (data) {
-				        var res = data.options;
-				        var stop = ((new Date()).getTime() - start);
-				        
-				        total_time += stop;
-				        total_count += 1;
-				        console.log(stop);
-				      },
-					async: false
-			    });
+	if (search_setting === 1) {
+		total_time = 0.0;
+		total_count = 0;
+		for (var num in test_words) {
+			for (var i = 1; i <= test_words[num].length; i++) {
+				var query = test_words[num].substring(0,i);
+	
+			  	console.log(query);
+			  	
+			  		var start = (new Date()).getTime();
+				  	$.ajax({
+				  		url: '/search/' + query,
+				  		success: function (data) {
+					        var res = data.options;
+					        var stop = ((new Date()).getTime() - start);
+					        
+					        total_time += stop;
+					        total_count += 1;
+					        console.log(stop);
+					      },
+						async: false
+				    });
+				}
 			}
-			if (search_setting === 2) {
-				var start = (new Date()).getTime();
-				
-				var result = search_client(query);
-				result.start = start;
-				result.onsuccess = function() {
-					var res = result.result.options;
-					var stop = ((new Date()).getTime() - result.start);
-					total_time += stop;
-			        total_count += 1;
-					console.log(stop);
-					
-					
-				};
-		
-			}
+			$("#timer").text((total_time/total_count) + "ms");
 		}
+			
+		if (search_setting === 2) {
+			var start = (new Date()).getTime();
+			
+			
+			var word = test_words[counter];
+			var query = word.substring(0,counter2);
+			if (counter2 === word.length) {
+				counter++;
+				counter2 = 1;
+			} else {
+				counter2++;
+			}
+			console.log(query);
+			
+			var result = search_client(query);
[…]

### 2014-12-10 code/trieindex-new.js
Small poster edits

@@ -277,11 +277,13 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
 								}
 							}
 							else {
-								throw new Error("Can't find " + node.prefix + " in the children of " + parentPrefix);
+								//throw new Error("Can't find " + node.prefix + " in the children of " + parentPrefix);
+								cursor.continue();
 							}
 						}
 						else {
-							throw new Error("Can't find parent of " + node.prefix + ". I tried " + parentPrefix + " but no avail");
+							//throw new Error("Can't find parent of " + node.prefix + ". I tried " + parentPrefix + " but no avail");
+							cursor.continue();
 						}
 					}
 					

### 2014-12-10 paper/paper.tex
add to section on ranking

@@
 There are many ways to score and rank results of a search query.
-Some techniques, such as \textit{tf-idf}, require precalculated document metadata.
+Some techniques, such as \textit{tf-idf}, require constant recalculation of document metadata.
 Others require knowning positional information about a word within a document.
@@
 The PostgreSQL's functions take into account how often the query terms appear in the document as well as how close together the terms are in the document.
-However, it is possible for a developer to implement their own ranking function and replace ours with theirs within Lucy.js.
+However, it is possible for a developer to implement their own ranking function and replace ours with theirs within Lucy.js if they so wish.
 
-The default rank that we implement is
+One function that we provide is \texttt{Lucy.calculateWeight()}, which counts the number of words in the search query that appear in the document.
+The other ranking we provide is \texttt{Lucy.calculateCoverDensity()}, which implements Cover Density Ranking~\cite{li2002improvement}, an algorithm that takes into account positional information.
+For this algorithm to work, we need to store at index creation time the positions that the word appears in the document.
+Both functions take in an optional \texttt{normalization} integer where the developer can specify whether they are interested in normalizing by document length or unique number of words in the document.
+If normalization is desired, then at index creation time, we calculate these measures and store them with the document object.
 

### 2014-12-10 code/index.js

@@ -1,31 +1,0 @@
-
-/*
-Constructs a TrieIndex for pattern-matching.
-data - array of strings to be indexed
-*/
-var TrieIndex = function(data) {
-    // Perform pattern-matching (prefix/suffix search), return whole string
-    this.get = function(pattern) {
-        return null;
-    };
-
-    // Normalize data before insertion (no tokenization for pattern-matching)
-    this.insert = function(text) {};
-
-    return this;
-};
-
-/*
-Constructs a BTreeIndex for full-text search.
-data - array of strings to be indexed
-*/
-var BTreeIndex = function(data) {
-    // Perform index search for a tokenized word
-    this.get = function(word) {
-        return null;
-    };
-
-    // Normalize and tokenize data before insertion.
-    this.insert = function(text) {};
-    return this;
-};

### 2014-12-11 code/trieindex.js
added graphs for trieindex max depth lookups

@@ -82,7 +82,7 @@ var TrieIndex = function(objStore, name, field, mode, maxDepth) {
                                 var matches = result.wordMap[key];
                                 for (var i=0; i < matches.length; i++) {
                                     var m = matches[i];
-                                    docIdsDict[m] = docIdsDict[docId] || 0;
+                                    docIdsDict[m] = docIdsDict[m] || 0;
                                     docIdsDict[m] += weight;
                                 }
                             }

### 2014-12-11 paper/paper.tex
added section on max depth

@@
 
-\paragraph{Trie Node Object Store}
+\subsubsection{Trie Node Object Store}
 Each entry in the object store represents a different node in the trie. The structure of entries in the object store is as follows:
@@
 Inserting a word from a given document therefore involves appending that document's id into the doc\_ids of each node along the path corresponding to the word.
+The structure of the trie is shown in Figure ******.
+It is important to note that this approach is not very scalable; since each node stores a list of matching document ids, interior nodes closer to the root of the trie could store large lists of these ids.
+However, the benefit is that searches in the trie do not require traversal all the way down to the leaves.
+Matches can be returned as soon as the prefix is traced in the trie, and no further traversal along subtrees is needed.
+An alternative design to the trie index is the Hybrid Trie discussed in the next section.
 
-\paragraph{Trie Node Index}
+\subsubsection{Trie Node Index}
 While the structure of the trie node object store optimizes lookups by node id, this is not particularly useful for trie traversal.
@@
 
-\paragraph{Lookups}
+\subsubsection{Lookups}
 Lookups in the trie index are performed by traversing the trie downward, character by character in the search pattern.
@@
 
-\paragraph{Tokenization}
+\subsubsection{Tokenization}
 Unlike with the inverted index, words are not stemmed before insertion or lookups.
@@
 
-\paragraph{Synchronization}
+\subsubsection{Synchronization}
 Due to the manner in which letters in a word need to be inserted sequentially in a trie, much of IndexedDB's built-in asynchronous behavior cannot be used to improve performance.
@@
 
-\subsection{Lossy Search Trees}
+\subsubsection{Depth-Limiting}
+To limit the size of trie indexes, an optional maximum depth can be set.
+If set, words longer than the depth are cut off so that the remainder substrings are stored at the leaves.
+Figure ****** shows the structure of the same trie as before, but with a maximum depth of 4.
+Leaf nodes store this substring data as a mapping from substring to document ids containing that substring.
+During lookups, if the maximum depth of the trie is reached, this map is searched for matches.
+So while depth-limiting trie indexes can limit the number of trie nodes that need to be traversed upon lookups, they incur the cost of searching these maps at the leaves.
+If the max depth parameter is too small, these maps can be large and slow down search significantly.
+If set too large, the max depth parameter has no effect.
+
+\subsection{Hybrid Tries}
 

### 2014-12-11 paper/paper.tex
added performance section on depth limiting

@@
 
+\subsubsection{Comparing Different Index Types}
+
+\subsubsection{Depth-Limiting for Tries}
+As seen in Figure *****, the maximum depth parameter has an effect on lookup times in trie indexes.
+The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches.
+A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing max depths.
+The lookup time tends to decrease as the maximum depth increases; this is because depth cutoffs can result in slow searches through word mappings stored on leaf nodes (see section **** for details).
+The difference in times is more pronounced for the term ``feel'', with a drop from 26.78ms to 18.05ms.
+For the term ``james'', lookup times are much closer together and not as affected by depth limits.
+This is due to the fact that ``feel'' yielded many more results (85 results) than ``james'' (4 results), suggesting that more potential matches had to be searched at the leaf nodes for ``feel'' than for ``james''.
+Results for ``wait'' are between the others, and also show a moderate drop in lookup time as the maximum depth increases.
+This is most likely because ``wait'' produced a moderate 36 results, and therefore a moderate number of terms were searched at the leaves.
+
+The data also shows that the number of results has an  impact on lookup time.
+The three graphs are tiered such that ``feel'', with the most results, is also the slowest query.
+While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.
+
+\subsubsection{Client-side vs. Server-side Search}
+
 \section{Evaluation}

### 2014-12-11 paper/paper.tex
added figures for tries to paper

@@
 
+\begin{figure}[h!]
+  \centering
+   \includegraphics[scale=.35]{trie_figure}
+  \caption{Structure of a trie index with two input tweets.
+The tweets are first tokenized and stop words are removed.
+Note that document ids are stored in every node.
+An artificial root node is created as the root of the trie.}
+\end{figure}
+
 \subsubsection{Trie Node Index}
@@
 
+\begin{figure}[h!]
+  \centering
+   \includegraphics[scale=.35]{trie_maxdepth_figure}
+  \caption{Structure of a trie index with a maximum depth of 4.
+If a word gets cut off by the depth limit, the substring remainder is stored at the leaves.
+Each substring remainder maps to a list of document ids with that remainder.}
+\end{figure}
+
 \subsection{Hybrid Tries}

### 2014-12-11 paper/paper.tex
added max depth performance graph
fixed structure of performance section

@@
 
-\subsection{Performance and Comparison}
+\section{Performance and Comparison}
 
-\subsubsection{Comparing Different Index Types}
+\subsection{Comparing Different Index Types}
 
-\subsubsection{Depth-Limiting for Tries}
+\subsubsection{Index Creation}
+
+\subsubsection{Index Lookups}
+
+\subsection{Depth-Limiting for Tries}
 As seen in Figure *****, the maximum depth parameter has an effect on lookup times in trie indexes.
@@
 
+\begin{figure}[h!]
+   \includegraphics[scale=.43]{trie_maxdepth_graph}
+  \caption{Maxiumum depth vs lookup times for a prefix trie index.
+A depth of ``None'' indicates that there is no limit.
+The results for three different search terms are shown.
+The dataset size was roughly 2100 tweets.}
+\end{figure}
+
 The data also shows that the number of results has an  impact on lookup time.
@@
 
-\subsubsection{Client-side vs. Server-side Search}
+\subsection{Client-side vs. Server-side Search}
 

### 2014-12-11 code/demo.js
baseline search for perf comparison

@@ -128,29 +128,36 @@ $('#build-suffix-index').onclick = function () {
 
 };
 
-function search(db, query, objectStore) {
+function search(db, query, objectStore, optionalArgs) {
 	var startTime = now();
-	var type = "inverted";
-	var indexName = objectStore + '_text';
-	
-	if (/%$/.test(query)) { // Ends with %?
-		// Prefix search
-		type = "prefix";
-		indexName += '_' + type;
-	}
-	else if (query.indexOf('%') === 0) { // Starts with %?
-		// Suffix search
-		type = "suffix"
-		indexName += '_' + type;
-	}
-	
-	var transaction = db.transaction([objectStore, indexName], "readonly");
-	var objectStore = transaction.objectStore("tweets");
+    var request;
+    
+    if (optionalArgs && optionalArgs.noIndex) {
+        // optional arg to revert to a baseline search of objectStore
+        request = Lucy.baselineSearch(db, query, objectStore);
+    } else {
+        var type = "inverted";
+        var indexName = objectStore + '_text';
+        
+        if (/%$/.test(query)) { // Ends with %?
+            // Prefix search
+            type = "prefix";
+            indexName += '_' + type;
+        }
+        else if (query.indexOf('%') === 0) { // Starts with %?
+            // Suffix search
+            type = "suffix"
+            indexName += '_' + type;
+        }
+        
+        var transaction = db.transaction([objectStore, indexName], "readonly");
+        var objectStore = transaction.objectStore("tweets");
 
-	var index = objectStore.index("text", type);
-	
-	// get returns a single entry (one with lowest key value)
-	var request = index.get(query.replace(/%/g, ''));
+        var index = objectStore.index("text", type);
+        
+        // get returns a single entry (one with lowest key value)
+        request = index.get(query.replace(/%/g, ''));
+    }
 	
 	request.onerror = function(evt) {
 		console.error(evt, query);

### 2014-12-11 code/lucy.js

@@ -59,6 +59,7 @@ Lucy.tokenize = function(string, options) {
 	options = options || {};
 	options.disableStemming = !!options.disableStemming;
 	options.enablePosition = !!options.enablePosition;
+    options.allowStopWords = !!options.allowStopWords;
 	
 	string = string.toLowerCase();
 	var tokens = string.match(/\w+/g);
@@ -73,7 +74,11 @@ Lucy.tokenize = function(string, options) {
 	for (var i=0; i<tokens.length; i++) {
 		var stem = options.disableStemming? tokens[i] : stemmer(tokens[i]);
 		
-		var count = Lucy.isStopWord(tokens[i])? stopwordCount : tokenCount;
+        if (options.allowStopWords) {
+            var count = tokenCount;
+        } else {
+            var count = Lucy.isStopWord(tokens[i])? stopwordCount : tokenCount;
+        }
 		
 		
 		if (!options.enablePosition) {
@@ -203,6 +208,41 @@ Lucy.normalizeWeights = function(doc_obj, norm_level) {
 	}
 };
 
+Lucy.baselineSearch = function(db, query, objectStoreName) {
+    var transaction = db.transaction([objectStoreName], "readonly");
+    var objectStore = transaction.objectStore(objectStoreName);
+    var opencursor = objectStore.openCursor();
+    var matches = [];
+    var ret = new IDBIndexRequest(objectStore, transaction);
+    ret.result = [];
+    opencursor.onsuccess = function (evt) {
+        var cursor = evt.target.result; 
+        if (cursor) {
+            var text = cursor.value["text"];
+            var docId = cursor.value["id"];
+            var queryText = query.replace(/%/g, '');
+
+            // tokenize string
+            var tokens = Object.keys(Lucy.tokenize(queryText, {disableStemming: true, allowStopWords: true}).tokens);
+            for (var i=0; i<tokens.length; i++) {
+                if (text.indexOf(tokens[i]) != -1) {
+                    ret.result.push(cursor.value);
+                    break;
+                }
+            }
+            cursor.continue(); 
+        } else {
+            ret.onsuccess();
+        }
+    };
+    
+    opencursor.onerror = function (evt) {
+        console.log(evt);
+        ret.onerror();
+    };
+
+    return ret;
+};
 
 
 /*

### 2014-12-11 paper/paper.tex
add figures to paper

@@
 
-In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give further details of our implementation.
+In this section, we explain the overall goals and architecture of the Lucy.js system, how it fits into IndexedDB, as well as give further details of our implementation.
+
+\begin{figure}[]
+   \includegraphics[scale=.43]{arch}
+  \caption{caption here.}
+\end{figure}
 
@@
 
+\begin{figure}[h!]
+   \includegraphics[scale=.53]{query-times}
+  \caption{caption here}
+\end{figure}
+
 \subsection{Depth-Limiting for Tries}
@@
 
+\section{Evaluation and Applications}
+
 \subsection{Client-side vs. Server-side Search}
 
-\section{Evaluation}
+\begin{figure}[h!]
+   \includegraphics[scale=.53]{demo_results}
+  \caption{caption here.}
+\end{figure}
 

### 2014-12-11 paper/paper.tex
fix auther section
clean up intro and related work

@@
 
-\numberofauthors{3}
+\numberofauthors{1}
 
 \author{
-\alignauthor
-Amy X. Zhang\\
-       \email{axz@mit.edu}
-\alignauthor Lea Verou\\
-       \email{leaverou@mit.edu}
-\alignauthor Manali Naik\\
-       \email{manalinaik@mit.edu}
+\alignauthor Amy X. Zhang, Lea Verou, Manali Naik\\
+\vspace{.2cm}
+	\affaddr{MIT CSAIL}\\
+	\affaddr{Cambridge, MA USA} \\
+       \email{\{axz, leaverou, mnaik\}@mit.edu}
 }
@@
 
-Many applications on the web use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
-However, standard client side databases within browsers do not currently support full-text searching. 
-In this paper, we describe a client-side search engine built on top of IndexedDB that makes use of several types of indexes common to many well-known server-side search engines.
-We compare the performance of different indexes on different types of full-text content and queries and find that....
-We also compare the performance of our system with that of fully server side systems and examine scenarios where a hybrid approach may be fastest. We find that...
-
+Many applications on the web today use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
+However, standard client side databases within browsers do not currently support full-text searching, and it is not clear the best way to engineer full-text indexes on top of the existing infrastructure.
+In this paper, we introduce Lucy.js, a fully client-side search engine built as an extension of the existing well-supported IndexedDB API.
+We compare the performance of the different indexes we implement on different types of full-text content and queries.
+We find that a hybrid approach combining inverted indexes and tries perform the best, particularly on larger datasets.
+We also implement various real-life applications of our system and compare the performance of our system with that of using a fully server side system.
+We find that given the costs of network latency, our approach is signficantly faster than relying on a server-side search engine.
+Finally, we discuss how our system may open up novel web application and data storage designs that solely use client-side search engines or combine both client and server search engines.
 \end{abstract}
@@
 
-Most web applications store the bulk of their data on a backend web server or on the cloud, and the client side queries the server when it needs to access data.
+A typical web application stores the bulk of its data on a backend web server or on the cloud, and the client side queries the server when it needs to access data.
 As web applications have become more interactive and responsive in the past several years, developers have built larger and more complex web servers to support them.
-However, this separation of data from the client introduces significant network effects that can often lead to noticeable latency, as data may be retrieved from servers that are very far away.
+However, this separation of data from the client introduces significant network effects that can often lead to noticeable latency, as large amounts of data may need to be retrieved from servers that are very far away.
 
-In recent years, more applications are being built that heavily rely on client-side storage and offload data processing to web browsers.
+In recent years, more applications have been built that heavily rely on client-side storage and offload data processing to web browsers.
 Today most commonly used browsers support the current HTML5 standards, which include a persistent client-side DBMS with the name IndexedDB that is accessible via a set of JavaScript APIs.
 The ability to use local storage enables real-time interactivity on data-intensive and collaborative tasks by reducing the number of network roundtrips.
-These have been useful for many large and complex web applications such as massive multi-player games CITE that would have previously only existed as desktop applications.
-Issues around privacy and ownership of data have also given rise to a number of applications CITE that move most or all of data storage to the client~\cite{bilenko2011predictive}. 
-Finally, many popular smartphone browsers rely on wireless signals to transmit information, which is prone to failure in areas with poor signal, suggesting that applications that are entirely client-side or applications that retains some functionality during downtime could be useful~\cite{balasubramanian2012findall}.
+These have been useful for many large and complex web applications such as massive multi-player games and collaborative editing tools that would have previously only existed as desktop applications.
+Issues around privacy and ownership of data have also given rise to a number of applications that aim to move sensitive data analysis and data storage to the client~\cite{bilenko2011predictive, khoshgozaran2009private}.
+Finally, most smartphone browsers rely on wireless signals to transmit information, which is prone to failure in areas with poor signal, suggesting that applications that are entirely client-side or applications that retains some functionality during downtime could be useful~\cite{balasubramanian2012findall}.
 
-While much work has been done to make it easier to store and query data in the browser~\cite{benson2010sync}, currently there are few known ways to conduct full-text searching on the client side.
-Search engines are a very important component of a large number of applications and are necessary to make sense of many forms of full-text data such as chat or private messages, social media content, search queries, and webpage titles and content.
+While much work has focused on making client-side storage and query easier~\cite{benson2010sync}, currently there are few known ways to conduct full-text searching on the client side.
+This is a problem because search engines are a very important component of a large number of applications and are necessary to make sense of many forms of full-text data such as chat or private messages, social media content, search queries, and webpage titles and content.
 As personalization has become more important for search engines, many designers of systems and architectures have highlighted the opportunities for client-side data computation~\cite{bharat2000searchpad,teevan2005personalizing}.
 Issues of privacy are also important when it comes to social applications and searching over personal data.
-New social applications such as CITE have been built that can operate without any servers, instead using peer-to-peer or Bluetooth connections.
 However, while it is possible to store full-text content on the client side, there is still no way to conduct full-text search on the client side at a reasonable speed, preventing most data computation necessary for a fully-featured search engine.
@@
 
-In this paper, we introduce Lucy.js, a fully client-side JavaScript search engine that is an extension of the current IndexedDB API CITE.
+In this paper, we introduce Lucy.js, a fully client-side JavaScript search engine that is an extension of the current IndexedDB API~\cite{indexeddb}.
 It has been designed to be easy for anyone currently using IndexedDB in their application to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communication.
-There are also no dependencies on a server or on a network, so it can be harnessed offline.
-In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene CITE and within PostgreSQL CITE, including inverted indexes, prefix and suffix tries, and lossy search trees.
-We discuss how we managed to create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks.
+There are also no dependencies on a server or network, so it can be harnessed offline.
+In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and variations on these.
+We discuss how we create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks.
 We compare their performance on different types of queries and with different sizes and types of datasets.
-We find that...
+We find that...FILL IN HERE.
 
-Finally, we imagine the potential real-world use cases for a client-side search engine and how performance may be improved using this system.
-We implement a set of applications that would be reasonable in the real world and measure performance between fully client-side, fully server-side, and mixtures of both databases to respond to queries.
-We find that....
-This research demonstrates not only the feasibility of having search engines within the browser but also the potential for new applications and improved performance of existing applications through the additional capabilities provided by a client-side search engine.
+We evaluate our system on several real-world applications and compare performance of fully client-side and fully server-side data architectures.
+We find that on the whole, using client-side indexes significantly decreases the time to complete search queries due to the network latency brought on by communicating with a remote server.
+Finally, we consider potential novel systems and architectures that could be implemented that take advantage of a client-side search engine.
+This research demonstrates not only the feasibility of having fast search engines within the browser but also the improved performance of existing applications and the potential for new applications through the additional capabilities provided by a client-side search engine.
 
@@
 
-Though previous HTML standards and browser capabilities were more limited, the idea of using of the client side for data storage and data computation has been around for many years. 
+Though previous HTML standards and browser capabilities were more limited, the idea of using of the client side for data storage and data computation has been around for many years~\cite{bharat2000searchpad}.
 Some research has looked into building tools to support an architecture that includes client-side databases, including toolkits to synchronize data between the client and server~\cite{benson2010sync}.
@@
 When it comes to search engines, specifically web search, prior work has found that 40\% to 60\% of search queries are re-finding queries~\cite{teevan2005personalizing}.
-This finding has lead to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,bharat2000searchpad,balasubramanian2012findall}.
-Prior work in this area have also highlighted how web search can often be a highly personal activity, and that web search should be personalized to the user to improve accuracy.
+This finding has led to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,bharat2000searchpad,balasubramanian2012findall}.
+Prior work in this area have also highlighted how web search can often be a highly personal activity, and that web search could be personalized to the user to improve accuracy.
 Personal information can then be stored on the client side as this information is primarily useful for this particular client~\cite{teevan2005personalizing}.
@@
 However, this search engine is not usable with other browsing apps or other phones.
-Because we build an extension on top of IndexedDB, our search engine will be able to work for all browsers, desktop or mobile, that support IndexedDB, which is the majority of them.
+Because we build an extension on top of IndexedDB, our search engine will be able to work for all browsers, desktop or mobile, that support IndexedDB.
 
-Some prototypes of client-side search engines have previously been built CITE. Currently, all existing implementations only create basic inverted indexes.
-For instance, previous research has demonstrated that it is feasible to store an inverted index within IndexedDB~\cite{lin:jscene} though it is much slower than using a server-side application such as Lucene.
+Some prototypes of client-side search engines have previously been built. However, all existing implementations only create basic inverted indexes.
+For instance, previous research has demonstrated that it is feasible to store an inverted index within IndexedDB~\cite{lin:jscene} though it was found to be much slower than using a server-side application such as Lucene.
 We improve on these works by implementing different types of indexes for full-text search and comparing their performance. 
@@
 Instead, our system uses IndexedDB object stores to hold indexes.
-Also, the YDN-DB module\footnote{https://github.com/yathit/ydn-db-fulltext} which wraps around the IndexedDB API, requires developers to migrate over to use the YDN system.
-Instead our system is simply an extension of IndexedDB.
+Also, the YDN-DB module\footnote{https://github.com/yathit/ydn-db-fulltext} which implements an inverted index, wraps around the IndexedDB API, requiring developers to migrate over to use the YDN system.
+Instead our system is simply an extension of the IndexedDB API, making it easy to integrate.
 We also demonstrate several real-life situations that may call for a hybrid client and server database architecture for full-text search and measure their speed.
@@
 
+Newer peer-to-peer standards such as WebRTC for browsers may make more client-heavy social and interactive applications feasible in the future.
+
 \section{Future Work}

### 2014-12-11 paper/paper.tex
Weird merge conflicts
Added inverted index figure

@@
 
-\title{Client-Side Indexes for Fast Full-Text Searching}
+\title{Lucy.js: Client-Side Indexes for Fast Full-Text Searching}
 
@@
 	\includegraphics[scale=.43]{arch}
-  \caption{caption here.}
+	\caption{Architecture of Lucy.js}
 \end{figure}
@@
 
+\begin{figure}
+  \centering
+   \includegraphics[scale=.35]{inverted-index}
+  \caption{Structure of a simplified inverted index, as it would be stored in IndexedDB.
+Note that our implementation also includes additional information about the position of the tokens in the document (among other things), for better ranking}
+\end{figure}
+
 \subsection{Inverted Indexes}

### 2014-12-11 paper/paper.tex
Added hybrid trie figure
update system section

--- 2014-12-11 paper/paper.tex
@@
 
-The two main goals of Lucy.js we aimed to achieve while implementing it were: (i) to build a search engine extension to IndexedDB that is easy to use and similar to the existing IndexedDB API, and (ii) to create different types of indexes that can all be used for full-text searching and find out which are more suited to which tasks and what the trade-offs are.
-We design Lucy.js so that it is easy as a developer to be able to specify which type of index to make on a field based on the type of queries that will most often be submitted.
+The two main goals of Lucy.js we aimed to achieve during implementation were: (i) to build a search engine extension to IndexedDB that is easy to use and similar to the existing IndexedDB API, and (ii) to create different types of indexes that can all be used for full-text searching and find out which are more suited to which tasks and what the trade-offs are.
+We design Lucy.js so that it is easy as a developer to be able to specify what type of index they wish to make on a field.
 
@@
 In LevelDB, keys and values are arbitrary byte arrays and data is stored in sorted order by key.
-It supports batch writing, put and get commands using the key, and forward and backward iteration over keys.
+It supports batch writing, secondary indexes, \texttt{put} and \texttt{get} commands using the key, and forward and backward iteration over keys (range queries).
 
 The IndexedDB API supports transactions that rely on shared read and exclusive write locking.
-At transaction creation time, the code must specifies what kind of transaction it is (read-only, write-only, or read-write) and what object stores (similar to tables in a relational data store) it will access.
-Read-only transactions can run concurrently but transactions that write lock the specified object stores for the entire duration of the transaction.
-All transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function.
+At transaction creation time, the code must specify what kind of transaction it is (read-only, write-only, or read-write) and what object stores (similar to tables in a relational data store) it will access.
+Read-only transactions can run concurrently but transactions that write will lock the specified object stores for the entire duration of the transaction.
+All transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a \texttt{put} or a \texttt{get}, to happen and then pass a callback function.
 Then a notification via a DOM event is triggered when the operation actually completes, and the type of event returned tells whether the operation succeeded or failed.
 
-\subsection{Extending IndexedDB}
+\subsection{Extending IndexedDB with Lucy.js}
 
@@
 Otherwise, the creation of a full-text index is very similar to that of a normal index.
-Given the object store \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, key\_path\right)$} function for creating full-text indexes.
+Given the \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, key\_path\right)$} function for creating full-text indexes.
 We add an additional optional parameter of \texttt{type} which allows the developer to specify a type of full-text index they would like to build.
 The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}.
-If the developer does not specify a type, then a typical IndexedDB index would be created.
-Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on an object field \texttt{text} in an object store of Twitter tweets.
+*********UPDATE If the developer does not specify a type, then a typical IndexedDB index would be created.
+Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.
 
@@
 In our case, a given search query may return many results that have different levels of relevance to the query.
-For this reason, each object returned has an addition field called \texttt{score}, which has a relevancy value with higher being more relevant.
+For this reason, each object returned has an additional field called \texttt{score},  with higher being more relevant.
 In the next section, we go into more detail into how the score is calculated for different types of search queries.
-By default we return all relevant (\texttt{score} $>$ 0) objects in reverse order of \texttt{score}.
-
+By default we return all relevant (\texttt{score} $>$ 0) objects in descending\texttt{score} order. 
 However, a query can return a large number of items with low relevancy if the query contains a term that is common.
-In IndexedDB, there is an interface called \texttt{IDBKeyRange} that is used for when a user wishes to query a range of keys.
-We extend this interface to include ranges of \texttt{score} values, so that users can set a cutoff or range of the relevancy score.
-This feature is also one that is available in PostgreSQL as **********.
+We extend the \texttt{IDBKeyRange} interface to include ranges of \texttt{score} values, so that users can set a cutoff or range of the relevancy score.
 
 In the follow code snippet, we provide an example of a \texttt{get} function on the inverted index created in the last section.
-The object returned is an \texttt{IDBIndexRequest} object, which mimics the behavior of \texttt{IDBRequest}.
+The object returned by the second line is an \texttt{IDBIndexRequest} object which mimics the behavior of \texttt{IDBRequest}.
 
@@
 In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of any word to search for parts of words.
+This is possible with our trie indexes, as we explain in the next section.
 At this time, we do not support full regular expressions nor exact phrase matches.
@@
 Our system allows the developer to pass optional parameters to disable stopword removal or stemming when desired.
-It is also possible for developers to edit the stopwords list for a list that is domain-specific or otherwise more preferred.
+It is also possible for developers to replace the stopwords list for a list that is domain-specific or otherwise more preferred.
 
@@
 There are many ways to score and rank results of a search query.
-Some techniques, such as \textit{tf-idf}, require constant recalculation of document metadata.
-Others require knowning positional information about a word within a document.
-We define several built-in ranking functions derived from PostgreSQL's built-in \texttt{ts\_rank} and \texttt{ts\_rank\_cd} functions that take in a \texttt{normalization} option, with integer inputs providing different types of document normalizations\footnote{http://www.postgresql.org/docs/8.3/static/textsearch-controls.html}.
-The PostgreSQL's functions take into account how often the query terms appear in the document as well as how close together the terms are in the document.
+Some techniques, such as \textit{tf-idf}, require continual recalculation of document metadata.
+Others require knowing positional information about a word within a document.
+We define several built-in ranking functions similar to PostgreSQL's built-in \texttt{ts\_rank} and \texttt{ts\_rank\_cd} functions that take in a \texttt{normalization} option, with integer inputs providing different types of document normalizations\footnote{http://www.postgresql.org/docs/8.3/static/textsearch-controls.html}.
+PostgreSQL's functions take into account how often the query terms appear in the document as well as how close together the terms are in the document.
 However, it is possible for a developer to implement their own ranking function and replace ours with theirs within Lucy.js if they so wish.
@@
 The other ranking we provide is \texttt{Lucy.calculateCoverDensity()}, which implements Cover Density Ranking~\cite{li2002improvement}, an algorithm that takes into account positional information.
-For this algorithm to work, we need to store at index creation time the positions that the word appears in the document.
+For this algorithm to work, we need to store at index creation time the positions that the word appears in within the document.
 Both functions take in an optional \texttt{normalization} integer where the developer can specify whether they are interested in normalizing by document length or unique number of words in the document.
@@
 We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.
-The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, and \texttt{trieindex.js} that the developer must include in their HTML file.
+The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-new.js} *********UPDATE?
+plus some third-party files that the user must include in their HTML file.
 The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.
@@
 When a user calls \texttt{add},  \texttt{delete}, or \texttt{put} on an object store that has a full-text index, we additionally add the item to our indexes.
+In the following section, we explain in more detail our index implementations.
+The core code as well as examples can be found on Github\footnote{https://github.com/amyxzhang/lucy.js}.
 
@@
 
-We looked to many existing implementations of search engines and the indexes they used. Reverse indexes in Lucene. GiN and GiST indexes in PostgreSQL. Prefix and suffix tries from
+We looked to many existing implementations of search engines and the indexes they use to decide what indexes to build, such as inverted indexes in Lucene and GiN and GiST indexes in PostgreSQL.
+We initially implemented an inverted index as well as prefix and suffix tries, before also developing a hybrid trie combining elements of both inverted index and tries as a third index.
 

### 2014-12-11 paper/paper.tex
Minor typo

@@
 We also implement various real-life applications of our system and compare the performance of our system with that of using a fully server side system.
-We find that given the costs of network latency, our approach is signficantly faster than relying on a server-side search engine.
+We find that given the costs of network latency, our approach is significantly faster than relying on a server-side search engine.
 Finally, we discuss how our system may open up novel web application and data storage designs that solely use client-side search engines or combine both client and server search engines.
@@
 
+\begin{figure}[h!]
+  \centering
+   \includegraphics[scale=.4]{hybrid-trie}
+  \caption{Structure of a hybrid trie.}
+\end{figure}
+
 \section{Performance and Comparison}

### 2014-12-11 paper/paper.tex
section on inverted index

--- 2014-12-11 paper/paper.tex
@@
 In this section, we explain the overall goals and architecture of the Lucy.js system, how it fits into IndexedDB, as well as give further details of our implementation.
+In Figure~\ref{system}, the overall architecture is shown as well as a simplified workflow for a typical \texttt{get} call on an inverted index.
 
@@
 	\caption{Architecture of Lucy.js}
+	\label{system}
 \end{figure}
@@
 We looked to many existing implementations of search engines and the indexes they use to decide what indexes to build, such as inverted indexes in Lucene and GiN and GiST indexes in PostgreSQL.
-We initially implemented an inverted index as well as prefix and suffix tries, before also developing a hybrid trie combining elements of both inverted index and tries as a third index.
+We initially implemented an inverted index as well as prefix and suffix tries, before also developing a hybrid trie combining elements of both inverted index and tries as a third index.:
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=.35]{inverted-index}
+  \caption{Structure of a simplified inverted index, as it would be stored in IndexedDB.
+Note that our implementation can also include additional information about the position of the tokens in the document (among other things), for better ranking}
+\label{invindex}
+\end{figure}
 
 \subsection{Inverted Indexes}
+
+In an inverted or reverse index, tokens taken from the full-text field make the keys of this object store.
+The value given a token key is a set of document ids that correspond to the documents that contain this token in that field.
+A example of what a inverted index could look like is given in Figure~\ref{invindex}.
+Our implementation of an inverted index is relatively straightforward, as the structure is suited to a key-value store.
+When the user wishes to use Cover Density Ranking to compute relevancy scores, we also store positions of tokens along with the document ids.
+We comma delinate positions, keep them in sorted order, and separate them from the document id with a colon.
+For example, given the data in Figure~\ref{invindex}, we could have \texttt{"tweet":\{docIds:[3:0,7,10]\}}.
+
+When creating an inverted index, we first create a new object store that will hold the index.
+Then we use an \texttt{IDBCursor} over the original object store to iterate through all documents in succession.
+After tokenizing, removing stopwords, and stemming the tokens, we then iterate through all the tokens, inserting them into the inverted index asynchronously.
+Because we do need to often get and rewrite lists of documents for each new occurrence, a potential better version of this method would be to construct partial inverted indexes in memory and batch write them to the database.
+Additionally, some tokens may have a very large number of documents, making getting and rewriting even more wasteful, though a stricter stopword list can help to mitigate this problem somewhat.
+
+When a get call is made to an inverted index, we use the same natural language processing we used for the index creation on the search query.
+Then for each token in the query, we make an asychronous call to the index to search for that token and return the document ids that contain that token.
+After resolving duplicates and counting frequencies for each document, we go back to the original object store to retrieve the original documents given the document ids.
+IndexedDB does not provide batch \texttt{get} calls, so we grab the documents one-by-one asynchronously.
+Once all of them are retrieved, we use the designated ranking algorithm to calculate \texttt{score} values and sort the documents before returning them to the user via a callback function.
 

### 2014-12-11 paper/paper.tex
cleaned up some of the section on tries

@@
 The other ranking we provide is \texttt{Lucy.calculateCoverDensity()}, which implements Cover Density Ranking~\cite{li2002improvement}, an algorithm that takes into account positional information.
+The result is that documents that contain the terms in the search query closer together are ranked higher than documents that have them farther apart.
 For this algorithm to work, we need to store at index creation time the positions that the word appears in within the document.
+
 Both functions take in an optional \texttt{normalization} integer where the developer can specify whether they are interested in normalizing by document length or unique number of words in the document.
 If normalization is desired, then at index creation time, we calculate these measures and store them with the document object.
+Our current implementation stores them in the original object store, but another implementation could store them in a separate object store for document metadata.
 
@@
 
-A trie index in Lucy.js (prefix or suffix trie) is represented by two underlying entities in IndexedDB: an objects store to save nodes in the trie, and an index on that object store to make trie traversal faster.
-A reference to the input object store to be indexed -- which contains the full-text to be searched -- is also saved.
+A trie index in Lucy.js (prefix or suffix trie) is represented by two underlying entities in IndexedDB: an object store to save nodes in the trie, and an index on that object store to make trie traversal faster.
+A reference to the input object store to be indexed, which contains the full-text to be searched, is also saved.
 
@@
 \begin{center}
-node\_id: \{ parent\_id: a, char: b, doc\_ids: [x,y,z] \}
+\texttt{node\_id:\{parent\_id:a, char:b, docIds:[x,y,z]\}}
 \end{center}
-The key to the object store is the node\_id, and the corresponding value object has three attributes: parent\_id, char, and doc\_ids.
-The parent\_id attribute is the node id of the parent node in the trie, and the char attribute is the character value for the trie node.
-The final attribute is doc\_ids, which is a list of keys into the input text object store.
+The key to the object store is the \texttt{node\_id}, and the corresponding value object has three attributes: \texttt{parent\_id}, \texttt{char}, and \texttt{docIds}.
+The \texttt{parent\_id} attribute is the node id of the parent node in the trie, and the \texttt{char} attribute is the character value for the trie node.
+The final attribute is \texttt{doc\_ids}, which is a list of keys into the input text object store.
 The keys in this list are like foreign keys that allow the trie index to retrieve the actual text from the input object store when answering queries.
-Each path -- and therefore each node -- in the trie represents a unique prefix/suffix.
-The doc\_ids for a node contains the ids of all documents with that given prefix/suffix.
-Inserting a word from a given document therefore involves appending that document's id into the doc\_ids of each node along the path corresponding to the word.
-The structure of the trie is shown in Figure ******.
+Each path, and therefore each node, in the trie represents a unique prefix/suffix.
+The \texttt{docIds} for a node contains the ids of all documents with that given prefix/suffix.
+Inserting a word from a given document therefore involves appending that document's id into the \texttt{docIds} of each node along the path corresponding to the word.
+The structure of the trie is shown in Figure~\ref{trie}.
 It is important to note that this approach is not very scalable; since each node stores a list of matching document ids, interior nodes closer to the root of the trie could store large lists of these ids.
@@
 Matches can be returned as soon as the prefix is traced in the trie, and no further traversal along subtrees is needed.
+This is useful for when the dataset in question is reasonably small and speed is of great importance.
 An alternative design to the trie index is the Hybrid Trie discussed in the next section.
@@
 An artificial root node is created as the root of the trie.}
+\label{trie}
 \end{figure}
@@
 Additionally, we would then need to iterate over this list of children ids in order to find a particular child node with a given character value.
-With the current object store structure, we can optimize lookups by parent\_id and char by building an index on both these attributes.
-Overall, the trie index is backed by an object store for node storage and an index on that object store with a compound key of both parent\_id and char.
+With the current object store structure, we can optimize lookups by \texttt{parent\_id} and \texttt{char} by building an index on both these attributes.
+Overall, the trie index is backed by an object store for node storage and an index on that object store with a compound key of both \texttt{parent\_id} and \texttt{char}.
 
@@
 Partial matches are not accepted; the entire prefix (or suffix) must be present in the trie or no results are returned.
-If the entire pattern is found, the doc\_ids are extracted from the trie node corresponding to the last letter of the search pattern.
+If the entire pattern is found, the \texttt{docIds} are extracted from the trie node corresponding to the last letter of the search pattern.
 These ids are used to key into the input text object store and retrieve the original text data.
@@
 If set, words longer than the depth are cut off so that the remainder substrings are stored at the leaves.
-Figure ****** shows the structure of the same trie as before, but with a maximum depth of 4.
+Figure~\ref{triemax} shows the structure of the same trie as before, but with a maximum depth of 4.
 Leaf nodes store this substring data as a mapping from substring to document ids containing that substring.
@@
 Each substring remainder maps to a list of document ids with that remainder.}
+\label{triemax}
 \end{figure}

### 2014-12-11 paper/paper.tex

@@
 \subsubsection{Depth-Limiting}
+\label{depthlimit}
 To limit the size of trie indexes, an optional maximum depth can be set.
@@
 \subsection{Depth-Limiting for Tries}
-As seen in Figure *****, the maximum depth parameter has an effect on lookup times in trie indexes.
+As seen in Figure~\ref{comptrie}, the maximum depth parameter has an effect on lookup times in trie indexes.
 The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches.
-A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing max depths.
-The lookup time tends to decrease as the maximum depth increases; this is because depth cutoffs can result in slow searches through word mappings stored on leaf nodes (see section **** for details).
+A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing maximum depths.
+The lookup time tends to decrease as the maximum depth increases; this is because depth cutoffs can result in slow searches through word mappings stored on leaf nodes (see Section~\ref{depthlimit} for details).
 The difference in times is more pronounced for the term ``feel'', with a drop from 26.78ms to 18.05ms.
@@
    \includegraphics[scale=.43]{trie_maxdepth_graph}
-  \caption{Maxiumum depth vs lookup times for a prefix trie index.
+  \caption{Maximum depth vs lookup times for a prefix trie index.
 A depth of ``None'' indicates that there is no limit.
@@
 The dataset size was roughly 2100 tweets.}
+\label{comptrie}
 \end{figure}

### 2014-12-11 paper/paper.tex
future work, excel file for graph so we can edit it if needed

@@
 As seen in Figure~\ref{comptrie}, the maximum depth parameter has an effect on lookup times in trie indexes.
-The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches.
+The graph shows the results for a trie index prefix search, but similar results would be expected on suffix searches.
 A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing maximum depths.
@@
 \section{Future Work}
+The functionality of Lucy.js can be expanded to perform more complex queries and to improve the quality of returned results.
+While prefix and suffix searches are currently handled, arbitrary substring or regex searches are not supported.
+With these new features, users could write more customized queries and get better results.
+Additional forms of natural language processing could also improve the quality of results returned on searches.
+For example, synonym replacement could be implemented similarly to Postgres , allowing Lucy.js to find text results with similar themes or meaning.
+To improve performance, the existing indexes -- particularly the trie index -- could be optimized during index creation.
+
+Another avenue for future research would be collaborative searches between a client and server.
+A client could store partial data and use Lucy.js to search locally, while the server could respond with additional results not stored on the client.
+This could be useful to perform client-side caching of data for a web application, so that communication with the server is not always required.
 
@@
 
-\bibliographystyle{abbrv}
-\bibliography{paper}
+%\bibliographystyle{abbrv}
+%\bibliography{paper}
 

### 2014-12-11 paper/paper.tex
typo
add setup of evaluation

--- 2014-12-11 paper/paper.tex
@@
 
-\section{Evaluation and Applications}
+\section{Evaluation}
 
-\subsection{Client-side vs. Server-side Search}
+As seen previously, our implemented indexes perform much faster than a naive sequential scan over all full-text values.
+Given the current state of the IndexedDB API, this constitutes a great improvement in new functionality for fully client-side applications.
+However, most web applications are not client-side only and have a server component that can then query a server-side search engine such as Lucene, MySQL, or PostgreSQL.
+Thus in our evaluation, we seek to determine whether the client-side approach is faster than the server-side approach.
+While Lucene may generally be faster than Lucy.js for query evaluation, which is likely given that it has special purpose data structures and many years of development, a fully client-side approach may still beat a server-side approach due to network latency.
+
+We conduct our evaluation on two different real-life applications: a full-text search bar and a typeahead search bar that makes queries for every character as they are typed.
+The dataset that we test on is the same Twitter dataset used previously.
+For each set of tests, we test it on a random subset of tweets.
+For the search queries, because we do not have access to typical search queries, we simply take a random sample of 20 non-stopword words from the full tweet dataset.
+
+The server is implemented in Python and uses Django, Apache, and mod\_wsgi.
+It is hooked up to a MySQL database which has a full-text index on the tweet text.
+Both are hosted on the OpenStack cloud in a virtual machine, with the database residing in the virtual machine's local storage.
+Demonstrations of the two applications are accessible at \texttt{http://128.52.184.3/}.
+Figure~\ref{demo} has a screenshot of the typeahead search bar demo.
+For both demos, the user can first delete all data on the server as well as on the client.
+Then they choose whether to import the data, existing as a JSON file on the server, into the server-side MySQL database or into the client-side IndexedDB database.
+At that point the typeahead bar will work, querying the respective database, returning results, and outputting the time taken for each query.
+The user can additionally do a time test, which runs a selection of queries against the respective database and outputs the average time.
+Since IndexedDB does not yet support a synchronous API, the time test for the client database requires the user to continue clicking the button to run more queries and see an updating average time.
+
+\begin{figure}[h!]
+\centering
+   \includegraphics[scale=.34]{typeahead}
+  \caption{caption here.}
+\label{demo}
+\end{figure}
+
+\subsection{Results}
 

### 2014-12-11 paper/paper.tex
First draft of section on hybrid tries, added figure for perf comparison to the paper

--- 2014-12-11 paper/paper.tex
@@
    \includegraphics[scale=.4]{hybrid-trie}
-  \caption{Structure of a hybrid trie.}
+  \caption{Structure of a hybrid trie with leaf and path shrink.}
 \end{figure}
+
+We also implemented a novel approach, which we call a hybrid trie: A hybrid between an inverted index and a prefix (or suffix) trie.
+This approach takes advantage of the fact that every object store in IndexedDB is essentially a hash index with very fast key lookups.
+
+Every node in our hybrid trie has its entire path as its key.
+Therefore, when faced with a prefix query, we can directly jump to the position in the trie that corresponds to that prefix instead of doing \(O(n)\) lookups on the size of the prefix.
+
+Then, every node includes an array of characters that are the children of the node in the trie.
+The key of each child is determined by concatenating the key of the parent node with each of the strings in the children array.
+
+Every node can also potentially include a list of document ids, for documents that contain its prefix as a token (i.e.
+not a prefix of some longer token).
+Nodes without children must contain a list of document ids, but internal nodes can also contain document ids.
+For example, the node for “cat” would contain document ids of documents with the word "cat" itself, as well as children, for terms like "catsitting", "caturday" or "catnip".
+For these examples, the list of children could be \texttt{['n', 's', 'u']}.
+
+\subsubsection{Leaf and path Shrink}
+
+To eliminate wasteful lookups, we implement leaf and path shrinkage.
+In tries, there are often long sequences of nodes with only one child.
+If those nodes have no document ids, we can combine them to a single node without any loss of functionality.
+
+Shrinkage is a post-processing step after index generation, since we cannot know which nodes can be combined until all documents have been added to the index.
+Then our shrinkage algorithm works as follows:
+
+\begin{verbatim}
+for each node: 
+    if node.children = 1:
+        for each parent's children:
+        	    if children[i] points to node:
+        	    	children[i] += child.prefix;
+        // number of characters to reach parent:
+        child.parent++
+        delete node
+\end{verbatim}
+
+This results in a small speed increase, but since lookups by key in indexedDB are already quite fast, the increase is not significant.
+However, it also results in space savings, which is important because space on the client-side is very limited: after only a few Megabytes, browsers will ask for confirmation by the user, which is disruptive and can lead to non-technical users declining merely out of confusion.
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
    \includegraphics[scale=.53]{query-times}
-  \caption{caption here}
+  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers).
+}
 \end{figure}

### 2014-12-11 paper/paper.tex
Added some perf text

@@
 
+We can see that if we discard children and child-less nodes, our index basically becomes a simple inverted index with no stemming.
+However, traversing the subtree for prefix searches also makes it function like a prefix trie, hence the name Hybrid (prefix/suffix) trie.
+
 \subsubsection{Leaf and path Shrink}
@@
 
+\subsubsection{Asynchronous depth-first search}
+
+Since IndexedDB is multi-threaded, every step of a single transaction is asynchronous.
+This brings several challenges to writing transactions that are not present in most other DBMS', where concurrency conundrums only arise in the context of multiple concurrent transactions.
+
+Even something as simple as a depth-first search on our trie subtree becomes nontrivial when asynchronicity is added in the mix.
+Individual statements (reads or writes) are atomic, but reads and writes can be interleaved in any possible way (unless special care is taken to enforce a specific interleaving, at the cost of parallelism).
+
+For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by 1 when we encounter a subtree with more than one elements.
+When the counter becomes zero at a leaf, we conclude the search.
+
 \section{Performance and Comparison}
+
+\subsection{Data set}
+
+For the performance comparisons in this section we used a CSV dataset of a one million tweet sample originally intended for sentiment analysis\footnote{http://help.sentiment140.com/for-students}.
+
+We first removed unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content.
+We then wrote an ad-hoc Python script to select a random subset and convert it to JSON, which is what the generic IndexedDB importer we wrote expected.
+
+After several tests with different sample sizes, we settled for about 5\% of the data (44771 tweets), since our target browser (Google Chrome) was having difficulty with larger datasets.
 
@@
 
+For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes and 12 seconds to build the suffix trie and 2 minutes and 53 seconds to build the hybrid prefix trie (we did not measure
+
 \subsubsection{Index Lookups}
+
+We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB offers out of the box.
+The results can be seen in Figure~\ref{querytimes}.
+
+While all of our indexes have comparable performance, they outperform sequential search by several orders of magnitude.
+Sequential search for all four of our queries seems to be taking close to 3 seconds, whereas our index-optimized queries take only about 10-100ms.
 
@@
 }
+  \label{querytimes}
 \end{figure}

### 2014-12-11 paper/paper.tex
Some more fixes and additions

@@
 
-Indexed Database (IndexedDB) is a collection of Javascript APIs and is an official W3C specification (Proposed Recommendation stage) ~\cite{w3c}.
+Indexed Database (IndexedDB) is a collection of Javascript APIs for a multi-threaded, asynchronous client-side key-value store.
+It is an official W3C specification ~\cite{w3c}, at the Proposed Recommendation stage as of November 20th, 2014.
 It is supported by almost every modern browser, both on desktop and mobile devices.
@@
 For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.
+
 On Chrome browsers, IndexedDB interfaces with a key-value store named LevelDB built at Google in C++ and inspired by BigTable.
@@
 \subsubsection{Creating a Full-Text Index}
+
 The interface to a database is maintained through an \texttt{IDBDatabase} object.
@@
 The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}.
-*********UPDATE If the developer does not specify a type, then a typical IndexedDB index would be created.
+If the developer does not specify a type, then the function call is deferred to the native IndexedDB API and a regular index would be created.
 Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.
@@
 
-We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.
-The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-new.js} *********UPDATE?
+We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API.
+The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} *********UPDATE?
 plus some third-party files that the user must include in their HTML file.
@@
      	    children[i] += child.prefix;
-        // number of characters to reach parent:
-        child.parent++
+     child.parent++ (# of chars to reach parent)
      delete node
@@
 
-For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by 1 when we encounter a subtree with more than one elements.
+For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by max(0, n) when we encounter a node with n+1 children.
 When the counter becomes zero at a leaf, we conclude the search.
@@
 
-We first removed unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content.
+We first stripped off unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content.
 We then wrote an ad-hoc Python script to select a random subset and convert it to JSON, which is what the generic IndexedDB importer we wrote expected.
 
-After several tests with different sample sizes, we settled for about 5\% of the data (44771 tweets), since our target browser (Google Chrome) was having difficulty with larger datasets.
+After several tests with different sample sizes, we settled for about 5\% of the original dataset (44771 tweets), as our target browser (Google Chrome) was having difficulty with larger datasets.
 
@@
 
-For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes and 12 seconds to build the suffix trie and 2 minutes and 53 seconds to build the hybrid prefix trie (we did not measure
+For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes 12 seconds to build the suffix trie, 2 minutes 53 seconds to build a hybrid prefix trie and 3 minutes 2 seconds to build a hybrid suffix tree.
 
@@
 
-We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB offers out of the box.
+We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB provides out of the box.
 The results can be seen in Figure~\ref{querytimes}.
 
-While all of our indexes have comparable performance, they outperform sequential search by several orders of magnitude.
+While all of our indexes have comparable performance, they outperform sequential search by orders of magnitude.
 Sequential search for all four of our queries seems to be taking close to 3 seconds, whereas our index-optimized queries take only about 10-100ms.
@@
 \begin{figure}[h!]
-   \includegraphics[scale=.43]{trie_maxdepth_graph}
+   \includegraphics[scale=.38]{trie_maxdepth_graph}
   \caption{Maximum depth vs lookup times for a prefix trie index.

### 2014-12-11 paper/paper.tex
results section

--- 2014-12-11 paper/paper.tex
@@
    \includegraphics[scale=.4]{hybrid-trie}
-  \caption{Structure of a hybrid trie with leaf and path shrink.}
+  \caption{Structure of a hybrid trie.}
 \end{figure}
-
-We also implemented a novel approach, which we call a hybrid trie: A hybrid between an inverted index and a prefix (or suffix) trie.
-This approach takes advantage of the fact that every object store in IndexedDB is essentially a hash index with very fast key lookups.
-
-Every node in our hybrid trie has its entire path as its key.
-Therefore, when faced with a prefix query, we can directly jump to the position in the trie that corresponds to that prefix instead of doing \(O(n)\) lookups on the size of the prefix.
-
-Then, every node includes an array of characters that are the children of the node in the trie.
-The key of each child is determined by concatenating the key of the parent node with each of the strings in the children array.
-
-Every node can also potentially include a list of document ids, for documents that contain its prefix as a token (i.e.
-not a prefix of some longer token).
-Nodes without children must contain a list of document ids, but internal nodes can also contain document ids.
-For example, the node for “cat” would contain document ids of documents with the word "cat" itself, as well as children, for terms like "catsitting", "caturday" or "catnip".
-For these examples, the list of children could be \texttt{['n', 's', 'u']}.
-
-\subsubsection{Leaf and path Shrink}
-
-To eliminate wasteful lookups, we implement leaf and path shrinkage.
-In tries, there are often long sequences of nodes with only one child.
-If those nodes have no document ids, we can combine them to a single node without any loss of functionality.
-
-Shrinkage is a post-processing step after index generation, since we cannot know which nodes can be combined until all documents have been added to the index.
-Then our shrinkage algorithm works as follows:
-
-\begin{verbatim}
-for each node: 
-    if node.children = 1:
-        for each parent's children:
-        	    if children[i] points to node:
-        	    	children[i] += child.prefix;
-        // number of characters to reach parent:
-        child.parent++
-        delete node
-\end{verbatim}
-
-This results in a small speed increase, but since lookups by key in indexedDB are already quite fast, the increase is not significant.
-However, it also results in space savings, which is important because space on the client-side is very limited: after only a few Megabytes, browsers will ask for confirmation by the user, which is disruptive and can lead to non-technical users declining merely out of confusion.
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
    \includegraphics[scale=.53]{query-times}
-  \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers).
-}
+  \caption{caption here}
 \end{figure}
@@
 As seen in Figure~\ref{comptrie}, the maximum depth parameter has an effect on lookup times in trie indexes.
-The graph shows the results for a trie index prefix search, but similar results would be expected on suffix searches.
+The graph shows the results for a trie index prefix search, but the similar results would be expected on suffix searches.
 A small set of input tweet data was used (367 KB data, about 2100 tweets), and the same three words were looked up in indexes created with differing maximum depths.
@@
 
-\section{Evaluation and Applications}
+\section{Evaluation}
 
-\subsection{Client-side vs. Server-side Search}
+As seen previously, our implemented indexes perform much faster than a naive sequential scan over all full-text values.
+Given the current state of the IndexedDB API, this constitutes a great improvement in new functionality for fully client-side applications.
+However, most web applications are not client-side only and have a server component that can then query a server-side search engine such as Lucene, MySQL, or PostgreSQL.
+Thus in our evaluation, we seek to determine whether the client-side approach is faster than the server-side approach.
+While Lucene may generally be faster than Lucy.js for query evaluation, which is likely given that it has special purpose data structures and many years of development, a fully client-side approach may still beat a server-side approach due to network latency.
+
+The server we built is implemented in Python and uses Django, Apache, and mod\_wsgi.
+It is hooked up to a MySQL database which has a full-text index on the tweet text.
+Both are hosted on the OpenStack cloud in a virtual machine, with the database residing in the virtual machine's local storage.
+The full-text search bar on the client side uses our inverted index to search for the query, while the typeahead search bar uses our prefix trie as it is more suited to finding prefixes.
+
+We conduct our evaluation on two different real-life applications: a full-text search bar and a typeahead search bar that makes queries for every character as they are typed.
+The dataset that we test on is the same Twitter dataset used previously.
+We test each application on two different size datasets of 100 and 2000 tweets picked randomly.
+For the search queries, because we do not have access to typical search queries in real life, we simply take a random sample of 20 non-stopword words from the full tweet dataset for each set of experiments.
+We conduct 8 trials for each condition and delete and reinsert and recreate indexes before each trial.
+For the full-text search bar, we simply search for the 20 words and record the time taken.
+For the typeahead bar, we search for each of the 20 words as well as all prefixes of each word, in order as if one were typing into the search bar, and record the time.
 
 \begin{figure}[h!]
-   \includegraphics[scale=.53]{demo_results}
-  \caption{caption here.}
+   \includegraphics[scale=.43]{figure_1}
+  \caption{Comparison of client-side versus server-side indexes for full-text search.
+Tested on a full-text search bar (FT Search) and a typeahead search bar (Typeahead) and with Twitter dataset sizes of 100 and 2000 tweets.}
+\label{compare}
 \end{figure}
+
+\subsection{Results}
+
+In Figure~\ref{compare}, we report the average time taken for each of the approaches (client versus server) on the two applications and dataset sizes.
+As can be seen, overall the client-side only approach is faster than than the server-side approach.
+When looking at full-text search, even when the dataset size grows over a magnitude larger, the server-side average time varies little.
+This suggests that the time taken is mostly taken up by network latency.
+We do see a small increase in the time taken for the client-side database.
+This suggests that as datasets grow larger, it may be a better decision to store the majority of the data on the server side and do queries on smaller subsets in the client.
+
+When looking at the typeahead search bar, we see that when the dataset gets larger, the average time taken for both client and server increases, though the client-side increase is greater.
+When looking more closely at the times for different queries made, we notice that there is a great deal of variation in the time because a very short prefix will return a much larger result set than a longer prefix.
+The client side had greater variation overall, with a standard deviation of 56.477ms, maximum time of 256ms, and minimum time of 1ms.
+The server side had a standard deviation of 49.116ms, maximum time of 220ms, and minimum time of 14ms.
+Given these findings, a best approach may be employ a mixed approach and send shorter prefixes to the server and longer prefixes to the client.
+Generally, queries that will return a small result set would be faster if they are served from the client, as the network latency always tacks on extra time for the query to the server.
+Queries that will return a very large result set may have better performance if they are sent to the server.
+
+\subsection{Live Demos}
+
+\begin{figure}[h!]
+\centering
+   \includegraphics[scale=.34]{typeahead}
+  \caption{Screenshot of typeahead search bar demo.}
+\label{demo}
+\end{figure}
+Demonstrations of the two applications are accessible at \texttt{http://128.52.184.3/}.
+Figure~\ref{demo} has a screenshot of the typeahead search bar demo.
+For both demos, the user first deletes all data on the server as well as on the client.
+Then they choose whether to import the data, existing as a JSON file on the server, into the server-side MySQL database or into the client-side IndexedDB database.
+At that point the typeahead bar will work, querying the respective database, returning results, and outputting the time taken for each query.
+The user can additionally do a time test, which runs a selection of queries against the respective database and outputs the average time.
+Since IndexedDB does not yet support a synchronous API, the time test for the client-side database requires the user to continue clicking the button to run more queries and see an updating average time.
 
@@
 \section{Future Work}
-The functionality of Lucy.js can be expanded to perform more complex queries and to improve the quality of returned results.
-While prefix and suffix searches are currently handled, arbitrary substring or regex searches are not supported.
-With these new features, users could write more customized queries and get better results.
-Additional forms of natural language processing could also improve the quality of results returned on searches.
-For example, synonym replacement could be implemented similarly to Postgres , allowing Lucy.js to find text results with similar themes or meaning.
-To improve performance, the existing indexes -- particularly the trie index -- could be optimized during index creation.
-
-Another avenue for future research would be collaborative searches between a client and server.
-A client could store partial data and use Lucy.js to search locally, while the server could respond with additional results not stored on the client.
-This could be useful to perform client-side caching of data for a web application, so that communication with the server is not always required.
 

### 2014-12-11 paper/paper.tex
conclusion

@@
 When looking at the typeahead search bar, we see that when the dataset gets larger, the average time taken for both client and server increases, though the client-side increase is greater.
-When looking more closely at the times for different queries made, we notice that there is a great deal of variation in the time because a very short prefix will return a much larger result set than a longer prefix.
+When looking more closely within trials at the times for all the queries made, we notice that there is a great deal of variation because a very short prefix will return a much larger result set than a longer prefix.
 The client side had greater variation overall, with a standard deviation of 56.477ms, maximum time of 256ms, and minimum time of 1ms.
@@
 
-\begin{figure}[h!]
-\centering
-   \includegraphics[scale=.34]{typeahead}
-  \caption{Screenshot of typeahead search bar demo.}
-\label{demo}
-\end{figure}
 Demonstrations of the two applications are accessible at \texttt{http://128.52.184.3/}.
@@
 
+\begin{figure}[h!]
+\centering
+   \includegraphics[scale=.34]{typeahead}
+  \caption{Screenshot of typeahead search bar demo.}
+\label{demo}
+\end{figure}
+
 \section{Discussion}
+
+From our findings, we determine that client-side search engines are indeed feasible to build and have reasonable performance on 
+ could be very useful for the right application and
 
@@
 
-Another avenue for future research would be collaborative searches between a client and server.
+Another avenue for future research would be to build and evaluate applications that do collaborative searches between a client and server.
 A client could store partial data and use Lucy.js to search locally, while the server could respond with additional results not stored on the client.
@@
 
+Client-side search engines offer new functionality to client-side applications and potential speed improvements for applications that query a server-side search engine.
+We implemented a client-side search engine as an extension of the IndexedDB API, building several different types of index structures including inverted indexes, prefix and suffix tries, and a hybrid approach combining the two.
+We compare the performance of our indexes against each other and find that our hybrid approach is overall the fastest.
+We additionally evaluate our system by implementing a full-text search bar and a typeahead search bar and compare performance of a client-side only approach with a server-side only approach using MySQL.
+We find that for small to moderate datasets, the network latency incurred by trips to the server make client-size querying faster.
+Finally, we imagine potential applications that could be enhanced using our client-side search engine.
+
 \bibliographystyle{abbrv}

### 2014-12-11 paper/paper.tex
Paper edits

--- 2014-12-11 paper/paper.tex
@@
 We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API.
-The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} *********UPDATE?
-plus some third-party files that the user must include in their HTML file.
+The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js}.
 The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.
@@
 
-We looked to many existing implementations of search engines and the indexes they use to decide what indexes to build, such as inverted indexes in Lucene and GiN and GiST indexes in PostgreSQL.
+We looked into many existing implementations of search engines and the indexes they use to decide what indexes to build, such as inverted indexes in Lucene and GiN and GiST indexes in PostgreSQL.
 We initially implemented an inverted index as well as prefix and suffix tries, before also developing a hybrid trie combining elements of both inverted index and tries as a third index.:
@@
 \subsubsection{Trie Node Object Store}
+
 Each entry in the object store represents a different node in the trie. The structure of entries in the object store is as follows:
@@
          if children[i] points to node:
-     	    children[i] += child.prefix;
+     	    children[i] += child.prefix
+     	    exit loop
      child.parent++ (# of chars to reach parent)
@@
 
-For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes 12 seconds to build the suffix trie, 2 minutes 53 seconds to build a hybrid prefix trie and 3 minutes 2 seconds to build a hybrid suffix tree.
+For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes 11 seconds to build the suffix trie, 2 minutes 53 seconds to build a hybrid prefix trie and 3 minutes 2 seconds to build a hybrid suffix tree.
+
+For a dataset of 5000 tweets, it takes 20 seconds to build the inverted index and the hybrid indices, but 3 minutes to build the prefix/suffix tries, which indicates that the prefix/suffix tries would be more suited to smaller datasets.
 
@@
 
-\section{Evaluation}
+\section{Evaluation and Applications}
 
-As seen previously, our implemented indexes perform much faster than a naive sequential scan over all full-text values.
-Given the current state of the IndexedDB API, this constitutes a great improvement in new functionality for fully client-side applications.
-However, most web applications are not client-side only and have a server component that can then query a server-side search engine such as Lucene, MySQL, or PostgreSQL.
-Thus in our evaluation, we seek to determine whether the client-side approach is faster than the server-side approach.
-While Lucene may generally be faster than Lucy.js for query evaluation, which is likely given that it has special purpose data structures and many years of development, a fully client-side approach may still beat a server-side approach due to network latency.
-
-The server we built is implemented in Python and uses Django, Apache, and mod\_wsgi.
-It is hooked up to a MySQL database which has a full-text index on the tweet text.
-Both are hosted on the OpenStack cloud in a virtual machine, with the database residing in the virtual machine's local storage.
-The full-text search bar on the client side uses our inverted index to search for the query, while the typeahead search bar uses our prefix trie as it is more suited to finding prefixes.
-
-We conduct our evaluation on two different real-life applications: a full-text search bar and a typeahead search bar that makes queries for every character as they are typed.
-The dataset that we test on is the same Twitter dataset used previously.
-We test each application on two different size datasets of 100 and 2000 tweets picked randomly.
-For the search queries, because we do not have access to typical search queries in real life, we simply take a random sample of 20 non-stopword words from the full tweet dataset for each set of experiments.
-We conduct 8 trials for each condition and delete and reinsert and recreate indexes before each trial.
-For the full-text search bar, we simply search for the 20 words and record the time taken.
-For the typeahead bar, we search for each of the 20 words as well as all prefixes of each word, in order as if one were typing into the search bar, and record the time.
+\subsection{Client-side vs. Server-side Search}
 
 \begin{figure}[h!]
-   \includegraphics[scale=.43]{figure_1}
-  \caption{Comparison of client-side versus server-side indexes for full-text search.
-Tested on a full-text search bar (FT Search) and a typeahead search bar (Typeahead) and with Twitter dataset sizes of 100 and 2000 tweets.}
-\label{compare}
+   \includegraphics[scale=.53]{demo_results}
+  \caption{caption here.}
 \end{figure}
-
-\subsection{Results}
-
-In Figure~\ref{compare}, we report the average time taken for each of the approaches (client versus server) on the two applications and dataset sizes.
-As can be seen, overall the client-side only approach is faster than than the server-side approach.
-When looking at full-text search, even when the dataset size grows over a magnitude larger, the server-side average time varies little.
-This suggests that the time taken is mostly taken up by network latency.
-We do see a small increase in the time taken for the client-side database.
-This suggests that as datasets grow larger, it may be a better decision to store the majority of the data on the server side and do queries on smaller subsets in the client.
-
-When looking at the typeahead search bar, we see that when the dataset gets larger, the average time taken for both client and server increases, though the client-side increase is greater.
-When looking more closely at the times for different queries made, we notice that there is a great deal of variation in the time because a very short prefix will return a much larger result set than a longer prefix.
-The client side had greater variation overall, with a standard deviation of 56.477ms, maximum time of 256ms, and minimum time of 1ms.
-The server side had a standard deviation of 49.116ms, maximum time of 220ms, and minimum time of 14ms.
-Given these findings, a best approach may be employ a mixed approach and send shorter prefixes to the server and longer prefixes to the client.
-Generally, queries that will return a small result set would be faster if they are served from the client, as the network latency always tacks on extra time for the query to the server.
-Queries that will return a very large result set may have better performance if they are sent to the server.
-
-\subsection{Live Demos}
-
-\begin{figure}[h!]
-\centering
-   \includegraphics[scale=.34]{typeahead}
-  \caption{Screenshot of typeahead search bar demo.}
-\label{demo}
-\end{figure}
-Demonstrations of the two applications are accessible at \texttt{http://128.52.184.3/}.
-Figure~\ref{demo} has a screenshot of the typeahead search bar demo.
-For both demos, the user first deletes all data on the server as well as on the client.
-Then they choose whether to import the data, existing as a JSON file on the server, into the server-side MySQL database or into the client-side IndexedDB database.
-At that point the typeahead bar will work, querying the respective database, returning results, and outputting the time taken for each query.
-The user can additionally do a time test, which runs a selection of queries against the respective database and outputs the average time.
-Since IndexedDB does not yet support a synchronous API, the time test for the client-side database requires the user to continue clicking the button to run more queries and see an updating average time.
 

### 2014-12-11 paper/paper.tex
discussion

--- 2014-12-11 paper/paper.tex
@@
 
-From our findings, we determine that client-side search engines are indeed feasible to build and have reasonable performance on 
- could be very useful for the right application and
+From our findings, we determine that client-side search engines are indeed feasible to build, can be easy to use, and have improved performance over server-side search engines for certain applications and data sizes.
+Thus, our system Lucy.js opens up many possibilities for new applications and new data processing and storage architectures.
 
+First, as stated earlier, there are many reasons why we would want to build applications that store and process more data on the client side.
+One issue that has had a great deal of attention lately is privacy and the question of the ownership of data.
+As a pushback against companies and web applications collecting personal and sensitive data to sell or give to others, many people have worked on applications that are more distributed than centralized, such as the Diaspora social network.
 Newer peer-to-peer standards such as WebRTC for browsers may make more client-heavy social and interactive applications feasible in the future.
+Additionally, another benefit of having data stored in the client specifically for full-text searching is that the queries themselves need not be sent to a server and logged.
+As shown previously, search queries can reveal a great deal about a person~\cite{teevan2005personalizing, khoshgozaran2009private} and potentially some users would be interested in having private search.
+
+We have also postulated from our findings that a mixed approach combining server and client search queries may be beneficial for performance reasons.
+For instance, as we saw with the typeahead search bar, longer prefixes are much faster served from the client.
+Another interesting application that may call for a mixed approach combining server and client queries is personalization.
+As we found in the previous section, queries that return a large result set might be better sent to the server.
+This could be used for personalization by having a server return generic results for a query and letting the client side personalize the results through re-ranking and other means.
+This is additionally useful because this offloads client-specific processing and client-specific data to the client and frees up resources on the server.
+
+Finally, building out client-side storage and processing capabilities makes applications more robust to downtimes, which may be common on smartphone browsers.
+In addition to caching web pages locally for re-finding, a web application can now also provide searching over these web pages offline.
 

### 2014-12-11 paper/paper.tex

--- 2014-12-11 paper/paper.tex
@@
 
+\begin{figure}
+   \includegraphics[scale=.2]{search-screenshot}
+  \caption{Our local full-text search demo that we used to take the measurements described in this experiment.}
+\end{figure}
+
 \subsection{Data set}
@@
 \begin{figure}
-   \includegraphics[scale=.53]{query-times}
+   \includegraphics[scale=.39]{query-times}
   \caption{Comparison of query times for various queries with different result set sizes (left to right: smaller to larger) between our three main types of indexes and sequential search (the only way to search strings that indexedDB offers).
@@
 The data also shows that the number of results has an  impact on lookup time.
-The three graphs are tiered such that ``feel'', with the most results, is also the slowest query.
+The three graphs are tiered such that "feel", with the most results, is also the slowest query.
 While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.
+
+\subsection{Comparison}
+
+As we have seen earlier in this section, prefix and suffix tries are very intensive to create in a key-value store, and thus, are better suited to smaller datasets.
+This is what initially motivated us to build the hybrid approach, which, as we have demonstrated, is orders of magnitude faster in index creation time and slightly faster in query time.
+However, the hybrid approach is less space efficient than tries (in the general case), since the entire path to the node needs to be stored as its key, which makes it better suited for shorter tokens.
+The inverted index is slightly (within the margin of error) slower for lookups than both tries, but this is likely due to the overhead of stemming.
 

### 2014-12-11 paper/paper.tex
cleaning up

--- 2014-12-11 paper/paper.tex
@@
 We compare their performance on different types of queries and with different sizes and types of datasets.
-We find that...FILL IN HERE.
+We find that overall, our hybrid trie index, which is a combination of inverted index and trie, performs the best.
 
@@
 We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API.
-The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} *********UPDATE?
-plus some third-party files that the user must include in their HTML file.
+The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} plus some third-party files that the user must include in their HTML file.
 The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.
@@
 We find that for small to moderate datasets, the network latency incurred by trips to the server make client-size querying faster.
-Finally, we imagine potential applications that could be enhanced using our client-side search engine.
+Finally, we imagine potential applications that could be enhanced or realized using our client-side search engine.
 

### 2014-12-11 paper/paper.tex
Minor

@@
 In this paper, we introduce Lucy.js, a fully client-side search engine built as an extension of the existing well-supported IndexedDB API.
-We compare the performance of the different indexes we implement on different types of full-text content and queries.
-We find that a hybrid approach combining inverted indexes and tries perform the best, particularly on larger datasets.
+We compare the performance of the different indexes we implement, on different types of full-text content and queries.
+We find that a hybrid approach combining inverted indexes and tries performs the best, particularly on larger datasets.
 We also implement various real-life applications of our system and compare the performance of our system with that of using a fully server side system.

### 2014-12-11 paper/paper.tex
bugs
final paper

@@
 Nodes without children must contain a list of document ids, but internal nodes can also contain document ids.
-For example, the node for “cat” would contain document ids of documents with the word "cat" itself, as well as children, for terms like "catsitting", "caturday" or "catnip".
+For example, the node for ``cat” would contain document ids of documents with the word ``cat" itself, as well as children, for terms like ``catsitting", ``caturday" or ``catnip".
 For these examples, the list of children could be \texttt{['n', 's', 'u']}.
@@
 
-\subsubsection{Leaf and path Shrink}
+\subsubsection{Leaf and Path Shrink}
 
@@
 The data also shows that the number of results has an  impact on lookup time.
-The three graphs are tiered such that "feel", with the most results, is also the slowest query.
+The three graphs are tiered such that ``feel", with the most results, is also the slowest query.
 While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.
